---
title: "sink_appeears_scripts.Rmd"
author: "K. Enns"
date: "2/28/2020"
output: html_document
---

Sandbox for appeears Functions to be used for Cronjob (in theory)



Get a token for appeears
```{r}
appeears_get_token = function(username, password){
  secret = jsonlite::base64_enc(paste(username, password, sep = ":"))
  response = httr::POST(paste0("https://lpdaacsvc.cr.usgs.gov/appeears/api", "/login"),
                   httr::add_headers("Authorization" = paste("Basic", gsub("\n", "", secret)),
                               "Content-Type" = "application/x-www-form-urlencoded;charset=UTF-8"),
                   body = "grant_type=client_credentials")
  token_response = httr::content(response)

  token_response
}

username_ = 'username'
my_token_response = appeears_get_token(username = username_, password = .rs.askForPassword('Password'))
my_token_response
```

get tasks for this user from appeears
```{r}
appeears_get_tasks = function(token_response){
  bearer_token         = paste("Bearer", token_response$token)
  response      = GET("https://lpdaacsvc.cr.usgs.gov/appeears/api/task", add_headers(Authorization = bearer_token))
  task_response = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
  tasks = jsonlite::fromJSON(txt=task_response)
  return(tasks)
}

my_appeears_tasks = appeears_get_tasks(my_token_response)
my_appeears_tasks
```


Convert the my_appeears_tasks dataframe into a easier to manipulate one that has a field for phenocam names
```{r}
get_appeears_clean_tasks = function(my_appeears_tasks){
  # These strings are used in the tasks names in Appeears
  task_strs    = c('_EVI_v6_tera_sinu', '_EVI_v6_aqua_sinu', '_NDVI_v6_tera_sinu',  '_NDVI_v6_aqua_sinu', '_TDs_v6', '_LC_sinu_v6')
  # These strings are what we name the tasks in the submit tasks function for Appeears
  task_str_ids = c('evi_tera', 'evi_aqua','ndvi_tera', 'ndvi_aqua', 'tds', 'lc_v6')
  
  # walk between the two lists with this dataframe
  str_lookup_df = data.frame(task_str_id = task_str_ids, 
                             task_str    = task_strs, stringsAsFactors = FALSE)
  
  final_df = data.frame()
  # loop through types and check tasks at this site
  for (t_type in task_str_ids){
    t_str    = subset(str_lookup_df, str_lookup_df$task_str_id == t_type)$task_str
    tasks_df = my_appeears_tasks[grep(c(t_str), my_appeears_tasks$task_name),]
    cache_df = tasks_df %>% select('task_id', 'task_name', 'created')
    cache_df_names = as.character(strsplit(cache_df$task_name, t_str))
    cache_df$created = as.Date(cache_df$created)
    cache_df$site_name = cache_df_names 
    cache_df$data_type = t_type
    
    if (dim(final_df)[1]==0){
      final_df = cache_df
    }else{
      final_df = rbind(final_df, cache_df)
    }
  }
  return(final_df)
}
clean_tasks = get_appeears_clean_tasks(my_appeears_tasks)
clean_tasks
```


check to see how many remaining tasks you have available
```{r}
appeears_get_remaining_tasks = function(appeears_tasks){
  # Get current time in POSIXct
  now = Sys.time()
  appeears_tasks$created = as.POSIXct(appeears_tasks$created,format="%Y-%m-%dT%H:%M", tz = 'UTC')
  attributes(appeears_tasks$created)$tzone = 'MST'
  
  # Grab tasks created in the last 24 hours
  last_24h_tasks     = subset(appeears_tasks, appeears_tasks$created > (now - (60*60*24*1)))
  over_24h_ago_tasks = subset(appeears_tasks, appeears_tasks$created < (now - (60*60*24*1)))
  if (dim(over_24h_ago_tasks)[1] > 0){
    pending_tasks = subset(over_24h_ago_tasks, over_24h_ago_tasks$status == 'pending') 
  }else{
    pending_tasks = data.frame()
  }
  
  # Number of submitions remaining for the last 24hours
  n_tasks_24h = dim(last_24h_tasks)[1]
  n_pending_tasks = dim(pending_tasks)[1]
  submitions_remaining = 100 - n_tasks_24h - n_pending_tasks
}

my_remaining_tasks = appeears_get_remaining_tasks(my_appeears_tasks)
my_remaining_tasks
```

Get all of the phenocam sites with ROIs to use to download data from appeears with
```{r}
source('../../functions/phenocam_api.R')
# dir argument is just saying that the main director for phenosynth is up 2 directories (../..)
pc_data   = cache_phenocam_data(dir = '../..')
cams_     = pc_data$cams
cams_
```

Put together some test sites to use
```{r}
phenocam_sites = cams_$site
test_sites = phenocam_sites[16:25]
test_sites
```


Take stock of phenocam sites -
  - do they have all their appeears tasks?
  - are all of the tasks recent (last 3 months)
  - do they have a nlcd layer if it exists?
  - are they in the cams_ list?
```{r}
# Returns a dataframe 
appeears_stock_df = function(sites_phenocam, clean_task_df){
  task_str_ids = c('evi_tera', 'evi_aqua','ndvi_tera', 'ndvi_aqua', 'tds', 'lc_v6')
  clean_task_df$complete_appeears = FALSE
  
  for (site_ in sites_phenocam){
    # Tasks for this site
    these_tasks = subset(clean_task_df, clean_task_df$site_name %in% site_)
    
    # Get the length of the site's tasks (should be 6 for all data)
    site_task_length = length(unique(these_tasks$task_name))
    # Set whether this site has all the tasks it needs
    if (site_task_length == 6){
      clean_task_df$complete_appeears[clean_task_df$site_name == site_] = TRUE
    }
  }
  return (clean_task_df)
}

appeears_stocked_df = appeears_stock_df(phenocam_sites, clean_tasks)
```

Check phenocam site has all tasks (complete?)
```{r}
appeears_check_site = function(this_site){
  site_status_row = subset(appeears_stocked_df, appeears_stocked_df$site_name  == this_site) %>% 
    dplyr::select(site_name, complete_appeears) %>% 
    distinct()
  site_status = site_status_row$complete_appeears
}
# FALSE = not complete, TRUE = complete aka has the 6 tasks
site_status_ = appeears_check_site('harvardfarmnorth')
```

Check phenocam missing tasks if not all tasks exist (missing tasks for 1 site)
```{r}


```


Check phenocam site age (check the age of site tasks)
```{r}


```


Submit tasks that are missing, or old.
```{r}


```

Check completion of phenocam site tasks (are they done or pending)
```{r}


```


```

```

Clean up duplicates (remove old tasks if 2 exist)
```{r}


```






































