---
title: "submit_appeears_tasks.Rmd"
author: "K. Enns"
date: "5/31/2019"
output: html_document
---

##Submitting tasks to AppEEARS using the submit_appeears_tasks.R script

Get token for AppEEARS
```{r}
####################################################################################
# GO RUN global.R for variables and libraries required in this RMD file
####################################################################################
username = 'earth_data_username'
password = .rs.askForPassword('Password')

token_response = AppEEARS4R::appeears_start_session(username,password)
rm(password)
```

View all AppEEARS tasks under user
```{r}
token         = paste("Bearer", token_response$token)
response      = GET("https://lpdaacsvc.cr.usgs.gov/appeears/api/task", add_headers(Authorization = token))
task_response = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
tasks = jsonlite::fromJSON(txt=task_response)
tasks

# See how many submissions are available.  
get_submitions_remaining(tasks)
```

Submit ALL SINU tasks at a site:
```{r}
# Tasks submitted in alphabetical order: 1:4
source('submit_appeears_tasks.R')
# Get phenocam sites to submit to appeears
phenocam_sites = cams_$site

# If you download all data types at once than you can assume all the different
#   data types exist for each site already submitted.  This means we can
#   use either of the two below (cached_lc_names or cached_ndvi_names) to
#   find the difference between tasks we have submitted to AppEEARS and
#   tasks we need to submit.

# cached_lc_names
lc = tasks[grep(c('LC_sinu_v6'), tasks$task_name),]
cached_lc = lc %>% select('task_id','task_name')
cached_lc_names = as.character(strsplit(cached_lc$task_name, '_LC_sinu_v6'))
# Grab first 16 of the site names that need to be submitted as tasks 
#  - 16 is 16*6=96 which is less than 100 (the limit per day)
roi_sites_ = setdiff(phenocam_sites, cached_lc_names)[1:16]
roi_sites_

# cached_ndvi_names
ndvi = tasks[grep(c('NDVI_v6_tera_sinu'), tasks$task_name),]
cached_ndvi = ndvi %>% select('task_id','task_name')
cached_ndvi_names = as.character(strsplit(cached_ndvi$task_name, '_NDVI_v6_tera_sinu'))
# Grab first 16 of the site names that need to be submitted as tasks
roi_sites_ = setdiff(phenocam_sites, cached_ndvi_names)[1:16]
roi_sites_

# tasks[grep(c('gaspard'), tasks$task_name),]
```

Submit missing tasks from previous cell
```{r}
# Layer choices = 'NDVI_tera_sinu' | 'EVI_tera_sinu' | 'NDVI_aqua_sinu' | 'EVI_aqua_sinu' | 'TDS_v6' | 'LC_sinu_nc'
# size length should be 16
print (length(roi_sites_))
submit_all_tasks_for_site_appeears(appeears_token=token, 
  roi_sites = roi_sites_, 
  layers_ = c('NDVI_tera_sinu', 'EVI_tera_sinu', 'NDVI_aqua_sinu', 'EVI_aqua_sinu', 'TDS_v6', 'LC_sinu_nc'), 
  test = TRUE, 
  phenocam_roi_df = cams_,
  void_size_ = TRUE)

```



















```{r}
pc_data   = cache_phenocam_data(dir = '../..')
cams_     = pc_data$cams
roi_files = pc_data$rois

source('submit_appeears_tasks.R')
# size length should be 16
print (length(roi_sites_))
submit_all_tasks_for_site_appeears(appeears_token=token, 
  roi_sites = roi_sites_, 
  layers_ = c('NDVI_tera_sinu', 'EVI_tera_sinu', 'NDVI_aqua_sinu', 'EVI_aqua_sinu', 'TDS_v6', 'LC_sinu_nc'), 
  test = FALSE, 
  phenocam_roi_df = cams_,
  void_size_ = TRUE)


# submit_all_tasks_for_site_appeears(appeears_token=token, roi_sites= roi_sites_, test = TRUE, void_size_ = FALSE)
# submit_all_tasks_for_site_appeears(appeears_token=token, roi_sites=roi_sites_, layers_ = c('LC_sinu_nc'), test=TRUE, void_size_ = TRUE)
```




find failed tasks with only 1 year of data!
```{r}
getwd()
year1_data = c()
sites_ = cams_$site
for (site_ in sites_with_nlcd){
  file_location = paste0('../../www/site_data/', site_ ,'/data_layers/ndvi/tera/', gsub("\\.", "-", site_),'-NDVI-v6-tera-sinu-request.json')
  start_d = read_json(file_location)$params$dates[[1]]$startDate
  if (start_d == "01-01-2018"){
    year1_data = c(year1_data, site_)
  }
}

length(year1_data)



test = list.files('../../www/site_data/')
length(test)

subset(cams_, cams_$site != 'asa')

setdiff(cams_$site, test)

'../../www/site_data/NEON.D01.BART.DP1.00033/data_layers/ndvi/tera/NEON-D01-BART-DP1-00033-NDVI-v6-tera-sinu-request.json'

```



```{r}
all_sites = cameras$Sitename


# Function and example to grab all the rows from a vector of phenocams like priority_cams
get_phenocam_site_row = function(names, phenocam_df){
  selected_phenocam_df = data.frame()
  for (name in names){
    row = (subset(phenocam_df, phenocam_df$Sitename == name))
    selected_phenocam_df = rbind(selected_phenocam_df, row)
  }
  return (selected_phenocam_df)
}
get_phenocam_site_row('harvard', cameras)

# Search for sites in site list
all_sites[grepl('jer', all_sites)]

# Build high priority list of phenocam sites PIs from Andrew for email functionality
priority_cams = c('harvard', 'harvardbarn', 'harvardbarn2', 'harvardblo', 'harvardfarmnorth', 'harvardfarmsouth', 'harvardgarden', 'harvardhemlock', 'harvardhemlock2', 'harvardlph',
                  'morganmonroe', 'morganmonroe2', 
                  'proctor',
                  'uiefmaize', 'uiefmiscanthus', 'uiefprairie', 'uiefswitchgrass',
                  'butte',
                  'bartlett', 'bartlettir',
                  'howland1', 'howland2',
                  'kamuela',
                  'woodshole',
                  'oregonMP',
                  'tonzi',
                  'vaira',
                  'lethbridge',
                  'missouriozarks',
                  'turkeypointdbf', 'turkeypointenf02', 'turkeypointenf39', 'turkeypointenf74',
                  'alligatorriver',
                  'konza',
                  'southerngreatplains',
                  'willowcreek',
                  'kendall',
                  'westpond',
                  'arbutuslake',
                  'burnssagebrush',
                  'kansas',
                  'merbleue',
                  'niwot3',
                  'downerwoods',
                  'uwmfieldsta',
                  'bostoncommon',
                  'dukehw',
                  'worcester',
                  'silverton',
                  'twitchell',
                  'gcesapelo',
                  'laurentides',
                  'umichbiological', 'umichbiological2',
                  'usmpj', 'sevilletagrass', 'sevilletashrub',
                  'jasperridge',
                  'coweeta',
                  'ibp', 'ibp0',
                  'jerbajada'
                  )

# check to see if sites are in all_sites list
priority_cams %in% all_sites

# Create the csv to send to andrew and katharyn
priority_phenocam_df = get_phenocam_site_row(priority_cams, cameras)
priority_phenocam_df_contacts = priority_phenocam_df %>% select(Sitename, contact1, contact2, date_first, date_last)
priority_phenocam_df_contacts[grep(c('turkeypoint'), priority_phenocam_df_contacts$Sitename),]$contact2 = 'Eric Beamesderfer <beamesde AT mcmaster DOT ca>'
write.csv(x = priority_phenocam_df_contacts, file = '/users/kenns/downloads/PI_priority_phenocams.csv', row.names = FALSE)
read.csv('/users/kenns/downloads/PI_priority_phenocams.csv')


# check to see what sites already have ndvi/evi/td data tasks created
ndvi = tasks[grep(c('NDVI_v6_aqua_sinu'), tasks$task_name),] %>% select(task_name, user_id)
ndvi[,'task_name'] = as.character(strsplit(ndvi[,'task_name'], '_NDVI_v6_aqua_sinu'))

needs_lc = c()
sites_without_any_tasks    = c()
good_to_go  = c()
needs_all_but_lc = c()
for (site in priority_cams){
  if (dim(subset(ndvi, ndvi$task_name == site))[1]==1){
    if (site %in% cached_lc_names){
      good_to_go = c(good_to_go, site)
    }else {
      needs_lc = c(needs_lc, site)
    }
  }else{
    if (site %in% cached_lc_names){
      needs_all_but_lc = c(needs_all_but_lc, site)
    }else {
      sites_without_any_tasks = c(sites_without_any_tasks, site)
    }
  }
}


landcover_tasks_to_submit = setdiff(needs_lc, cached_lc_names)


need_all_but_lc = setdiff(sites_without_any_tasks, cached_lc_names)


tasks[grep(c('NDVI_v6_aqua_sinu'), tasks$task_name),]

```

```{r}
ndvi_tera = ready_tasks[grep(c('NDVI_v6_tera_sinu'), ready_tasks$task_name),]
cache_ndvi_tera = ndvi_tera %>% select('task_id','task_name')


```

submit tasks
```{r}
# submit_all_tasks_for_site_appeears(appeears_token=token, roi_sites=landcover_tasks_to_submit, layers_ = c('LC_sinu_nc'), test=FALSE, void_size_ = TRUE)
# submit_all_tasks_for_site_appeears(appeears_token=token, roi_sites= c('arscolesnorth'), layers_ = c('NDVI_tera_sinu', 'EVI_tera_sinu', 'NDVI_aqua_sinu', 'EVI_aqua_sinu', 'TDS_v6'), test=TRUE, void_size_ = TRUE)
submit_all_tasks_for_site_appeears(appeears_token=token, roi_sites= sites_without_any_tasks, test=TRUE, void_size_ = TRUE)
```



Submit transition dates tasks to appeears
```{r}
# layer_     = 'TDS_v6'
# source('submit_appeears_tasks.R')
# submit_appeears_tasks(appeears_token=token, roi_sites=c('acadia'), data_layer=layer_, test=TRUE)
```


submit phenocam tasks for NDVI_aqua
```{r}
# Remove acadia, kamuela (159), and kelloggcorn(162) from list
#### NDVI AQUA RUNS ##### 5/31/2019 #########
# Should be 455 sites in cams_$Sitename @ this time
# Run # 1 [2:90]   ----- already submitted 2 today (must stay under 100)
# Run # 2 [c(91:158,160,161,163:192)]
# Run # 3 [193:292]
# Run # 4 [293:392]
# Run # 5 [393:455]

#### NDVI TERA RUNS ##### 6/10/2019 #########
# Should be 455 sites in cams_$Sitename @ this time
# Run # 1 [2:101]
# Run # 2 [c(91:158,160,161,163:192)]
# Run # 3 [193:203]
# Run # 4 [204:273]
# Run # 5 [274:373]
# Run # 6 [374:459]

#### EVI AQUA RUNS ##### 6/12/2019 #########
# Should be 455 sites in cams_$Sitename @ this time
# Run # 1 [2:101]
# Run # 2 [c(102:158,160,161,163:203)]
# Run # 3 [204:303]
# Run # 4 [304:403]
# Run # 5 [404:455] (52 total)

#### EVI TERA RUNS ##### 6/12/2019 #########
# Should be 455 sites in cams_$Sitename @ this time
# Run # 1 [2:99] # wanted to save room submit a task in the ui for LandCover geotiff 2017
# Run # 2 [c(100:158,160,161,163:181)]
# Run # 3 [182:229]
# Run # 4 [230:329]
# Run # 4 [330:429]
# Run # 4 [430:459] (30 total)

roi_sites_ = cams_$Sitename[374:459]
length(cams_$Sitename)
length(roi_sites_)
layer_     = 'NDVI_tera'
source('submit_appeears_tasks.R')
submit_appeears_tasks(appeears_token=token, roi_sites=roi_sites_, data_layer=layer_, test=TRUE)
```








################################################################################
misc
################################################################################

# check number of tasks for ndvi/aqua ndvi/tera evi/aqua and evi/tera
```{r}
ndvi_aqua_tasks = tasks[grep(c('NDVI_v6_aqua'), tasks$task_name),]$task_name

names = c()
for (x in ndvi_aqua_tasks){
  ele = strsplit(x, split = '_', fixed=TRUE)
  names = c(names, ele[[1]][1])
}

names
cams_$Sitename
m = match(cams_$Sitename,names)
# Show extra sites
cams_$Sitename[is.na(m)]
# Results: 6/26/2019
# "arsspltarc2" "hwmo1"       "hwmo2"       "hwmo3"  

elements = strsplit(task_name_, split = '_', fixed=TRUE)
element_length = length(elements[[1]])

print (tasks[grep(c('NDVI_v6_aqua'), tasks$task_name),])
print ((tasks[grep(c('NDVI_v6_tera'), tasks$task_name),]))
print ((tasks[grep(c('EVI_MOD13Q1_v6_aqua'), tasks$task_name),]))
print ((tasks[grep(c('EVI_MOD13Q1_v6_tera'), tasks$task_name),]))


# print ((tasks[grep(c('hwmo'), tasks$task_name),]))
# tasks[grep(c('EVI_MOD13Q1_v6_aqua'), tasks$task_name),]
```


Check to see how many phenocam sites we have with ROIS
```{r}
# Sanity check
rois            = jsonlite::fromJSON('https://phenocam.sr.unh.edu/api/roilists/?format=json&limit=2000')
phenocam_roi_df = rois$results %>% distinct(site,lat,lon)
# These should be the same
print (dim(phenocam_roi_df)[1])
print (dim(cams_)[1])
# Last check they were both 455 @ 5/31/2019
```

Take a look at the NDVI tasks in AppEEARS
```{r}
ndvi_tasks = tasks[grep(c('NDVI_v6'), tasks$task_name),]
length(unique(ndvi_tasks$task_name))
print (length(cams_$Sitename))

sites_ = paste(cams_$Sitename, collapse='|')
data_appeears = ndvi_tasks[grep(c(sites_), ndvi_tasks$task_name),]
data_appeears[,8:dim(data_appeears)[2]]
```

Submit tasks
```{r}
roi_sites_ = 
layer_     = 'NDVI_aqua'
submit_appeears_tasks_rmd(appeears_token=token, roi_sites=roi_sites_, data_layer='NDVI_tera', test=TRUE)

```

































