---
title: "submit_appeears_tasks.Rmd"
author: "K. Enns"
date: "5/31/2019"
output: html_document
---

##Submitting tasks to AppEEARS using the submit_appeears_tasks.R script

Get token for AppEEARS
```{r}
####################################################################################
# GO RUN global.R for variables and libraries required in this RMD file
####################################################################################

# devtools::install_github("ennsk/AppEEARS4R")
library(jsonlite)
library(appeears)
library(httr)
username = ''
password = ''

token_response = appeears::appeears_start_session(username,password)
rm(password)
```
View all AppEEARS tasks under user
```{r}
token         = paste("Bearer", token_response$token)
response      = GET("https://lpdaacsvc.cr.usgs.gov/appeears/api/task", add_headers(Authorization = token))
task_response = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
tasks = jsonlite::fromJSON(txt=task_response)
# tasks = tasks %>% distinct(task_id,task_name)
tasks[,2:dim(tasks)[2]]
```

Submit transition dates tasks to appeears
```{r}
layer_     = 'TDS_v6'
source('submit_appeears_tasks.R')
submit_appeears_tasks(appeears_token=token, roi_sites=c('acadia'), data_layer=layer_, test=FALSE)
```

Downloadj transition date task for acadia
```{r}
# download_bundle_file(site_task_id_ = 'dbed8c3e-4776-429c-86b0-42474ae33fc5' , filepath_ = '/users/kenns/downloads/')
tds_brick = raster::brick('/users/kenns/downloads/MCD12Q2.006_500m_aid0001.nc', varnames)
names(tds_brick)
```

submit phenocam tasks for NDVI_aqua
```{r}
# Remove acadia, kamuela (159), and kelloggcorn(162) from list
#### NDVI AQUA RUNS ##### 5/31/2019 #########
# Should be 455 sites in cams_$Sitename @ this time
# Run # 1 [2:90]   ----- already submitted 2 today (must stay under 100)
# Run # 2 [c(91:158,160,161,163:192)]
# Run # 3 [193:292]
# Run # 4 [293:392]
# Run # 5 [393:455]

#### NDVI TERA RUNS ##### 6/10/2019 #########
# Should be 455 sites in cams_$Sitename @ this time
# Run # 1 [2:101]
# Run # 2 [c(91:158,160,161,163:192)]
# Run # 3 [193:203]
# Run # 4 [204:273]
# Run # 5 [274:373]
# Run # 6 [374:459]

#### EVI AQUA RUNS ##### 6/12/2019 #########
# Should be 455 sites in cams_$Sitename @ this time
# Run # 1 [2:101]
# Run # 2 [c(102:158,160,161,163:203)]
# Run # 3 [204:303]
# Run # 4 [304:403]
# Run # 5 [404:455] (52 total)

#### EVI TERA RUNS ##### 6/12/2019 #########
# Should be 455 sites in cams_$Sitename @ this time
# Run # 1 [2:99] # wanted to save room submit a task in the ui for LandCover geotiff 2017
# Run # 2 [c(100:158,160,161,163:181)]
# Run # 3 [182:229]
# Run # 4 [230:329]
# Run # 4 [330:429]
# Run # 4 [430:459] (30 total)

roi_sites_ = cams_$Sitename[374:459]
length(cams_$Sitename)
length(roi_sites_)
layer_     = 'NDVI_tera'
source('submit_appeears_tasks.R')
submit_appeears_tasks(appeears_token=token, roi_sites=roi_sites_, data_layer=layer_, test=TRUE)
```








################################################################################
misc
################################################################################

# check number of tasks for ndvi/aqua ndvi/tera evi/aqua and evi/tera
```{r}
ndvi_aqua_tasks = tasks[grep(c('NDVI_v6_aqua'), tasks$task_name),]$task_name

names = c()
for (x in ndvi_aqua_tasks){
  ele = strsplit(x, split = '_', fixed=TRUE)
  names = c(names, ele[[1]][1])
}

names
cams_$Sitename
m = match(cams_$Sitename,names)
# Show extra sites
cams_$Sitename[is.na(m)]
# Results: 6/26/2019
# "arsspltarc2" "hwmo1"       "hwmo2"       "hwmo3"  

elements = strsplit(task_name_, split = '_', fixed=TRUE)
element_length = length(elements[[1]])

print (tasks[grep(c('NDVI_v6_aqua'), tasks$task_name),])
print ((tasks[grep(c('NDVI_v6_tera'), tasks$task_name),]))
print ((tasks[grep(c('EVI_MOD13Q1_v6_aqua'), tasks$task_name),]))
print ((tasks[grep(c('EVI_MOD13Q1_v6_tera'), tasks$task_name),]))


# print ((tasks[grep(c('hwmo'), tasks$task_name),]))
# tasks[grep(c('EVI_MOD13Q1_v6_aqua'), tasks$task_name),]
```


Check to see how many phenocam sites we have with ROIS
```{r}
# Sanity check
rois            = jsonlite::fromJSON('https://phenocam.sr.unh.edu/api/roilists/?format=json&limit=2000')
phenocam_roi_df = rois$results %>% distinct(site,lat,lon)
# These should be the same
print (dim(phenocam_roi_df)[1])
print (dim(cams_)[1])
# Last check they were both 455 @ 5/31/2019
```

Take a look at the NDVI tasks in AppEEARS
```{r}
ndvi_tasks = tasks[grep(c('NDVI_v6'), tasks$task_name),]
length(unique(ndvi_tasks$task_name))
print (length(cams_$Sitename))

sites_ = paste(cams_$Sitename, collapse='|')
data_appeears = ndvi_tasks[grep(c(sites_), ndvi_tasks$task_name),]
data_appeears[,8:dim(data_appeears)[2]]
```

Submit tasks
```{r}
roi_sites_ = 
layer_     = 'NDVI_aqua'
submit_appeears_tasks_rmd(appeears_token=token, roi_sites=roi_sites_, data_layer='NDVI_tera', test=TRUE)

```

































