---
title: "Animate PhenoCam"
author: "K Duffy"
date: "2/18/2020"
output: html_document
---

First load the required R packages
```{r}
library(animation)
library(phenocamapi)
library(lubridate)
library(jpeg)
```

If you don't have FFmpeg, you'll need to git clone it or install it here: http://ffmpeg.org/download.html

Here I've started with ibp grass because we were wondering if that signal was 'real'.  You can sub any site/PFT combo.

First I'll use the phenocamapi package to see which years are available:

```{r}
cameras=get_phenos()
```
```{r}
site <-'NEON.D15.ONAQ.DP1.00033' # phenocam site name
Years <- 2019 # vector of years to make the animation
vegType <- 'GR' # vegetation type DB = deciduous broadloeaf
roiID <- 1000  # ROI ID 
```
Then we create an empty directory same as the site name to later download the images into this directory.
```{r}
#create a new folder to download the midday images
dir.create('NEON.D15.ONAQ.DP1.00033', showWarnings = FALSE)
```
Obtain the timeseries
#getting the timeseries from the phenocam server
```{r}
gcc_ts <- get_pheno_ts(site, 
                       vegType = vegType, 
                       roiID = roiID, 
                       type = '3day')
gcc_ts_sh <- get_pheno_ts(site, 
                       vegType = 'SH', 
                       roiID = roiID, 
                       type = '3day')
```

```{r}
#organizing columns
gcc_ts[, month:=month(YYYYMMDD)] # extracting month from the date
gcc_ts[, YYYYMMDD:=as.Date(YYYYMMDD)] # convert to the right format
gcc_ts[,midday_url:=sprintf('https://phenocam.sr.unh.edu/data/archive/%s/%04d/%02d/%s', 
                            site, year, month, midday_filename)] #making the URL of midday images
gcc_ts_sh[, month:=month(YYYYMMDD)] # extracting month from the date
gcc_ts_sh[, YYYYMMDD:=as.Date(YYYYMMDD)] # convert to the right format
gcc_ts_sh[,midday_url:=sprintf('https://phenocam.sr.unh.edu/data/archive/%s/%04d/%02d/%s', 
                            site, year, month, midday_filename)] #making the URL of midday images
```


# organizing the data into a new data.table including the URL, date and GCC90 values
```{r}
gcc_file_tbl <- gcc_ts[year%in%(Years),.(midday_url, YYYYMMDD, gcc_90)] 
gcc_file_tbl_sh<- gcc_ts_sh[year%in%(Years),.(midday_url, YYYYMMDD, gcc_90)] 
gcc_file_tbl$gcc_sh=gcc_file_tbl_sh$gcc_90
```

# creating the destination filename to download each midday image
```{r}
gcc_file_tbl[,midday_dest:=paste0(site, '/', basename(midday_url))] 
gcc_file_tbl <- na.omit(gcc_file_tbl) # removing the NA values


#gcc_file_tbl <- gcc_file_tbl[month(YYYYMMDD)==5]

```
Download all the selected midday images
#downloading midday files
```{r}
mapply(
  function(x){
    dest <- paste0(site, '/', basename(x))
    if(file.exists(dest)) {
      message(dest, ' ', 'already exists!')
      return()
    }
    try(download.file(x, dest))
  },
  gcc_file_tbl$midday_url)
```
*Note: Every image for a couple of years takes a long time to run.  Options: choose fewer years or every 5 days?

Making the video
# a simple function to plot midday image given an index and corresponding gcc timeseries upto that date
```{r}
show_midday <- function(i){
  
  par(fig = c(0,1, .3, 1),  mar=c(0,0,0,0), bg = '#000000')  
  plot(0:1,0:1, type='n', axes= FALSE, xlab= '', ylab = '')
  
  img <- readJPEG(gcc_file_tbl$midday_dest[i])
  rasterImage(img, 0, 0, 1, 1)
  mtext('Greenup Seasonality at ONAQ', col = '#51fddc')
  
  par(fig = c(0,1, 0, 0.3), new = T, mar=c(2,2,0,0))  
  plot(gcc_file_tbl$YYYYMMDD[1:i], 
       gcc_file_tbl$gcc[1:i], 
       bty ='n', 
       type = 'l',
       lwd = 2,
       cex.axis =1.5,
       col = '#51fddc', 
       col.axis = '#51fddc',
       xlim = range(gcc_file_tbl$YYYYMMDD),
       ylim = range(gcc_file_tbl$gcc, na.rm = TRUE)
  )
    plot(gcc_file_tbl$YYYYMMDD[1:i], 
       gcc_file_tbl$gcc_sh[1:i], 
       bty ='n', 
       type = 'l',
       lwd = 2,
       cex.axis =1.5,
       col = '#51b5fd', 
       col.axis = '#51fddc',
       xlim = range(gcc_file_tbl$YYYYMMDD),
       ylim = range(gcc_file_tbl$gcc, na.rm = TRUE)
  )
  mtext('Canopy Greenness', side = 2, line = 0, col = '#51fddc', cex = 2, font = 2)
  
  points(gcc_file_tbl$YYYYMMDD[i], 
         gcc_file_tbl$gcc[i], 
         pch = 19,
         col = '#ca5f63')
}

# dummy
gcc_file_tbl[,gcc:=gcc_90]



#number of image
n <- nrow(gcc_file_tbl)
```

```{r}
show_midday2 <- function(i){
  
  par(fig = c(0,1, .3, 1),  mar=c(0,0,0,0), bg = '#000000')  
  plot(0:1,0:1, type='n', axes= FALSE, xlab= '', ylab = '')
  
  img <- readJPEG(gcc_file_tbl$midday_dest[i])
  rasterImage(img, 0, 0, 1, 1)
  mtext('Greenup Seasonality at ONAQ', col = '#f2f3f4')
  
  par(fig = c(0,1, 0, 0.3), new = T, mar=c(2,2,0,0))  
  plot(gcc_file_tbl$YYYYMMDD[1:i], 
       gcc_file_tbl$gcc[1:i], 
       bty ='n', 
       type = 'l',
       lwd = 2,
       cex.axis =1.5,
       col = '#51fddc', 
       col.axis = '#f2f3f4',
       xlim = range(gcc_file_tbl$YYYYMMDD),
       ylim = range(gcc_file_tbl$gcc, na.rm = TRUE)
  )
  lines(gcc_file_tbl$YYYYMMDD[1:i], 
       gcc_file_tbl$gcc_sh[1:i], col='#51b5fd')
  legend("topright",
c("Invasive Cheatgrass","Native Shrubs"),
fill=c('#51fddc','#51b5fd'), text.col ='#f2f3f4' , cex = 2)
    
  mtext('Vegetation Greenness', side = 3, line = 0, col = '#f2f3f4', cex = 2, font = 2)
  
  points(gcc_file_tbl$YYYYMMDD[i], 
         gcc_file_tbl$gcc[i], 
         pch = 19,
         col = '#ca5f63')
}

# dummy
gcc_file_tbl[,gcc:=gcc_90]



#number of image
n <- nrow(gcc_file_tbl)
```

# make the animation using the saveVideo animation file
```{r}
saveVideo(interval = 0.25, # animation interval in seconds
          ani.width = 1000, # image width in pixels
          ani.height = 900,# image height in pixels
          ani.res = 75, # resolution, not important here
          video.name = paste0(site, '.mp4'),
          
          for(i in seq(20, 110, by = 1)){
            cat(i, '\n')
            show_midday2(i)
          })
```


if FFmpeg is cranky or hard, you could always use some software like iMovie etc to generate an .mp4.