---
title: "Animate PhenoCam"
author: "K Duffy"
date: "2/18/2020"
output: html_document
---

First load the required R packages
```{r}
library(animation)
library(phenocamapi)
library(lubridate)
library(jpeg)
```

If you don't have FFmpeg, you'll need to git clone it or install it here: http://ffmpeg.org/download.html

Here I've started with ibp grass because we were wondering if that signal was 'real'.  You can sub any site/PFT combo.

First I'll use the phenocamapi package to see which years are available:

```{r}
# cameras=get_phenos()
cameras = cams_
```

```{r}
site <-'ibp' # phenocam site name
Years <- 2019 # vector of years to make the animation
vegType <- 'GR' # vegetation type DB = deciduous broadloeaf
roiID <- 1000  # ROI ID 
```

Then we create an empty directory same as the site name to later download the images into this directory.
```{r}
#create a new folder to download the midday images
dir.create(site, showWarnings = FALSE)
```

Obtain the timeseries
  - getting the timeseries from the phenocam server
```{r}
gcc_ts <- get_pheno_ts(site, 
                       vegType = vegType, 
                       roiID = roiID, 
                       type = '1day')
```

```{r}
#organizing columns
gcc_ts[, month:=month(YYYYMMDD)] # extracting month from the date
gcc_ts[, YYYYMMDD:=as.Date(YYYYMMDD)] # convert to the right format
gcc_ts[,midday_url:=sprintf('https://phenocam.sr.unh.edu/data/archive/%s/%04d/%02d/%s', 
                            site, year, month, midday_filename)] #making the URL of midday images

```


# organizing the data into a new data.table including the URL, date and GCC90 values
```{r}
gcc_file_tbl <- gcc_ts[year%in%(Years),.(midday_url, YYYYMMDD, gcc_90)] 
```

# creating the destination filename to download each midday image
```{r}
gcc_file_tbl[,midday_dest:=paste0(site, '/', basename(midday_url))] 
gcc_file_tbl <- na.omit(gcc_file_tbl) # removing the NA values
```



```{r}
library(magick)
library(imager)
test_midday_f = gcc_file_tbl$midday_dest[1]
test_roi_f_png    = 'ibp/ibp_roi_mask_GR.png'

mask_png = magick::image_read(test_roi_f_png)
pc_img = magick::image_read(test_midday_f)
class(pc_img)

mask_png_line = mask_png %>%
  image_edge(radius = 2) %>%
  image_convert(type = 'grayscale') %>%
  image_negate() 

mask_jpg = image_convert(mask_png_line, 'jpeg')

mask_final = mask_jpg %>%
  image_quantize(max = 256,colorspace = "rgb") %>% image_background(color = 'none', flatten = TRUE)
# mask_final = mask_jpg

pc_img_final = pc_img %>% image_annotate("A", color = "black",strokecolor = 'white', size = 170, location =paste0("+",width_-200,"+50"))
plot(pc_img_final)

image_write(mask_final, path = 'mask.jpg', format = 'jpg')
image_write(pc_img_final, path = 'img.jpg', format = 'jpg')

plot(mask_final)

?image_annotate

```

Create image with highlight of ROI on top of image
```{r}
# Read in the mask object
jpg_mask  = imager::load.image('mask.jpg')
# Read in the phenocam image
jpg_img  = imager::load.image(gcc_file_tbl$midday_dest[1])

plot(jpg_img)
highlight(jpg_mask, col = 'blue', lwd=.4) 

```

Try to save out the highlighted image
```{r}
jpg_img = imager::load.image('img.jpg')
grDevices::jpeg('tes1t.jpg', height =height(jpg_img), width = width(jpg_img))
raster::plot(jpg_img, axes = FALSE, box = FALSE)
imager::highlight(jpg_mask, col = 'blue', lwd=.4) 
grDevices::dev.off()


```


Build the images and save them out into a new directory called pc_roi_imgs
```{r}

# Create directory to store the phenocam/roi images for each site
dir.create('pc_roi_imgs', showWarnings = FALSE)
dir.create('pc_roi_imgs/masks', showWarnings = FALSE)
dir.create('pc_roi_imgs/final_masks', showWarnings = FALSE)
dir.create('pc_roi_imgs/imgs', showWarnings = FALSE)
dir.create('pc_roi_imgs/final_imgs', showWarnings = FALSE)
# Get the sites for the paper
sites_df = read.csv('jornada_sites.csv', stringsAsFactors = FALSE)[1:9,] # Removing one of the NEON.d14.JORN.DP1 sites
site_labels = c('A','B','C','D','E','F','G','H','I')
montage_name = 'Phenosynthesis'
# Sites to add (use a total of 9 for 3x3 to work)
jorn_sites = sort(sites_df$Name)
# jorn_sites = sort(c('acadia','alleypond','arbutuslake','cafboydsouthltar01', 'twolcsh',
#   'unca','bernatchez','bartlett','niwot5'))


# Loop through all the sites to build out the images
count = 1
for (site_ in jorn_sites[1]){
  print (site_)
  roiID = 1000
  label = site_labels[count]
  print (label)
  count = count + 1
  doy_ = 200
  
  
  site_cams_row = subset(cams_, cams_$site == site_)
  site_rois_row = subset(roi_files, roi_files$site == site_)
  pfts          = unique(site_rois_row$roitype)
  
  # Select 1 mid day image
  gcc_ts = get_pheno_ts(site_, vegType = pfts[1], roiID = roiID, type = '3day')
  gcc_ts[, month:=month(YYYYMMDD)] # extracting month from the date
  gcc_ts[, YYYYMMDD:=as.Date(YYYYMMDD)] # convert to the right format
  gcc_ts[,midday_url:=sprintf('https://phenocam.sr.unh.edu/data/archive/%s/%04d/%02d/%s', 
                              site_, year, month, midday_filename)] #making the URL of midday images
  gcc_ts = as.data.frame(gcc_ts, stringsAsFactors = FALSE)

  years = rev(unique(gcc_ts$year))[1]
  # If the year is 2020 or later change the year to 2019 (we aren't using 2020 data for this paper)
  if (years > 2019){years = 2019}
  
  # Filter out rows with no image 
  gcc_ts_clean = subset(gcc_ts, gcc_ts$image_count > 1 )
  
  doys_for_this_year = subset(gcc_ts_clean, gcc_ts_clean$year == years)$doy
  closest_doy = doys_for_this_year[findInterval(doy_, doys_for_this_year)+1]
  if (is.na(closest_doy)){closest_doy = doys_for_this_year[length(doys_for_this_year)]}
  
  this_midday_row = subset(gcc_ts_clean, gcc_ts_clean$year == years & gcc_ts_clean$doy == closest_doy)
  img_download_url = this_midday_row$midday_url
  fname = paste0('pc_roi_imgs/imgs/',this_midday_row$midday_filename)
  print (fname)
  download.file(img_download_url, fname)
  
  # Creating final directory to save out the final images
  final_doy_dir = paste0('pc_roi_imgs/',montage_name,'_doy_',doy_, '/')
  dir.create(final_doy_dir, showWarnings = FALSE)
  
  # Import img
  pc_img   = magick::image_read(fname)
  pc_img_final = pc_img %>% image_annotate(label, color = "black", size = 170, strokecolor = 'white', location =paste0("+",width_-200,"+10"))
  final_img_f = paste0('pc_roi_imgs/final_imgs/', site_, '.jpg')
  image_write(pc_img_final, path = final_img_f, format = 'jpg')
  
  # Create output directory for final masks per site
  site_mask_dir = paste0('pc_roi_imgs/final_masks/',site_,'/')
  dir.create(site_mask_dir, showWarnings = FALSE)
  
  # Load in final img 
  final_img_jpg = imager::load.image(final_img_f)
  grDevices::jpeg(paste0(final_doy_dir, site_,'_',years,'_',doy_,'_final.jpg'), height =height(final_img_jpg), width = width(final_img_jpg))
  raster::plot(final_img_jpg, axes = FALSE, box = FALSE)
  
  # Download the masks for each site
  for (roi_ in pfts){
    overlay_roi = get_roi_url(name = site_, pft_abr = roi_)
    mask_name = paste0('pc_roi_imgs/masks/', site_,'_',roi_,'.png')
    print (mask_name)
    mask_url = get_roi_url(name = site_, pft_abr = roi_)
    print (mask_url)
    download.file(mask_url, mask_name)
    
    # Read in the downloaded mask.png
    mask_png = magick::image_read(mask_name)
    
    # Create the mask outline using image_edge
    mask_png_line = mask_png %>%
    image_edge(radius = 2) %>%
    image_convert(type = 'grayscale') %>%
    image_negate() 
    
    # Convert from png to jpeg
    mask_jpg = image_convert(mask_png_line, 'jpeg')
    
    # Create a final mask
    mask_final = mask_jpg %>%
      image_quantize(max = 256,colorspace = "rgb") %>% image_background(color = 'none', flatten = TRUE)
    
    # Write out new mask jpg 
    final_mask_f = paste0(site_mask_dir, site_,'_',roi_,'.jpg')
    image_write(mask_final, path = final_mask_f, format = 'jpg')
    
    # Set roi color
    if (roi_ == 'GR'){
      color_ = '#CD6839'
    }else if (roi_ == 'SH'){
      color_ = '#20b2aa'
    }else if (roi_ == 'NV'){
      color_ = '#CDC9C9'
    }else{
      color_ = 'white'
    }
    
    # Read in mask and highlight it
    this_roi_mask = imager::load.image(mask_name)
    imager::highlight(this_roi_mask, col = color_, lwd= 6)
  }

  grDevices::dev.off()
}

```

Build grid and save out all images in a 3x3
```{r}
these_files = sort(list.files(final_doy_dir))
plot1 = readJPEG(paste0(final_doy_dir, these_files[1]))
plot2 = readJPEG(paste0(final_doy_dir, these_files[2]))
plot3 = readJPEG(paste0(final_doy_dir, these_files[3]))
plot4 = readJPEG(paste0(final_doy_dir, these_files[4]))
plot5 = readJPEG(paste0(final_doy_dir, these_files[5]))
plot6 = readJPEG(paste0(final_doy_dir, these_files[6]))
plot7 = readJPEG(paste0(final_doy_dir, these_files[7]))
plot8 = readJPEG(paste0(final_doy_dir, these_files[8]))
plot9 = readJPEG(paste0(final_doy_dir, these_files[9]))

library(grid)
library(gridExtra)
whole_p = grid.arrange(rasterGrob(plot1),rasterGrob(plot2),rasterGrob(plot3),
  rasterGrob(plot4),rasterGrob(plot5),rasterGrob(plot6),
  rasterGrob(plot7),rasterGrob(plot8),rasterGrob(plot9),ncol=3)

grDevices::jpeg(paste0('pc_roi_imgs/', doy_, '_', montage_name,'.jpg'), height =height(final_img_jpg), width = width(final_img_jpg))
raster::plot(whole_p, axes = FALSE, box = FALSE)
grDevices::dev.off()
```





























































































<!-- add ROI mask (png) over a midday phenocam image (jpg) -->
<!-- ```{r} -->
<!-- test_midday_f = gcc_file_tbl$midday_dest[1] -->
<!-- test_roi_f    = 'ibp/ibp_roi_mask_GR.png' -->
<!-- test_roi_f_jpg = "ibp_roi_mask_GR.jpg" -->
<!-- test_roi_f_tif = 'ibp_GR_1000_01.tif' -->




<!-- overlay_roi = get_roi_url(name = 'ibp', pft_abr = 'GR') -->

<!-- # Download overlay -->
<!-- # download.file(overlay_roi, test_roi_f) -->

<!-- library(png) -->
<!-- img_mask = readPNG(test_roi_f) -->
<!-- library(jpeg) -->
<!-- writeJPEG(img_mask, target = test_roi_f_jpg, quality = 1) -->

<!-- library(magick) -->
<!-- mask = magick::image_read(test_roi_f_tif) -->
<!-- pc_img = magick::image_read(test_midday_f) -->
<!-- mask -->


<!-- img = c(pc_img, mask) -->
<!-- print (mask) -->
<!-- magick::image_combine(img) -->
<!-- ?image_combine -->



<!-- library(imager) -->
<!-- im      = load.image(test_midday_f) -->
<!-- im_mask = load.image(test_roi_f_jpg) -->

<!-- fg <- c(510,521,670,671 ) -->
<!-- #Background -->
<!-- bg <- c(791,   28, 1020,  194 ) -->
<!-- #Corresponding pixel sets -->
<!-- px.fg <- ((Xc(im) %inr% fg[c(1,3)]) & (Yc(im) %inr% fg[c(2,4)])) -->
<!-- px.bg <- ((Xc(im) %inr% bg[c(1,3)]) & (Yc(im) %inr% bg[c(2,4)])) -->

<!-- plot(im) -->
<!-- plot(im_mask) -->

<!-- highlight(im_mask, col = 'blue') -->
<!-- highlight(px.fg) -->
<!-- highlight(px.bg,col="blue") -->

<!-- ??imager -->

<!-- im -->
<!-- im_mask -->
<!-- ``` -->


<!-- ```{r} -->
<!-- bitmap <- mask %>%  -->
<!--   image_edge(radius = 1) %>% -->
<!--   # image_channel(channel = 'lightness') %>% -->
<!--   image_convert(type = 'grayscale') %>% -->
<!--   image_quantize(2, colorspace = 'gray') %>% -->
<!--   image_negate() %>% -->
<!--   image_reducenoise(radius = 1) %>% -->
<!--   image_data(channels = 'gray') -->

<!-- ?image_quantize -->
<!-- ?image_combine -->
<!-- ?image_data -->

<!-- print(bitmap) -->

<!-- img = c(pc_img, bitmap) -->
<!-- magick::image_combine(img) -->
<!-- ``` -->


<!-- ```{r} -->
<!-- library(xROI) -->

<!-- #read a mask file in TIFF format -->
<!-- m <- tiff::readTIFF( test_roi_f_tif) -->
<!-- str(m) -->

<!-- #plot the mask in black color -->
<!-- addMask(m, add = FALSE) -->

<!-- #add the same mask in the red color to the existing plot -->
<!-- plot(im) -->
<!-- addMask(m, add = TRUE, col = 'red') -->


<!-- mm = image_read(m) -->
<!-- m %>% image_edge(radius = 1)  -->

<!-- ``` -->














