---
title: "site_point_extraction.Rmd"
author: "K. Enns"
date: "2/18/2020"
output: html_document
---

#

Run Global in main directory of project
```{r}
#######################################################
# Be sure to run global.R before running this script
#######################################################
```

Read in CSV
```{r}
jornada_sites_df = read.csv('jornada_sites.csv', stringsAsFactors = FALSE)
jornada_sites_df
```

Subset cams_ dataframe using the site names from the jornada_sites.csv
```{r}
sites_ = jornada_sites_df$Name
jorn_cams_df = subset(cams_, cams_$site %in% sites_)
jorn_cams_df
```

Grab the modis pixel that the phenocam site lives
```{r}
site_name = sites_[sample(1:length(sites_), 1)]
print (site_name)

site_row = subset(jorn_cams_df, jorn_cams_df$site == site_name)

# Extract lat and lon from site data
site_lat = site_row$lat
site_lon = site_row$lon

###############################################################################################################################
# Note: Be sure to run app and go to this site and enter analyzer mode.  This will download the MODIS NDVI layer we can use to 
#    calculate the pixel boundaries for analysis
###############################################################################################################################

ndvi_dir   = paste0('../../www/site_data/',site_name,'/data_layers/ndvi/tera/')
ndvi_files = list.files(ndvi_dir)
ndvi_tera_name   = ndvi_files[grepl('MOD13Q1.006_250m_aid0001.nc', ndvi_files)]
ndvi_tera_path   = paste0(ndvi_dir, ndvi_tera_name)
ndvi_tera_brick  = raster::brick(ndvi_tera_path, varname='_250m_16_days_NDVI', crs=sinu_crs)
ndvi_raster_t    = raster::subset(ndvi_tera_brick, 1)
ndvi_raster_merc = projectRaster(from = ndvi_raster_t, crs = merc_crs, res = res(ndvi_raster_t))

# Building Landcover layer and color pallette for specific pft composition in clipped raster
lat_wgs = site_lat
lng_wgs = site_lon
# from wgs to sinusoidal
pt_sinu = from_crs1_to_crs2_lon_lat(lon_ = lng_wgs, lat_ = lat_wgs, from_crs = wgs_crs, to_crs = sinu_crs)
lat_sin = pt_sinu@coords[2]
lng_sin = pt_sinu@coords[1]
# from wgs to web mercator
pt_merc = from_crs1_to_crs2_lon_lat(lon_ = lng_wgs, lat_ = lat_wgs, from_crs = wgs_crs, to_crs = merc_crs)
lat_merc = pt_merc@coords[2]
lng_merc = pt_merc@coords[1]

ndvi_r_m_c = crop_raster(lat_merc, lng_merc, ndvi_raster_merc, height = 10000, width = 10000, crs_str = merc_crs)
ndvi_r_m_c
```

Display NDVI raster and site
```{r}
# Set colors and legend values
colors = c('red','green')
at     = seq(0, maxValue(ndvi_r_m_c), length.out = 10)
cb     = colorBin(palette = colors, bins = at, domain = at)
# Build map
leaflet('map') %>% addTiles() %>% addRasterImage(ndvi_r_m_c, colors = cb) %>% addLegend(pal = cb, values = at) %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 5, color = 'black', weight=2, opacity = 1, label = site_name)
```


Build 5x5 grid of NDVI to use for analysis
```{r}
source('../../functions/geospatial.R')

# Set colors and legend values
colors = c('red','green')
at     = seq(0, maxValue(ndvi_raster_merc), length.out = 10)
cb     = colorBin(palette = colors, bins = at, domain = at)

resolution = res(ndvi_raster_merc)[1]

s_5      = resolution *2
e_5      = as(extent(lng_merc -s_5, lng_merc +s_5, lat_merc -s_5, lat_merc +s_5), 'SpatialPolygons')
crs(e_5) =  merc_crs

r_5by      = raster::crop(ndvi_raster_merc, e_5, snap='out')




# Build Map (5x5)
g_5by = build_raster_grid(r_5by, crs='merc')
leaflet() %>% addTiles() %>% addRasterImage(r_5by, colors = cb) %>% addLegend(pal = cb, values = at) %>% addPolylines(data = g_5by) %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 5, color = 'black', weight=2, opacity = 1, label = site_name)
```

Extract all the pixel center points and create a dataframe with id/lat/lng 
```{r}
# Values needed to calculate center pixels to use on analysis of netcdf data
r_         = r_5by
xmin       = xmin(extent(r_))
xmax       = xmax(extent(r_))
ymin       = ymin(extent(r_))
ymax       = ymax(extent(r_))
nrows      = nrow(r_)
ncols      = ncol(r_)
resolution = res(r_)[1]

lngs = c()
lats = c()
lng_start = xmin + .5*(resolution)
lat_start = ymax + .5*(resolution)
for (row in c(1:nrows)){
  for (col in c(1:ncols)){
    lng = lng_start + (resolution)*(col-1)
    lat = lat_start - (resolution)*(row)
    lngs = c(lngs,lng)
    lats = c(lats,lat)
  }
}
pixel_ids = c(1:(ncols*nrows))
all_site_pixels_df = data.frame(pixel_id=pixel_ids, lat = lats, lng = lngs, site='acadia')
all_site_pixels_df

pts_wgs = from_crs1_to_crs2_lon_lat(lon_ = all_site_pixels_df$lng, lat_ = all_site_pixels_df$lat, from_crs = merc_crs, to_crs = wgs_crs)
lats_wgs = pts_wgs@coords[,2]
lngs_wgs = pts_wgs@coords[,1]

```

display the centroids of the grid
```{r}
leaflet() %>% addTiles() %>% addPolylines(data = g_5by) %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 7, color = 'red', weight=3, opacity = 1, label = site_name) %>%
   addCircleMarkers(lat = lats_wgs, lng = lngs_wgs, radius = 3, color = 'grey', weight=2, opacity =1)
```


create the dataframe with sitename and centroids to give to CSP team (use case 2)
```{r}
site_name 
data.frame(site = rep(site_name, length(lats_wgs)), latitude = lats_wgs, longitude = lngs_wgs)
```

# Run all the above code in one chunk
```{r}
jornada_sites_df = read.csv('jornada_sites.csv', stringsAsFactors = FALSE)

sites_ = jornada_sites_df$Name
jorn_cams_df = subset(cams_, cams_$site %in% sites_)

final_jorns_df = data.frame(stringsAsFactors = FALSE)
for (site_name in sites_){
  print (site_name)
  site_row = subset(jorn_cams_df, jorn_cams_df$site == site_name)
  
  # Extract lat and lon from site data
  site_lat = site_row$lat
  site_lon = site_row$lon
  
  ###############################################################################################################################
  # Note: Be sure to run app and go to this site and enter analyzer mode.  This will download the MODIS NDVI layer we can use to 
  #    calculate the pixel boundaries for analysis
  ###############################################################################################################################
  
  ndvi_dir   = paste0('../../www/site_data/',site_name,'/data_layers/ndvi/tera/')
  ndvi_files = list.files(ndvi_dir)
  ndvi_tera_name   = ndvi_files[grepl('MOD13Q1.006_250m_aid0001.nc', ndvi_files)]
  ndvi_tera_path   = paste0(ndvi_dir, ndvi_tera_name)
  ndvi_tera_brick  = raster::brick(ndvi_tera_path, varname='_250m_16_days_NDVI', crs=sinu_crs)
  ndvi_raster_t    = raster::subset(ndvi_tera_brick, 1)
  ndvi_raster_merc = projectRaster(from = ndvi_raster_t, crs = merc_crs, res = res(ndvi_raster_t))
  
  # Building Landcover layer and color pallette for specific pft composition in clipped raster
  lat_wgs = site_lat
  lng_wgs = site_lon
  # from wgs to sinusoidal
  pt_sinu = from_crs1_to_crs2_lon_lat(lon_ = lng_wgs, lat_ = lat_wgs, from_crs = wgs_crs, to_crs = sinu_crs)
  lat_sin = pt_sinu@coords[2]
  lng_sin = pt_sinu@coords[1]
  # from wgs to web mercator
  pt_merc = from_crs1_to_crs2_lon_lat(lon_ = lng_wgs, lat_ = lat_wgs, from_crs = wgs_crs, to_crs = merc_crs)
  lat_merc = pt_merc@coords[2]
  lng_merc = pt_merc@coords[1]
  
  ndvi_r_m_c = crop_raster(lat_merc, lng_merc, ndvi_raster_merc, height = 10000, width = 10000, crs_str = merc_crs)
  
  # Set colors and legend values
  colors = c('red','green')
  at     = seq(0, maxValue(ndvi_r_m_c), length.out = 10)
  cb     = colorBin(palette = colors, bins = at, domain = at)
  
  source('../../functions/geospatial.R')
  
  # Set colors and legend values
  colors = c('red','green')
  at     = seq(0, maxValue(ndvi_raster_merc), length.out = 10)
  cb     = colorBin(palette = colors, bins = at, domain = at)
  
  resolution = res(ndvi_raster_merc)[1]
  
  s_5      = resolution *2
  e_5      = as(extent(lng_merc -s_5, lng_merc +s_5, lat_merc -s_5, lat_merc +s_5), 'SpatialPolygons')
  crs(e_5) =  merc_crs
  
  r_5by      = raster::crop(ndvi_raster_merc, e_5, snap='out')
  g_5by = build_raster_grid(r_5by, crs='merc')
  # Values needed to calculate center pixels to use on analysis of netcdf data
  r_         = r_5by
  xmin       = xmin(extent(r_))
  xmax       = xmax(extent(r_))
  ymin       = ymin(extent(r_))
  ymax       = ymax(extent(r_))
  nrows      = nrow(r_)
  ncols      = ncol(r_)
  resolution = res(r_)[1]
  
  lngs = c()
  lats = c()
  lng_start = xmin + .5*(resolution)
  lat_start = ymax + .5*(resolution)
  for (row in c(1:nrows)){
    for (col in c(1:ncols)){
      lng = lng_start + (resolution)*(col-1)
      lat = lat_start - (resolution)*(row)
      lngs = c(lngs,lng)
      lats = c(lats,lat)
    }
  }
  pixel_ids = c(1:(ncols*nrows))
  all_site_pixels_df = data.frame(pixel_id=pixel_ids, lat = lats, lng = lngs, site='acadia')
  all_site_pixels_df
  
  pts_wgs = from_crs1_to_crs2_lon_lat(lon_ = all_site_pixels_df$lng, lat_ = all_site_pixels_df$lat, from_crs = merc_crs, to_crs = wgs_crs)
  lats_wgs = pts_wgs@coords[,2]
  lngs_wgs = pts_wgs@coords[,1]
  this_site_df = data.frame(site = rep(site_name, length(lats_wgs)), latitude = lats_wgs, longitude = lngs_wgs)
  
  if (length(final_jorns_df)[1] == 0){
    final_jorns_df = this_site_df
  }else{
    final_jorns_df = rbind(final_jorns_df, this_site_df)
  }
  jorn_ls = leaflet() %>% addTiles() %>% addPolylines(data = g_5by) %>%
    addCircleMarkers(lat = site_lat, lng = site_lon, radius = 7, color = 'red', weight=3, opacity = 1, label = site_name) %>%
     addCircleMarkers(lat = lats_wgs, lng = lngs_wgs, radius = 3, color = 'grey', weight=2, opacity =1) %>%
      setView(lat = site_lat, lng = site_lon, zoom = 14)
  
  print (jorn_ls)
}
```

display dataframe
```{r}
final_jorns_df
write.csv(final_jorns_df, 'jornada_site_centroids.csv', row.names = FALSE)
```














