---
title: "appeears_data_analysis"
author: "K. Enns"
date: "4/3/2019"
output: html_document
---

# Download all files for NDVI data from AppEEARS and filter it using raster::brick objects
### Site and AppEEARS task ID from (K. Enns) tasks, edited by KDuffy
```{r}
library(jsonlite)
library(ncdf4)
library(ncdf4.helpers)
library(PCICt)
library(httr)
library(leaflet)
```

### Grab bundle from task id
```{r}
site_task_id = 'e106f82f-7191-4050-a8af-f142e2f981d3'
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", site_task_id, sep = ""))
bundle_response = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))

# all files in bundle
document = jsonlite::fromJSON(txt=bundle_response)
files = document$files
class(files)
```

### Getting netcdf id + other file ids from the bundle
```{r}
# csv files 
csvs      = subset(files, file_type == 'csv')
quality_lookup_id     = csvs[grep('Quality-lookup', csvs$file_name), ]$file_id
quality_statistics_id = csvs[grep('Quality-Statistics', csvs$file_name), ]$file_id
  
# Net cdf
netcdf    = subset(files, file_type == 'nc')
netcdf_id = netcdf$file_id
netcdf
```


### Download all the files from the task (NDVI, Quality Statistics, Quality Lookup, Statistics, Granule List, request, metadata, README)
```{r}
get_download_folder = function(){
  if (Sys.info()['sysname'] == 'Darwin'){
    folder = paste('/Users/', Sys.getenv('LOGNAME'),'/Downloads/', sep = '')
  }else if (Sys.info()['sysname'] == 'Windows'){
    folder = paste('C:/Downloads/', sep = '')
  }else{
    folder = ''
  }
  return (folder)
  }

filepaths = c()
filenames = c()
for (file in files$file_id){
  download_this_file = file
  # # retrieve the filename from the file_id
  bundle = jsonlite::fromJSON(bundle_response)$files
  filename = subset(bundle, bundle$file_id == download_this_file)$file_name
  # create a destination directory to store the file in
  dest_dir = get_download_folder()
  filepath = paste(dest_dir, filename, sep = '')
  print (filepath)
  filepaths = c(filepaths, filepath)
  filenames = c(filenames, filename)
  
  # write the file to disk using the destination directory and file name
  response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", site_task_id, '/', download_this_file, sep = ""),
                 write_disk(filepath, overwrite = TRUE), progress())
}
print (filepaths)
```

### Store all of the differen't downloaded files into variables
```{r}
# Netcdf for NDVI Data
ndvi_output = nc_open(filepaths[1])
# Quality lookup
ndvi_quality_lookup = read.csv(filepaths[2])
# Quality Statistics Quality Assurance
ndvi_quality_statistics = read.csv(filepaths[3])
# Statistics
ndvi_statistics = read.csv(filepaths[4])
# Granule list
ndvi_granule_list = read.delim(filepaths[5])
# Request JSON
ndvi_request_json = read_json(filepaths[6])
# Readme
ndvi_metadata = read.delim(filepaths[7])
# Readme
ndvi_readme = read.delim(filepaths[8])
```

### Read in netCDF file just downloaded above
```{r}
library(raster); library(rmarkdown); library(ncdf4); library(sp)
ndvi_output = nc_open(filepaths[1])

# Print a list of variables in file
print (attributes(ndvi_output$var)$names)

# Print a list of dimensions in file
print (attributes(ndvi_output$dim)$names)
```

## Start of the https://lpdaac.usgs.gov/sites/default/files/public/elearning/AppEEARS_NC_QualityFiltering_R.html#8_mask_by_land_cover_type example
### Extracting the NDVI and Quality layers from the netcdf (NDVI)
```{r}
# ndvi_info  = ncatt_get(ndvi_output, "_250m_16_days_NDVI")
# fillvalue = ncatt_get(ndvi_output, "_250m_16_days_NDVI", "_FillValue")$value
# ndvi_nc    = ncvar_get(ndvi_output, "_250m_16_days_NDVI")
# ndvi_qc_nc = ncvar_get(ndvi_output, "_250m_16_days_VI_Quality")  
# 
# fillvalue = ncatt_get(ndvi_output, "_250m_16_days_NDVI", "_FillValue")
# # v6_NDVI[v6_NDVI == fillvalue$value] = NA
# ndvi_crs   = ncatt_get(ndvi_output, "crs", "epsg_code")[2][[1]]
# ndvi_brick = raster::brick(filepaths[1], varname='_250m_16_days_NDVI')
# ndvi_brick_qc = raster::brick(filepaths[1], varname='_250m_16_days_VI_Quality')
# 
# 
# unique_qualities = unique(subset(ndvi_brick_qc, 5))
# 
# library(leaflet)
# leaflet() %>% addTiles() %>% addRasterImage(subset(ndvi_brick, 5))
# subset(ndvi_brick, 5)
# 
# nas_removed = reclassify(subset(ndvi_brick, 5), cbind(fillvalue$value, NA))
# 
# leaflet() %>% addTiles() %>% addRasterImage(nas_removed)
# 
# print (dim(ndvi_nc))
# print (dim(ndvi_qc_nc))
```

### Use one raster layer in the net cdf files (ndvi/qc) to remove low quality pixels
```{r}
library(raster); library(rmarkdown); library(ncdf4); library(sp); library(dplyr); library(leaflet)
ndvi_brick = raster::brick(filepaths[1], varname='_250m_16_days_NDVI')
ndvi_brick_qc = raster::brick(filepaths[1], varname='_250m_16_days_VI_Quality')
fillvalue = -3000
# Select a layer in the Raster (5th from the top)
raster_layer = 2 #Can be any value from 1 to 10 to work with cells bellow

# Use fill value to remove -3000 and change them to NA values
nas_removed = reclassify(subset(ndvi_brick, raster_layer), cbind(fillvalue, NA))
# Subset the raster by the selected raster_layer above
qualities_raster = subset(ndvi_brick_qc, raster_layer)
# Grab vector of all unique values from qualities_raster
unique_qualities = unique(qualities_raster)

# Display the qualities_raster layer 
leaflet() %>% addTiles() %>% addRasterImage(qualities_raster)

# Subset Dataframe with all Quality Types (Lookup table) by unique values present in selected raster
unique_qc_types  = subset(ndvi_quality_lookup, Value %in% unique_qualities)

# Extract all values that aren't highest quality
low_quality = subset(unique_qc_types, VI.Usefulness != 'Highest quality')

# Reclassifying all low quality to NA values
high_qual_raster = reclassify(qualities_raster, cbind(low_quality$Value,NA))
# high_qual_raster = reclassify(high_qual_raster, cbind())
leaflet() %>% addTiles() %>% addRasterImage(high_qual_raster, color='black')

# Filter NDVI raster using these high quality pixels
high_qual_ndvi_raster = nas_removed
high_qual_ndvi_raster[is.na(high_qual_raster)] = NA

# Plot NDVI high quality data
leaflet() %>% addTiles() %>% addRasterImage(high_qual_ndvi_raster)
```


### Remove low quality pixels with the rasterBricks instead of individual raster layers
```{r}
# Quality raster brick - shrink down rasterbrick to 10 layers to save time/memory
#    - this is a proof of concept on how to filter a whole raster brick using another raster
#      brick if needed
ndvi_brick_qc_subset = subset(ndvi_brick_qc, c(1,2,3,4,5,6,7,8,9,10))
dim(ndvi_brick_qc_subset)

# Extract all values that aren't highest quality
low_quality_all = subset(ndvi_quality_lookup, VI.Usefulness != 'Highest quality')
ndvi_brick_qc_high_quality = reclassify(ndvi_brick_qc_subset, cbind(low_quality_all$Value,NA))  # Comment out after initial run

#NDVI raster brick
filtered_ndvi_brick = subset(ndvi_brick, c(1,2,3,4,5,6,7,8,9,10))                               # Comment out after initial run
filtered_ndvi_brick[is.na(ndvi_brick_qc_high_quality)] = NA                                     # Comment out after initial run
```


# Use these leaflet maps below to compare the filtered_ndvi_brick data we created to the filtered data we created 2 cells above where we did 1 selected layer (raster_layer) instead of the whole netcdf.
```{r}
# unfiltered ndvi data
leaflet() %>% addTiles() %>% addRasterImage(subset(ndvi_brick, raster_layer))
# filtered ndvi data based on highest quality pixels
leaflet() %>% addTiles() %>% addRasterImage(subset(filtered_ndvi_brick, raster_layer))
```


### Getting raster for NDVI from netcdf using lat/lon and NDVI
```{r}
# Set lat and lon arrays for NDVI data
lat_NDVI = ncvar_get(ndvi_output, "lat")
lon_NDVI = ncvar_get(ndvi_output, "lon")

# Grab the fill value and set to NA
fillvalue = ncatt_get(ndvi_output, "_250m_16_days_NDVI", "_FillValue")
v6_NDVI[v6_NDVI == fillvalue$value] = NA                                         #Fails in binder on this line

# Define the coordinate referense system proj.4 string
crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0")

# Grab first observation of NDVI and Quality datasets
v6_NDVI = raster(t(v6_NDVI[,,1]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
v6_NDVI_original = v6_NDVI
v6_QA = raster(t(v6_QA[,,1]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
```


### Reading in netcdf as Brick and extracting using pixels
this cell won't run.  Just an example of how the app will plot the data
```{r}
library(rgdal)
library(plotly)
# Raw ndvi data (all time layers)
test_brick = brick(filepaths[1])
# Filtered ndvi data (only first 10 time layers)
# test_brick = filtered_ndvi_brick
test_pixel = readOGR('./Downloads/test_shp/') 

ndvi_under_pixels = extract(test_brick, test_pixel)
px1 = ndvi_under_pixels[[1]][1,]
px2 = ndvi_under_pixels[[2]][1,]
px3 = ndvi_under_pixels[[3]][1,]

dates = as.Date(names(px1),format='X%Y.%m.%d')
test_df = data.frame(date = dates, pixel_1=px1, pixel_2=px2, pixel_3=px3)
test_p = plot_ly(
    data = test_df
  ) %>%
  add_trace(
      x = ~ date,
      y = ~ px1,
      mode = "markers",
      type = "scatter",
      marker = list(color = "red", symbol = "circle"),
      name = "pixel 1",
      showlegend = TRUE
    ) %>%
  add_trace(
      x = ~ date,
      y = ~ px2,
      mode = "markers",
      type = "scatter",
      marker = list(color = "blue", symbol = "circle"),
      name = "pixel 2",
      showlegend = TRUE
    ) %>%
  add_trace(
      x = ~ date,
      y = ~ px3,
      mode = "markers",
      type = "scatter",
      marker = list(color = "green", symbol = "circle"),
      name = "pixel 3",
      showlegend = TRUE
    ) 
test_df
test_p
```



