---
title: "appeears_cron_job"
author: "K. Enns"
date: "9/4/2018"
output: html_document
---

# This code will create a task from all phenocam sites and grab all the available data from AppEEARS for MOD13Q1 (250 NDVI Layer)
### Builds all the requets for each Phenocam site with a 1 degree buffer in WGS

### Getting phenocam csv for site lat/lon data
```{r}
# Variables
table_url = 'https://phenocam.sr.unh.edu/webcam/network/siteinfo/?format=csv'
df        = read.csv(url(table_url))
cams_     = df

cams_$site
site_name = 'arsgacp1'
data      = subset(cams_, site == 'acadia')
lon       = data$lon
lat       = data$lat

subset(df, df$site == 'eastend')

nrow(df)
```

### looping through sites to send area requests to AppEEARS for each site using a .5 degree buffer (polygon) around the site.
```{r}

# Function that checks to see if the Task has already been submitted/completed within the last 2 weeks

# AppEEARS can only process 100 tasks at a time!!
# Loop through each row (each row is 1 site) and submit a task to AppEEARS
# for (x in c(1:length(df$site))){
for (x in c(500:500)){    #401 to 501 last run
  data       = df[x,]
  site       = data$site
  lat        = data$lat
  lon        = data$lon
  starteDate = data$date_start
  endDate    = data$date_end
  print (site)

  task_name_ = paste0(site, '_', format(Sys.time(), '%m_%d_%y_%H%M'))
  print (task_name_)
  task_type_ = 'area'
  startDate_ = '01-01-2000'
  endDate_   = '08-30-2018'
  layer_     = 'MOD13Q1.006, _250m_16_days_NDVI'
  format_    = 'netcdf4'
  projection_name_ = "geographic"
  
  
  # build boundary box based on lat/lon from site
  degree = .5
  # bbox needs to look like this: {min_longitude},{min_latitude},{max_longitude},{max_latitude}
  bbox_ = as.character(paste0(lon-degree,',', lon+degree,',', lat-degree,',', lat+degree))
  print (bbox_)
  xmin = lon-degree
  xmax = lon+degree
  ymin = lat-degree
  ymax = lat+degree
  pt1 = c(xmin,ymin)
  pt2 = c(xmax,ymin)
  pt3 = c(xmax,ymax)
  pt4 = c(xmin,ymax)
  
  coords_ = list(pt1,pt2,pt3,pt4,pt1)
  
  task_list = list(task_type = 'area', 
                 task_name = task_name_,
                 params    =  list(dates  = list(list(startDate = startDate_,
                                                 endDate   = endDate_)),
                                   layers = list(list(layer   = '_250m_16_days_NDVI',
                                                      product = 'MOD13Q1.006')),
                                   output = list(format     = list(type = 'netcdf4'),
                                                 projection = 'geographic'),
                                   geo    = list(type = 'FeatureCollection',
                                                 fileName = 'User-Drawn-Polygon',
                                                 features = list(list(type = 'Feature',
                                                                 geometry = list (type = 'Polygon',
                                                                                  coordinates = list(coords_)))))))
  
  ###########################################################
  ### Comment this section out unless submitting requests ###
  ###########################################################
  
  task_json = rjson::toJSON(task_list)
  print (rjson::toJSON(task_list))

  # # submit the task request
  token <- paste("Bearer", content(token_response)$token)
  response <- POST("https://lpdaacsvc.cr.usgs.gov/appeears/api/task", body = task_json, encode = "json",
                         add_headers(Authorization = token, "Content-Type" = "application/json"))
  task_response <- prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
  
  ###########################################################
  ### Comment this section out unless submitting requests ###
  ###########################################################
}




```

### Find all tasks for account
```{r}
token         = paste("Bearer", content(token_response)$token)
response      = GET("https://lpdaacsvc.cr.usgs.gov/appeears/api/task", add_headers(Authorization = token))
task_response = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
tasks = jsonlite::fromJSON(txt=task_response)
tasks
unique(tasks$task_name)
```

### Grab the task_id for the phenocam site we want
```{r}
site_name
site_row     = tasks[grep(site_name, tasks$task_name), ]
site_row[2,]
site_task_id = site_row[2,]$task_id
site_task_id

```

### Grabbing bundle for lat/lon (site) to get the files desired and their associated id (sha256)
### (Does not requre an authentication!!!)
```{r}
library(httr)
site_task_id
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", site_task_id, sep = ""))
bundle_response = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))

# all files in bundle
document = jsonlite::fromJSON(txt=bundle_response)
files = document$files
files

# csv files 
csvs      = subset(files, file_type == 'csv')
quality_lookup_id     = csvs[grep('Quality-lookup', csvs$file_name), ]$file_id
quality_statistics_id = csvs[grep('Quality-Statistics', csvs$file_name), ]$file_id
  
# Net cdf
netcdf    = subset(files, file_type == 'nc')
netcdf_id = netcdf$file_id
```

### Download the files in memory for app to use
```{r}
# task id for the site
sprintf('%s task id : %s', site_name, site_task_id)

# file id for file to download
sprintf('Quality Lookup CSV id     : %s', quality_lookup_id)
sprintf('Quality statistics CSV id : %s', quality_statistics_id)
sprintf('Net CDF id                : %s', netcdf_id)
```

### Download this file from AppEEARS task id filtered out previously
```{r}

download_this_file = netcdf_id
# # retrieve the filename from the file_id
bundle = fromJSON(bundle_response)$files
filename = bundle[bundle$file_id == download_this_file,]$file_name
# create a destination directory to store the file in
dest_dir = '/path/to/download/folder'
filepath = paste(dest_dir, filename, sep = '')
# suppressWarnings(dir.create(dirname(filepath)))
filepath

# write the file to disk using the destination directory and file name 
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", site_task_id, '/', download_this_file, sep = ""),
                      write_disk(filepath, overwrite = TRUE), progress())
response
```


# Below is code in progress to Create a task using a shapefile/geojson (simple shapefile works)

#### Creating a shapefile of contiguous US to use to submit a task to appeears
```{r}
library(rgdal)
library(raster)
library(rgeos)
library(sp)
library(leaflet)
library(spdplyr)
library(geojsonio)

crs_wgs = "+proj=longlat +datum=WGS84 +no_defs"
gClip = function(shp, bb){
  if(class(bb) == "matrix"){
    b_poly = as(extent(as.vector(t(bb))), "SpatialPolygons")
    proj4string(b_poly) = CRS(crs_wgs)
  }else {
    b_poly = as(extent(bb), "SpatialPolygons")
    proj4string(b_poly) = CRS(crs_wgs)
  }
  gIntersection(shp, b_poly, byid = TRUE)
}

bb = c(-138, -56, 21,54)
# shape_US_nad = readOGR(dsn = "./www/cb_2017_us_nation_20m", layer = "cb_2017_us_nation_20m")

shape_US_wgs  = spTransform(shape_US,CRS(crs_wgs))
shape_contigious_US_wgs = gClip(shape_US_wgs, bb)

leaflet(shape_US_wgs) %>% addTiles() %>%
    addPolygons(color = "#444444", weight = 1, smoothFactor = 0.5,
    opacity = 1.0, fillOpacity = 0.5)

leaflet(shape_contigious_US_wgs) %>% addTiles() %>%
    addPolygons(color = "#444444", weight = 1, smoothFactor = 0.5,
    opacity = 1.0, fillOpacity = 0.5)

shape_contigious_US_wgs_json = geojsonio::geojson_json(shape_contigious_US_wgs)

test = rgdal::readOGR(shape_contigious_US_wgs_json)

leaflet() %>% addTiles() %>% addPolygons(data=test, weight=2)


length(shape_contigious_US_wgs@polygons[[1]]@Polygons)



# Calling function in next cell
coords_compiled = get_latlon_from_shapefile(shape_contigious_US_wgs)
print (coords_compiled)

leaflet('map') %>% addTiles() %>% addPolygons(lng = lons, lat=lats)
print (coords_compiled)
task_list = list(task_type = 'area', 
                 task_name = 'Contiguous US 1yr 2017 MOD13Q1 NDVI',
                 params    =  list(dates  = list(list(startDate = '01-01-2017',
                                                 endDate   = '01-01-2018')),
                                   layers = list(list(layer   = '_250m_16_days_NDVI',
                                                      product = 'MOD13Q1.006')),
                                   output = list(format     = list(type = 'netcdf4'),
                                                 projection = 'geographic'),
                                   geo    = list(type = 'FeatureCollection',
                                                 fileName = 'User-Drawn-Polygon',
                                                 features = shape_colorado_wgs_json)))

task_json = rjson::toJSON(task_list)

# write(task_json, file = './www/testtaskjson.json')
print (rjson::toJSON(task_list))


# submit the task request
token <- paste("Bearer", content(token_response)$token)
response <- POST("https://lpdaacsvc.cr.usgs.gov/appeears/api/task", body = task_json, encode = "json",
                       add_headers(Authorization = token, "Content-Type" = "application/json"))
task_response <- prettify(toJSON(content(response), auto_unbox = TRUE))
task_response

```


# This cell takes a shapefile as input (works)
#### Creating a json file in WGS84 to submit to appeears through API (Using area)
```{r}
# shape_states_nad = readOGR(dsn = "./downloads/cb_2017_us_state_500k", layer = 'cb_2017_us_state_500k')
shape_colorado_wgs      = spTransform(shape_colorado_nad, CRS("+proj=longlat +ellps=WGS84"))
shape_colorado_wgs_json = geojson_json(shape_colorado_wgs)

leaflet() %>% addTiles() %>% addPolygons(data=shape_colorado_wgs, weight=2)
shape_colorado_wgs_json
print (shape_colorado_wgs)
shape_colorado_wgs_json = geojsonio::geojson_json(shape_colorado_wgs)
# print (shape_colorado_wgs@polygons[[1]]@Polygons[[1]]@coords)


# Function that takes a shapefile and returns a list of lon/lat coordinates
#   that can be sent in a JSON task to AppEEARS
get_latlon_from_shapefile = function(shapefile){
  # Shapefile Coordinates
  coordinates(shapefile)
  coords = shapefile@polygons[[1]]@Polygons[[1]]@coords
  # Build coordinates for json
  coords_compiled = list()
  lats = c()
  lons = c()
  # Loop through the coordinates and build them into a list AppEEARS tasks can use
  for (x in c(1:(length(coords)/2))){
    lon = coords[x,1]
    lat = coords[x,2]
    lons = append(lons, lon)
    lats = append(lats, lat)
    lon_lat = c(lon, lat)
    coords_compiled = append(coords_compiled, list(lon_lat))
  }
  return (coords_compiled)
}

coords_compiled = get_latlon_from_shapefile(shape_colorado_wgs)
print (coords_compiled)

leaflet('map') %>% addTiles() %>% addPolygons(lng = lons, lat=lats)
print (coords_compiled)
task_list = list(task_type = 'area', 
                 task_name = 'Colorado Test geojson2',
                 params    =  list(dates  = list(list(startDate = '01-01-2000',
                                                 endDate   = '08-29-2018')),
                                   layers = list(list(layer   = '_250m_16_days_NDVI',
                                                      product = 'MOD13Q1.006')),
                                   output = list(format     = list(type = 'netcdf4'),
                                                 projection = 'geographic'),
                                   geo    = list(type = 'FeatureCollection',
                                                 fileName = 'User-Drawn-Polygon',
                                                 features = list(list(type = 'Feature',
                                                                 geometry = list (type = 'Polygon',
                                                                                  coordinates = list(coords_compiled)))))))

task_json = rjson::toJSON(task_list)

# write(task_json, file = './www/testtaskjson.json')
print (rjson::toJSON(task_list))


# submit the task request
token <- paste("Bearer", content(token_response)$token)
response <- POST("https://lpdaacsvc.cr.usgs.gov/appeears/api/task", body = task_json, encode = "json",
                       add_headers(Authorization = token, "Content-Type" = "application/json"))
task_response <- prettify(toJSON(content(response), auto_unbox = TRUE))
task_response
```


## Manually input the coordinates for a box

```{r}

coords_ = list(c(-58,21),c(-58,54),c(-138,54),c(-138,53),c(-58,21))
coords_
task_list = list(task_type = 'area', 
                 task_name = 'Colorado Test geojson',
                 params    =  list(dates  = list(list(startDate = '01-01-2000',
                                                 endDate   = '08-29-2018')),
                                   layers = list(list(layer   = '_250m_16_days_NDVI',
                                                      product = 'MOD13Q1.006')),
                                   output = list(format     = list(type = 'netcdf4'),
                                                 projection = 'geographic'),
                                   geo    = list(type = 'FeatureCollection',
                                                 fileName = 'User-Drawn-Polygon',
                                                 features = list(list(type = 'Feature',
                                                                 geometry = list (type = 'Polygon',
                                                                                  coordinates = list(coords_)))))))

task_json = rjson::toJSON(task_list)
# write(task_json, file = './www/testtaskjson.json')
print (prettify(rjson::toJSON(task_list)))
# submit the task request
token <- paste("Bearer", content(token_response)$token)
response <- POST("https://lpdaacsvc.cr.usgs.gov/appeears/api/task", body = task_json, encode = "json",
                       add_headers(Authorization = token, "Content-Type" = "application/json"))
task_response <- prettify(toJSON(content(response), auto_unbox = TRUE))
task_response
```




```{r}
task_type_ = 'area'
task_name_ = 'test with geo'
startDate_ = '01-01-2000'
endDate_   = '08-29-2018'
layer_     = 'MOD13Q1.006, _250m_16_days_NDVI'
format_    = 'NetCDF4'
projection_name_ = "geographic"
# bbox_ = '-126.2109375, 22.5, -63.3515625, 50.765625'
bbox_ = '-138, -56, 21, 54'
# coordinates_ = '{-126.2109375, 22.5}, {-126.2109375, 50.765625}, {-63.3515625, 50.765625}, {-63.3515625, 22.5}, {-126.2109375, 22.5}'


task <- list(task_type       = task_type_, 
             task_name       = task_name_,
             startDate       = startDate_, 
             endDate         = endDate_, 
             layer           = layer_, 
             # bbox            = bbox_,
             coordinates     = shape_colorado_wgs_json,
             file_type       = format_,
             projection_name = projection_name_)



# submit the task request
token <- paste("Bearer", content(token_response)$token)
response <- POST("https://lpdaacsvc.cr.usgs.gov/appeears/api/task", query = task, add_headers(Authorization = token))
response

```