---
title: "appeears_data_analysis"
author: "K. Enns"
date: "9/4/2018"
output: html_document
---


### Site and AppEEARS task ID from (K. Enns) tasks, edited by KDuffy
```{r}
library(jsonlite)
library(ncdf4)
library(ncdf4.helpers)
library(PCICt)
library(httr)
library(leaflet)
```

### Grab bundle from task id
```{r}
site_task_id = 'e106f82f-7191-4050-a8af-f142e2f981d3'
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", site_task_id, sep = ""))
bundle_response = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))

# all files in bundle
document = jsonlite::fromJSON(txt=bundle_response)
files = document$files
class(files)
```

### Getting netcdf id + other file ids from the bundle
```{r}
# csv files 
csvs      = subset(files, file_type == 'csv')
quality_lookup_id     = csvs[grep('Quality-lookup', csvs$file_name), ]$file_id
quality_statistics_id = csvs[grep('Quality-Statistics', csvs$file_name), ]$file_id
  
# Net cdf
netcdf    = subset(files, file_type == 'nc')
netcdf_id = netcdf$file_id
netcdf
```


### Download the netcdf from the netcdf id
```{r}
get_download_folder = function(){
  if (Sys.info()['sysname'] == 'Darwin'){
    folder = paste('/Users/', Sys.getenv('LOGNAME'),'/Downloads/', sep = '')
  }else if (Sys.info()['sysname'] == 'Windows'){
    folder = paste('C:/Downloads/', sep = '')
  }else{
    folder = ''
  }
  return (folder)
  }

download_this_file = netcdf_id
# # retrieve the filename from the file_id
bundle = jsonlite::fromJSON(bundle_response)$files
filename = subset(bundle, bundle$file_id == download_this_file)$file_name
# create a destination directory to store the file in
dest_dir = get_download_folder()
filepath = paste(dest_dir, filename, sep = '')
# suppressWarnings(dir.create(dirname(filepath)))

# write the file to disk using the destination directory and file name 
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", site_task_id, '/', download_this_file, sep = ""),
                      write_disk(filepath, overwrite = TRUE), progress())
```

### Function to read in the netcdf





### Read in netCDF file just downloaded above
```{r}
library(raster); library(rmarkdown); library(ncdf4); library(sp)
ndvi_output = nc_open(filepath)

# Print a list of variables in file
print (attributes(ndvi_output$var)$names)

# Print a list of dimensions in file
print (attributes(ndvi_output$dim)$names)
```

## Start of the https://lpdaac.usgs.gov/sites/default/files/public/elearning/AppEEARS_NC_QualityFiltering_R.html#8_mask_by_land_cover_type example
### Extracting the NDVI and Quality layers from the netcdf (NDVI)
```{r}
v6_info = ncatt_get(ndvi_output, "_250m_16_days_NDVI")

v6_NDVI = ncvar_get(ndvi_output, "_250m_16_days_NDVI")
v6_QA   = ncvar_get(ndvi_output, "_250m_16_days_VI_Quality")                    #Fails in binder on this line
print (dim(v6_NDVI))
print (dim(v6_QA))
```

### Getting raster for NDVI from netcdf using lat/lon and NDVI
```{r}
# Set lat and lon arrays for NDVI data
lat_NDVI = ncvar_get(ndvi_output, "lat")
lon_NDVI = ncvar_get(ndvi_output, "lon")

# Grab the fill value and set to NA
fillvalue = ncatt_get(ndvi_output, "_250m_16_days_NDVI", "_FillValue")
v6_NDVI[v6_NDVI == fillvalue$value] = NA                                         #Fails in binder on this line

# Define the coordinate referense system proj.4 string
crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs+ towgs84=0,0,0")

# Grab first observation of NDVI and Quality datasets
v6_NDVI = raster(t(v6_NDVI[,,1]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
v6_NDVI_original = v6_NDVI
v6_QA = raster(t(v6_QA[,,1]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
```


### Get lookup table for the netcdf (quality table)
```{r}
download_this_file = quality_lookup_id
# # retrieve the filename from the file_id
bundle = fromJSON(bundle_response)$files
filename = bundle[[1]]$file_name
# create a destination directory to store the file in
dest_dir = get_download_folder()
filepath = paste(dest_dir, filename, sep = '')
# suppressWarnings(dir.create(dirname(filepath)))
# write the file to disk using the destination directory and file name 
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", site_task_id, '/', download_this_file, sep = ""),
                      write_disk(filepath, overwrite = TRUE), progress())
v6_QA_lut = read.csv(filepath)
v6_QA_lut
```


### Clipping the Landcover tif to the same coordinates as the netcdf
```{r}
us_pth = './www/uslandcover_modis.tif'
site_lon = -68.2608
site_lat = 44.3769

us_r   = raster(us_pth)
print (unique(values(us_r)))
resolution = res(us_r)[1]

height = 2
width  = 2
e      = as(extent(site_lon - width, site_lon + width, site_lat - height, site_lat + height), 'SpatialPolygons')
crs(e) <- "+proj=longlat +datum=WGS84 +no_defs"
lct_r_original      = crop(us_r, e)
unique(values(lct_r_original))
leaflet('map') %>% addTiles() %>% addRasterImage(lct_r_original, opacity = .7)
```

### 
```{r}
lct_forest = c(1,2,3,4,5,17)
lct_r_forest = lct_r_original
lct_r_forest[!lct_r_forest %in% lct_forest,] = NA 
lct_r_forest
sort(unique(values(lct_r_forest)), decreasing = FALSE)
leaflet('map') %>% addTiles() %>% addRasterImage(lct_r_forest, opacity = .7)

```
### Build color pallet for pft raster based on values available
```{r}

build_pft_palette = function(raster_){
  colors = c()
  color_list    = c('#1b8a28', '#36d03e', '#9ecb30', '#a0f79f', '#91bb88', '#b99091', '#f0dfb8', '#d6ed9a',
                                 '#f1dc07', '#ecbb5b', '#4981b1', '#fcee72', '#fd0608', '#9b9353', '#bdbec0', '#bdbec0', '#89cae3')
  v = unique(values(raster_))
  remove = c(NA)
  v = v [! v %in% remove]
  v = sort(v, decreasing = FALSE)
  print (v)
  for (x in v){
    colors = c(colors, color_list[x])
  }
  return (colors)
}

c3 = build_pft_palette(lct_r_forest)
leaflet('map') %>% addTiles() %>% addRasterImage(lct_r_original, col = c3, opacity = .7)

```



### Only using data that is good enough quality
```{r}
modland = c('VI produced, good quality', 'VI produced, but check other QA')
v6_QA_lut = v6_QA_lut[v6_QA_lut$MODLAND %in% modland,]

# Include better quality VI usefulness
VIU = c("Lowest quality","Quality so low that it is not useful","L1B data faulty","Not useful for any other reason/not processed")
v6_QA_lut = v6_QA_lut[!v6_QA_lut$VI.Usefulness %in% VIU,]

# Exclude climatology or high aerosol
AQ = c('Low','Average')
v6_QA_lut = v6_QA_lut[v6_QA_lut$Aerosol.Quantity %in% AQ,]

# Include where adjacent cloud, mixed clouds, or possible shadow were not detected
v6_QA_lut = v6_QA_lut[v6_QA_lut$Adjacent.cloud.detected == 'No',]
v6_QA_lut = v6_QA_lut[v6_QA_lut$Mixed.Clouds == 'No', ]
v6_QA_lut = v6_QA_lut[v6_QA_lut$Possible.shadow == 'No',]
v6_QA_lut

```

```{r}
# Visualize a basic plot:
plot(v6_NDVI_original)
leaflet('map') %>% addTiles() %>% addRasterImage(v6_NDVI_original, opacity = .8)
```

#
```{r}
# Import additional colormaps
library(RColorBrewer)

# Create custom colormap
YlGn = brewer.pal(9, "YlGn")

# Plot the unfiltered data for time step 1, using a colormap and setting a custom linear stretch
leaflet('map') %>% addTiles() %>% addRasterImage(v6_NDVI_original, col = YlGn, opacity = .8)
```

```{r}
v6_NDVI = ncvar_get(ndvi_output, "_250m_16_days_NDVI")
v6_QA   = ncvar_get(ndvi_output, "_250m_16_days_VI_Quality")

# See how many time steps the file contains
dim(v6_NDVI)
```


```{r}
invisible(library(rworldmap))
data(countriesLow)
# Define a function to apply scale factor
apply_sf = function(x){as.integer(x*10000)}

# Loop through all timesteps (observations) in the file, mask out poor quality and exclude non-forest pixels
for (i in 1:ndvi_output$dim$time$len){
  v6_NDVI_1 = raster(t(v6_NDVI[,,i]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
  v6_QA_1 = raster(t(v6_QA[,,i]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
  
  # Apply QA mask to the NDVI data
  v6_NDVI_1[!v6_QA_1 %in% v6_QA_mask,]= NA
  rm(v6_QA_1)
  
  # Next, apply LCT mask to the NDVI data
  v6_NDVI_1[!resampled_lct %in% lct_forest,]= NA
  v6_NDVI_1= calc(v6_NDVI_1, apply_sf)
  v6_NDVI[,,i] = t(v6_NDVI_1[,,1])
  rm(v6_NDVI_1)
}
rm(resampled_lct, v6_QA)

par(mfrow=c(2,3),oma = c(0, 0, 3, 0))
#title(, line = 0.21)
image(raster(t(v6_NDVI[,,1]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
      ,zlim=c(-200,10000),  col = YlGn,  xlab = 'Longitude', ylab = 'Latitude', main = '07-12-2005')
rect(par("usr")[1],par("usr")[3],par("usr")[2],par("usr")[4],col = "lightblue")
plot(countriesLow,col = 'white', add = TRUE)
image(raster(t(v6_NDVI[,,1]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
      ,zlim=c(-200,10000),  col = YlGn, add = T)
plot(countriesLow, add = T)
image(raster(t(v6_NDVI[,,2]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
      ,zlim=c(-200,10000),  col = YlGn,xlab = '', ylab = '', xaxt='n', yaxt='n', main ='07-28-2005')
rect(par("usr")[1],par("usr")[3],par("usr")[2],par("usr")[4],col = "lightblue")
plot(countriesLow,col = 'white', add = TRUE)
image(raster(t(v6_NDVI[,,2]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
      ,zlim=c(-200,10000),  col = YlGn, add = T)
plot(countriesLow, add = T)
image(raster(t(v6_NDVI[,,3]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
      ,zlim=c(-200,10000),  col = YlGn,xlab = '', ylab = '',xaxt='n', yaxt='n', main ='08-13-2005')
rect(par("usr")[1],par("usr")[3],par("usr")[2],par("usr")[4],col = "lightblue")
plot(countriesLow,col = 'white', add = TRUE)
image(raster(t(v6_NDVI[,,3]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
      ,zlim=c(-200,10000),  col = YlGn, add = T)
plot(countriesLow, add = T)
image(raster(t(v6_NDVI[,,4]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
      ,zlim=c(-200,10000),  col = YlGn,  xlab = '', ylab = '', xaxt='n', yaxt='n', main = '08-29-2005')
rect(par("usr")[1],par("usr")[3],par("usr")[2],par("usr")[4],col = "lightblue")
plot(countriesLow,col = 'white', add = TRUE)
image(raster(t(v6_NDVI[,,4]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
      ,zlim=c(-200,10000),  col = YlGn, add = T)
plot(countriesLow, add = T)
image(raster(t(v6_NDVI[,,5]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
      ,zlim=c(-200,10000),  col = YlGn,xlab = '', ylab = '', xaxt='n', yaxt='n', main ='09-14-2005')
rect(par("usr")[1],par("usr")[3],par("usr")[2],par("usr")[4],col = "lightblue")
plot(countriesLow,col = 'white', add = TRUE)
image(raster(t(v6_NDVI[,,5]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
      ,zlim=c(-200,10000),  col = YlGn, add = T)
plot(countriesLow, add = T)
image(raster(t(v6_NDVI[,,6]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
      ,zlim=c(-200,10000),  col = YlGn,xlab = '', ylab = '',xaxt='n', yaxt='n', main ='09-30-2005')
rect(par("usr")[1],par("usr")[3],par("usr")[2],par("usr")[4],col = "lightblue")
plot(countriesLow,col = 'white', add = TRUE)
image(raster(t(v6_NDVI[,,6]), xmn=min(lon_NDVI), xmx=max(lon_NDVI), ymn=min(lat_NDVI), ymx=max(lat_NDVI), crs=crs)
      ,zlim=c(-200,10000),  col = YlGn, add = T)
plot(countriesLow, add = T)
mtext('MODIS Version 6 Enhanced Vegetation Index (NDVI): 07-12-2005 to 09-30-2005', outer = TRUE, cex = 1.5)
```






























```{r}
lon     = ncvar_get(ndvi_output, varid = "lon")
lat     = ncvar_get(ndvi_output, varid = "lat")
lat = rev(lat)
time    = ncvar_get(ndvi_output, varid = "time")
ndvi    = ncvar_get(ndvi_output, varid='_250m_16_days_NDVI')
ndvi = ndvi[ , , 1]
# ndvi_VI = ncvar_get(ndvi_output, varid='_250m_16_days_VI_Quality')   # this fails in binder.. not sure why
```



```{r}
image(lon,lat,ndvi)

leaflet('map') %>% addTiles()

```


### Read in the netcdf(that we just downloaded above) to R
```{r}
library(sp)
library(raster)

netCDF_file = filepath
netCDF_file

plot(ndvi)
```


### function used in the application to download a netcdf
```{r}
# Downloads the netcdf from a task id
download_bundle_file = function(site_task_id_, ft){
  response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", site_task_id_, sep = ""))
  bundle_response = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
  document = jsonlite::fromJSON(txt=bundle_response)
  files = document$files
  if (ft == 'nc'){
    netcdf    = subset(files, file_type == 'nc')
    download_this_file = netcdf$file_id
    file_name = netcdf$file_name
  }else if(ft == 'qa_csv'){
    csvs      = subset(files, file_type == 'csv')
    qa_csv    = csvs[grep('Quality-lookup', csvs$file_name), ]$file_id
    download_this_file = qa_csv
    file_name = qa_csv$file_name
  }
  dest_dir = './www/'
  filepath = paste(dest_dir, file_name, sep = '')
  response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", site_task_id_, '/', download_this_file, sep = ""),
                 write_disk(filepath, overwrite = TRUE), progress())
  return (filepath)
}
file = download_bundle_file(site_task_id, 'nc')
```

### function used in app to delete the downloaded netcdf based on site_task_id
```{r}
# Deletes the netcdf from input filepath
delete_file = function(filepath_){
  if (file.exists(filepath_)) file.remove(filepath_)
}
delete_file(file)
```










