---
title: "appeears_workflow"
author: "Kyle"
date: "8/21/2018"
output: html_document
---

# AppEEARS api for R and grabbing box for NDVI timeseries

## Login
documentation: <https://lpdaacsvc.cr.usgs.gov/appeears/api/?language=R#login>

```{r}
library(httr)
library(jsonlite)

username = ''
password = ''

secret <- base64_enc(paste(username, password, sep = ":"))
response <- POST("https://lpdaacsvc.cr.usgs.gov/appeears/api/login", 
                             add_headers("Authorization" = paste("Basic", gsub("\n", "", secret)),
                                         "Content-Type" = "application/x-www-form-urlencoded;charset=UTF-8"), 
                             body = "grant_type=client_credentials")
token_response = response
token_response
```

## Get Products list (33 is MOD13Q1, and 4 is MCD12Q1)

```{r}
response <- GET("https://lpdaacsvc.cr.usgs.gov/appeears/api/product")
product_response <- toJSON(content(response))

# create a list indexed by the product name and version
products <- fromJSON(product_response)
products[[33]]$Product
length(products)

# for (x in c(1:91)){
#   print (x)
#   print (products[[x]]$Product)
# }

```


# Area Task Submition (using Query String)
## Using the area option to grab a box from 1 year of the LandCover Layer MCD12Q1 with Type1 as the band
documentation: <https://lpdaacsvc.cr.usgs.gov/appeears/api/?language=R#submit-task>

```{r}

task_type_ = 'area'
task_name_ = 'United States Landcover1'
startDate_ = '12-12-2015'
endDate_   = '03-03-2016'
layer_     = 'MCD12Q1.006, LC_Type1'
format_    = 'geotiff'
projection_name_ = "sinu_modis"
bbox_ = '-126.2109375, 22.5, -63.3515625, 50.765625'
# coordinates_ = '{-126.2109375, 22.5}, {-126.2109375, 50.765625}, {-63.3515625, 50.765625}, {-63.3515625, 22.5}, {-126.2109375, 22.5}'


task <- list(task_type       = task_type_, 
             task_name       = task_name_,
             startDate       = startDate_, 
             endDate         = endDate_, 
             layer           = layer_, 
             bbox            = bbox_,
             file_type       = 'geotiff',
             projection_name = projection_name_)

# submit the task request
token <- paste("Bearer", content(token_response)$token)
response <- POST("https://lpdaacsvc.cr.usgs.gov/appeears/api/task", query = task, add_headers(Authorization = token))
response
```

# Point Task Submition (using Query String)
## Using the point option to grab a pixel from one lat/lon 

```{r}
# Title for AppEEARS task
task_name_ = 'Fort Collins Point10'

task_type_ = 'point'
startDate_ = '01-01-2014'
endDate_   = '01-01-2015'
layer_     = 'MOD13Q1.006,_250m_16_days_NDVI'
# layer_ = 'MOD11A1.006,LST_Day_1km'
coordinate_1 = '40.5, -105.0'
coordinate_2 = '40.6, -105.1'
coordinate_3 = '40.7, -105.2'



task <- list(task_type = task_type_, 
             task_name = task_name_, 
             startDate = startDate_, 
             endDate = endDate_, 
             layer = layer_,
             coordinate = coordinate_1,
             coordinate = coordinate_2,
             coordinate = coordinate_3)

# This is how you can iterate over the list to add coordinates
#   - Could be helpful for adding all highlighted pixel lat/lon
#     to 1 task

# list_ = list(name = 'Kyle')
# for (x in c(1:10)){
#   add_this = list(coordinate = x)
#   list_ = append(list_, add_this)
# }
# print (list_)

# submit the task request
token <- paste("Bearer", content(token_response)$token)
response <- POST("https://lpdaacsvc.cr.usgs.gov/appeears/api/task", query = task, add_headers(Authorization = token))
response

```


```{r}
task_type_ = 'area'
task_name_ = 'Fort Collins area test'
startDate_ = '01-01-2014'
endDate_   = '01-01-2018'
layer_     = 'MOD13Q1.006, _250m_16_days_NDVI'
format_    = 'geotiff'
projection_name_ = "sinu_modis"
bbox_ = '-104.982119165361, 40.5666814327214, -104.944096170366, 40.5952334867392'


task <- list(task_type       = task_type_, 
             task_name       = task_name_,
             startDate       = startDate_, 
             endDate         = endDate_, 
             layer           = layer_, 
             bbox            = bbox_,
             file_type       = 'geotiff',
             projection_name = projection_name_)

# submit the task request
token <- paste("Bearer", content(token_response)$token)
response <- POST("https://lpdaacsvc.cr.usgs.gov/appeears/api/task", query = task, add_headers(Authorization = token))
response
```



# Attempting to build json to submit.  
## Creating a task as a JSON for the Task.

```{r}
library(jsonlite)
# MM-DD-YYYY

task_type_ = 'area'
task_name_ = 'United States Landcover1'
file_type_ = 'GeoJSON'
startDate_ = '12-12-2015'
endDate_   = '03-03-2016'
layer_     = 'MOD13Q1'
product_   = '250m_16_days_NDVI'
format_    = 'geotiff'
projection_name_ = "sinu_modis"
coordinates_ = '[[[-126.2109375, 22.5], [-126.2109375, 50.765625], [-63.3515625, 50.765625], [-63.3515625, 22.5], [-126.2109375, 22.5]]]'

geo_       = list(type = 'FeatureCollection',
                  fileName = 'User-Drawn-Polygon',
                  features = list(type = 'Feature',
                                  geometry = list(type = 'Polygon',
                                                  coordinates = coordinates_)))


dates_ = list(startDate = startDate_,
              endDate   = endDate_)

format_ = list(type = file_type_)

layers_    = list(product = product_, 
                  layer   = layer_)

params_    = list(dates  = dates_,
                  layers = layers_,
                  geo    = geo_,
                  output = output_)

output_ = list(format     = format_,
               projection = projection_name_)


task = list(task_type = task_type_, 
            task_name = task_name_, 
            params    = params_)

task_json = toJSON(task)
task_json
print (class(task_json))

```




```{r}


```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```



```{r}

```




```{r}

```




```{r}

```





```{r}

```





```{r}

```




```{r}

```