---
title: "Cache tasks locally"
author: "K. Enns"
date: "1/29/2020"
output: html_document
---

## RUN GLOBAL.R IN MAIN DIRECTORY FIRST!

Check for ndvi and landcover data in www/site_data/site_name/data_layers/ndvi/ndvi and lc.
Check for nlcd landcover data in www/landsat_lc/site_name_landsat_lc.tif
  - Build lists for sites without ndvi and MODIS landcover but that include NLCD
```{r}
sites_with_nlcd    = c()
sites_without_nlcd = c()
for (this_site in cams_$site){
  this_nlcd_file = paste0('../www/landsat_lc/', this_site, '_landsat_lc.tif')
    # If NLCD layer exists for site, add it to map
  if (file.exists(this_nlcd_file)){
    site_nlcd_raster = raster::raster(this_nlcd_file) 
    sites_with_nlcd = c(sites_with_nlcd, this_site)
  } else{
    sites_without_nlcd = c(sites_without_nlcd, this_site)
  }
}

sites_with_modis_lc    = c()
sites_without_modis_lc = c()
sites_with_ndvi        = c()
sites_without_ndvi     = c()
# Loop through the phenocam sites
for (this_site in sites_with_nlcd){
  # Get site Data
  # Extract nlcd file
  this_nlcd_file = paste0('../www/landsat_lc/', this_site, '_landsat_lc.tif')
  # Extract modis NDVI file
  modis_ndvi_dir = paste0('../www/site_data/', this_site, '/data_layers/ndvi/tera/')
  modis_ndvi_files = list.files(modis_ndvi_dir)
  this_modis_ndvi_file = paste0(modis_ndvi_dir, modis_ndvi_files[grep('.nc', modis_ndvi_files)])
  # Extract modis LC file
  modis_lc_dir   = paste0('../www/site_data/', this_site, '/data_layers/lc/')
  modis_lc_files = list.files(modis_lc_dir)
  this_modis_lc_file = paste0(modis_lc_dir, modis_lc_files[grep('.nc', modis_lc_files)])
  # MODIS LC
  if(file.exists(this_modis_lc_file)){
    sites_with_modis_lc = c(sites_with_modis_lc, this_site)
  }else{
    sites_without_modis_lc = c(sites_without_modis_lc, this_site)
  }
  # MODIS NDVI
  if(file.exists(this_modis_ndvi_file)){
    sites_with_ndvi = c(sites_with_ndvi, this_site)
  }else{
    sites_without_ndvi = c(sites_without_ndvi, this_site)
  }
}
print ('------------------ NLCD ------------------')
print ('Sites That have no NLCD layer:')
length(sites_without_nlcd)
print ('Sites with NLCD layer:')
length(sites_with_nlcd)
print ('------------------ Sites with NLCD ------------------')
print ('------------------ MODIS LC ------------------')
print ('Sites That have no MODIS LC layer:')
length(sites_without_modis_lc)
print ('Sites with MODIS LC layer:')
length(sites_with_modis_lc)
print ('------------------ MODIS NDVI ------------------')
print ('Sites That have no MDOIS NDVI layer:')
length(sites_without_ndvi)
print ('Sites with MODIS NDVI layer:')
length(sites_with_ndvi)
```

Loop through the sites_without_modis_lc and download into the local cache
-  Time estimate at 15 minutes to run
```{r}
cache_pc_sites_modis_lc = function(sites){
  for (this_modis_lc_site in sites){
    site_row = subset(cams_, cams_$site == this_modis_lc_site)
    
    # Set up directories to store data
    file_path     = paste0('../www/site_data/', this_modis_lc_site, '/data_layers/')
    main          = '../www/site_data'
    main_site = paste0(main, '/', this_modis_lc_site)
    lc_filepath        = paste0(file_path, 'lc/')
    
    # Build main path
    if (!file.exists(main)){
      dir.create(file.path(main))
    }
    # Build main_site path
    if (!file.exists(main_site)){
      dir.create(file.path(main_site))
    }
    # Build data_layers dir
    if (!file.exists(file_path)){
        dir.create(file.path(file_path))
    }
    # Build modis landcover path
    if (!file.exists(lc_filepath)){
      dir.create(file.path(lc_filepath))
    }
    # Download  landcover for this site
    this_landcover_row = get_appeears_task(this_modis_lc_site, type = 'landcover')
    lc_bundle_df = download_bundle_file(this_landcover_row$task_id, lc_filepath)
  }
}
cache_pc_sites_modis_lc(sites_without_modis_lc)

```

### For 500 sites this is over 15 GB of data.. (note)
Loop through the sites_without_ndvi and download into the local cache
```{r}
cache_pc_sites_modis_ndvi = function(sites){
  for (this_ndvi_site in sites){
    site_row = subset(cams_, cams_$site == this_ndvi_site)
  
    # Set up directories to store data
    file_path     = paste0('../www/site_data/', this_ndvi_site, '/data_layers/')
    main          = '../www/site_data'
    ndvi_filepath      = paste0(file_path,'ndvi/')
    ndvi_tera_filepath = paste0(ndvi_filepath, 'tera/')
    main_site = paste0(main, '/', this_ndvi_site)
    
    # Build main path
    if (!file.exists(main)){
      dir.create(file.path(main))
    }
    # Build main_site path
    if (!file.exists(main_site)){
      dir.create(file.path(main_site))
    }
    # Build ndvi path
    if (!file.exists(ndvi_filepath)){
      dir.create(file.path(ndvi_filepath))
    }
    # Build data_layers dir
    if (!file.exists(file_path)){
        dir.create(file.path(file_path))
    }
    # Build ndvi tera path
    if (!file.exists(ndvi_tera_filepath)){
      dir.create(file.path(ndvi_tera_filepath))
    }
    # Download NDVI for this site 
    ndvi_tera_row = get_appeears_task(this_ndvi_site, type = 'ndvi_tera')
    ndvi_bundle_df_tera = download_bundle_file(ndvi_tera_row$task_id, ndvi_tera_filepath)
  }
}
cache_pc_sites_modis_ndvi(sites_without_ndvi)
```



How to cache all of the nlcd site layers into applications
Get lat/lon for phenocam sites, reproject to merc, crop, and save out raster
<!-- ```{r} -->
<!-- library(raster) -->
<!-- # Point to the nlcd 2016 raster .img file that you download from WSMR -->
<!-- NLCD_lc = raster::raster('/Users/kenns/Downloads/NLCD_2016_Land_Cover_L48_20190424/NLCD_2016_Land_Cover_L48_20190424.img') -->
<!-- sites = cams_$site -->
<!-- output_dir = '../www/landsat_lc' -->

<!-- for (cam_site in sites){ -->
<!--   # cam_site = 'NEON.D15.ONAQ.DP1.00033' -->
<!--   print (cam_site) -->
<!--   site_row = subset(cams_, cams_$site == cam_site) -->
<!--   site_lat_wgs = site_row$lat -->
<!--   site_lon_wgs = site_row$lon -->

<!--   site_albs_point = from_crs1_to_crs2_lon_lat(lon_ = site_lon_wgs, lat_ = site_lat_wgs, from_crs = wgs_crs, to_crs = alb_crs) -->
<!--   site_lon_alb = site_albs_point@coords[[1]] -->
<!--   site_lat_alb = site_albs_point@coords[[2]] -->

<!--   site_sinu_point = from_crs1_to_crs2_lon_lat(lon_ = site_lon_wgs, lat_ = site_lat_wgs, from_crs = wgs_crs, to_crs = sinu_crs) -->
<!--   site_lon_sinu = site_sinu_point@coords[[1]] -->
<!--   site_lat_sinu = site_sinu_point@coords[[2]] -->

<!--   if (is.na(extract(NLCD_lc, site_albs_point)[1])){ -->
<!--     print (paste0(cam_site, ' does not have NLCD data because it is outside of the NLCD extent')) -->
<!--   } else{ -->
<!--     site_merc_point = from_crs1_to_crs2_lon_lat(lon_ = site_lon_wgs, lat_ = site_lat_wgs, from_crs = wgs_crs, to_crs = merc_crs) -->
<!--     site_lon_merc = site_merc_point@coords[[1]] -->
<!--     site_lat_merc = site_merc_point@coords[[2]] -->

<!--     width  = 15000 -->
<!--     height = 15000 -->

<!--     e      = as(extent(site_lon_alb - width, site_lon_alb + width, site_lat_alb - height, site_lat_alb + height), 'SpatialPolygons') -->

<!--     crs(e) = alb_crs -->

<!--     site_NLCD_lc_cropped      = raster::crop(NLCD_lc, e, snap='near') -->
<!--     site_NLCD_lc_cropped_merc = projectRaster(site_NLCD_lc_cropped, crs=merc_crs, method='ngb') -->

<!--     # Crop again in Merc -->
<!--     width  = 10000 -->
<!--     height = 10000 -->

<!--     e2 = as(extent(site_lon_merc - width, site_lon_merc + width, site_lat_merc - height, site_lat_merc + height), 'SpatialPolygons') -->
<!--     crs(e2) = merc_crs -->
<!--     site_NLCD_lc_final_merc = raster::crop(site_NLCD_lc_cropped_merc, e2, snap='near') -->

<!--     dir.create(output_dir) -->
<!--     file_name  = paste0(cam_site, '_landsat_lc') -->
<!--     output_file = paste0(output_dir, '/',file_name,'.tif') -->
<!--     raster::writeRaster(site_NLCD_lc_final_merc, output_file, format='GTiff', overwrite=TRUE) -->
<!--   } -->
<!-- } -->
<!-- ``` -->




