---
title: "find_best_pixel_match_sinu.Rmd"
author: "K. Enns"
date: "4/10/2019"
output: html_document
---

New version of best pixel_match notebook to use the sinusoidal data from AppEEARS instead of wgs84

Get token from appeears
```{r}
####################################################################################
# GO RUN global.R for variables and libraries required in this RMD file
####################################################################################
```

color palette
```{r}
library(plotly)
n = 400
colors_ = colorRampPalette(c('grey','black'))(n)
# colors_ = colorRampPalette(brewer.pal(n, 'Purples'))(n)
# colors_ = colorRampPalette(brewer.pal(n, 'RdYlBu'))(n)
a = rep(1, n)
b = seq(1, n)
# plot_ly(x = b, y = a, color = b, colors = colors_, type = 'bar')
```
``

grab acadia data
```{r}
test_download_dir = '../www/downloads_test'
if (!file.exists(test_download_dir)){
  dir.create(file.path(test_download_dir))
}
site_ = 'acadia'
# Grab acadia tasks for ndvi/evi/tds from cached AppEEARS dataframes
ndvi_task_t = appeears_tasks_ndvi_tera[grep(site_ ,appeears_tasks_ndvi_tera$task_name),]
ndvi_task_a = appeears_tasks_ndvi_aqua[grep(site_ ,appeears_tasks_ndvi_aqua$task_name),]
tds_task  = appeears_tasks_tds[grep(site_ ,appeears_tasks_tds$task_name),]
evi_task_t  = appeears_tasks_evi_tera[grep(site_ ,appeears_tasks_evi_tera$task_name),]
evi_task_a  = appeears_tasks_evi_aqua[grep(site_ ,appeears_tasks_evi_aqua$task_name),]
lc_task     = appeears_tasks_lc[grep(site_, appeears_tasks_lc$task_name),]
```

get task id for acadia datasets
```{r}
# Store the ID's specific to acadia and their data layer
ndvi_task_id_t = ndvi_task_t$task_id
ndvi_task_id_a = ndvi_task_a$task_id
tds_task_id  = tds_task$task_id
evi_task_id_t  = evi_task_t$task_id
evi_task_id_a  = evi_task_a$task_id
lc_task_id_nc  = lc_task$task_id
```

download data
```{r}
# Get bundle responses for ndvi tera
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", ndvi_task_id_t, sep = ""))
ndvi_bundle_response_t = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
# all files in bundle
document = jsonlite::fromJSON(txt=ndvi_bundle_response_t)
ndvi_files_t = document$files
if (!file.exists(paste0(test_download_dir, '/acadia_ndvi_t'))){
  dir.create(file.path(paste0(test_download_dir, '/acadia_ndvi_t')))
}

# Get bundle responses for ndvi aqua
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", ndvi_task_id_a, sep = ""))
ndvi_bundle_response_a = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
# all files in bundle
document = jsonlite::fromJSON(txt=ndvi_bundle_response_a)
ndvi_files_a = document$files
if (!file.exists(paste0(test_download_dir, '/acadia_ndvi_a'))){
  dir.create(file.path(paste0(test_download_dir, '/acadia_ndvi_a')))
}

# Get bundle responses for transition dates
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", tds_task_id, sep = ""))
tds_bundle_response = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
# all files in bundle
document = jsonlite::fromJSON(txt=tds_bundle_response)
tds_files = document$files
if (!file.exists(paste0(test_download_dir, '/acadia_tds'))){
  dir.create(file.path(paste0(test_download_dir, '/acadia_tds')))
}

# Get bundle responses for evi tera
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", evi_task_id_t, sep = ""))
evi_bundle_response_t = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
# all files in bundle
document = jsonlite::fromJSON(txt=evi_bundle_response_t)
evi_files_t = document$files
if (!file.exists(paste0(test_download_dir, '/acadia_evi_t'))){
  dir.create(file.path(paste0(test_download_dir, '/acadia_evi_t')))
}

# Get bundle responses for evi aqua
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", evi_task_id_a, sep = ""))
evi_bundle_response_a = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
# all files in bundle
document = jsonlite::fromJSON(txt=evi_bundle_response_a)
evi_files_a = document$files
if (!file.exists(paste0(test_download_dir, '/acadia_evi_a'))){
  dir.create(file.path(paste0(test_download_dir, '/acadia_evi_a')))
}

# Get bundle responses for LC nc
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", lc_task_id_nc, sep = ""))
lc_bundle_response_nc = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
# all files in bundle
document = jsonlite::fromJSON(txt=lc_bundle_response_nc)
lc_files_nc = document$files
if (!file.exists(paste0(test_download_dir, '/acadia_lc_nc'))){
  dir.create(file.path(paste0(test_download_dir, '/acadia_lc_nc')))
}

# # Get bundle responses for LC tiff
# response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", lc_task_id_tiff, sep = ""))
# lc_bundle_response_tiff = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
# # all files in bundle
# document = jsonlite::fromJSON(txt=lc_bundle_response_tiff)
# lc_files_tiff = document$files
# if (!file.exists(paste0(test_download_dir, '/acadia_lc_tiff'))){
#   dir.create(file.path(paste0(test_download_dir, '/acadia_lc_tiff')))
# }


# Download Landcover nc
lc_filepaths_nc = c()
for (file in lc_files_nc$file_id){
  download_this_file = file
  # # retrieve the filename from the file_id
  bundle = jsonlite::fromJSON(lc_bundle_response_nc)$files
  filename = subset(bundle, bundle$file_id == download_this_file)$file_name
  # create a destination directory to store the file in

  filepath = paste0(test_download_dir, '/acadia_lc_nc/',filename)
  print (filepath)
  lc_filepaths_nc = c(lc_filepaths_nc, filepath)
  #------------------------------------------------------------------------------------------
  #--------Comment out this bit of code if you don't want to download  NDVI-------
  # write the file to disk using the destination directory and file name
  # response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", lc_task_id_nc, '/',
  #                      download_this_file, sep = ""),
  #                write_disk(filepath, overwrite = TRUE), progress())
  #------------------------------------------------------------------------------------------
}

# # Download Landcover tiff
# lc_filepaths_tiff = c()
# for (file in lc_files_tiff$file_id){
#   download_this_file = file
#   # # retrieve the filename from the file_id
#   bundle = jsonlite::fromJSON(lc_bundle_response_tiff)$files
#   filename = subset(bundle, bundle$file_id == download_this_file)$file_name
#   # create a destination directory to store the file in
#   if (length(strsplit(filename, '/')[[1]]) >1){
#     if (!file.exists(paste0(test_download_dir, '/acadia_lc_tiff/',strsplit(filename, '/')[[1]][1]))){
#       dir.create(file.path(paste0(test_download_dir, '/acadia_lc_tiff/',strsplit(filename, '/')[[1]][1])))
#     }
#   }
# 
#   filepath = paste0(test_download_dir, '/acadia_lc_tiff/',filename)
#   print (filepath)
#   lc_filepaths_tiff = c(lc_filepaths_tiff, filepath)
#   #------------------------------------------------------------------------------------------
#   #--------Comment out this bit of code if you don't want to download  NDVI-------
#   # write the file to disk using the destination directory and file name
#   # response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", lc_task_id_tiff, '/',
#   #                      download_this_file, sep = ""),
#   #                write_disk(filepath, overwrite = TRUE), progress())
#   #------------------------------------------------------------------------------------------
# }




# Download ndvi tera
ndvi_filepaths_t = c()
for (file in ndvi_files_t$file_id){
  download_this_file = file
  # # retrieve the filename from the file_id
  bundle = jsonlite::fromJSON(ndvi_bundle_response_t)$files
  filename = subset(bundle, bundle$file_id == download_this_file)$file_name
  # create a destination directory to store the file in

  filepath = paste0(test_download_dir, '/acadia_ndvi_t/',filename)
  print (filepath)
  ndvi_filepaths_t = c(ndvi_filepaths_t, filepath)
  #------------------------------------------------------------------------------------------
  #--------Comment out this bit of code if you don't want to download  NDVI-------
  # write the file to disk using the destination directory and file name
  # response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", ndvi_task_id_t, '/',
  #                      download_this_file, sep = ""),
  #                write_disk(filepath, overwrite = TRUE), progress())
  #------------------------------------------------------------------------------------------
}
# Download ndvi aqua
ndvi_filepaths_a = c()
for (file in ndvi_files_a$file_id){
  download_this_file = file
  # # retrieve the filename from the file_id
  bundle = jsonlite::fromJSON(ndvi_bundle_response_a)$files
  filename = subset(bundle, bundle$file_id == download_this_file)$file_name
  # create a destination directory to store the file in

  filepath = paste0(test_download_dir, '/acadia_ndvi_a/',filename)
  print (filepath)
  ndvi_filepaths_a = c(ndvi_filepaths_a, filepath)
  #------------------------------------------------------------------------------------------
  #--------Comment out this bit of code if you don't want to download  NDVI-------
  # write the file to disk using the destination directory and file name
  # response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", ndvi_task_id_a, '/',
  #                      download_this_file, sep = ""),
  #                write_disk(filepath, overwrite = TRUE), progress())
  #------------------------------------------------------------------------------------------
}



# Download transition dates
tds_filepaths = c()
for (file in tds_files$file_id){
  download_this_file = file
  # # retrieve the filename from the file_id
  bundle = jsonlite::fromJSON(tds_bundle_response)$files
  filename = subset(bundle, bundle$file_id == download_this_file)$file_name
  # create a destination directory to store the file in
  filepath = paste0(test_download_dir, '/acadia_tds/',filename)
  print (filepath)
  tds_filepaths = c(tds_filepaths, filepath)
  #------------------------------------------------------------------------------------------
  #--------Comment out this bit of code if you don't want to download transition dates-------
  # write the file to disk using the destination directory and file name
  # response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", tds_task_id, '/',
  #                      download_this_file, sep = ""),
  #                write_disk(filepath, overwrite = TRUE), progress())
  #------------------------------------------------------------------------------------------
}

# Download evi tera
evi_filepaths = c()
for (file in evi_files_t$file_id){
  download_this_file = file
  # # retrieve the filename from the file_id
  bundle = jsonlite::fromJSON(evi_bundle_response_t)$files
  filename = subset(bundle, bundle$file_id == download_this_file)$file_name
  # create a destination directory to store the file in
  filepath = paste0(test_download_dir, '/acadia_evi_t/',filename)
  print (filepath)
  evi_filepaths = c(evi_filepaths, filepath)
  #------------------------------------------------------------------------------------------
  #--------Comment out this bit of code if you don't want to download EVI-------
  # write the file to disk using the destination directory and file name
  # response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", evi_task_id_t, '/',
  #                      download_this_file, sep = ""),
  #                write_disk(filepath, overwrite = TRUE), progress())
  #------------------------------------------------------------------------------------------
}
# Download evi aqua
evi_filepaths = c()
for (file in evi_files_a$file_id){
  download_this_file = file
  # # retrieve the filename from the file_id
  bundle = jsonlite::fromJSON(evi_bundle_response_a)$files
  filename = subset(bundle, bundle$file_id == download_this_file)$file_name
  # create a destination directory to store the file in
  filepath = paste0(test_download_dir, '/acadia_evi_a/',filename)
  print (filepath)
  evi_filepaths = c(evi_filepaths, filepath)
  #------------------------------------------------------------------------------------------
  #--------Comment out this bit of code if you don't want to download EVI-------
  # write the file to disk using the destination directory and file name
  # response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", evi_task_id_a, '/',
  #                      download_this_file, sep = ""),
  #                write_disk(filepath, overwrite = TRUE), progress())
  #------------------------------------------------------------------------------------------
}
```

Define crs strings
```{r}
# define number of digits to use
options(digits=12)
# defining CRS strings to use for geospatial conversions within the app
sinu_crs = "+proj=sinu +lon_0=0 +x_0=0 +y_0=0 +a=6371007.181 +b=6371007.181 +units=m +no_defs"
merc_crs = "+proj=merc +a=6378137 +b=6378137 +lat_ts=0.0 +lon_0=0.0 +x_0=0.0 +y_0=0 +k=1.0 +units=m +nadgrids=@null +wktext  +no_defs"
wgs_crs  = '+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs'
# coordinates for acadia center point phenocam
lat_merc = 5523962
lng_merc = -7598761
lat_sin = 4934497
lng_sin = -5425175
lng_wgs = -68.26083
lat_wgs = 44.37694

```

Read in sinusoidal landcover(500m) for acadia, display, transform, crop and compare to ndvi (250m)
```{r}
library(raster)
library(leaflet)
source('../functions/geospatial.R')
# Read in ndvi (250m sinusoidal)
ndvi_name = subset(ndvi_files_t, file_type == 'nc')$file_name
ndvi_path_t   = paste0(test_download_dir, '/acadia_ndvi_t/', ndvi_name)
ndvi_brick_t  = raster::brick(ndvi_path_t, varname='_250m_16_days_NDVI', crs = sinu_crs)
ndvi_raster_t = raster::subset(ndvi_brick_t, 1)

ndvi_name = subset(ndvi_files_a, file_type == 'nc')$file_name
ndvi_path_a   = paste0(test_download_dir, '/acadia_ndvi_a/', ndvi_name)
ndvi_brick_a  = raster::brick(ndvi_path_t, varname='_250m_16_days_NDVI', crs = sinu_crs)
ndvi_raster_a = raster::subset(ndvi_brick_t, 1)


# Read in landcover (500m sinusoidal)
lc_brick    = raster::brick(lc_filepaths_nc[1], crs=sinu_crs)
print (lc_brick)
lc_raster = raster::subset(lc_brick, 18)
lc_raster_ = raster::resample(x = lc_raster, y = ndvi_raster_t,crs = sinu_crs, method='ngb')

# Plot landcover and ndvi netcdf rasters over eachother in a regular in extent
# plot(lc_raster_, alpha = 1,col = colors_)
# plot(ndvi_raster_t, add=TRUE, alpha = .5)

# Plot landcover and ndvi netcdf rasters over eachother in a zoomed in extent
left = -5445000
bottom = 4925000
# plot(lc_raster_, alpha = 1,col = colors_, ext = c(left, left+5000, bottom, bottom+5000))
# plot(ndvi_raster_t, add=TRUE, alpha = .5, ext = c(left, left+5000, bottom, bottom+5000))

# Re-Project the landcover sinusoidal and ndvi sinusoidal into mercator
# ndvi_raster_merc  = projectRaster(from = ndvi_raster_t, crs = merc_crs, res = 231.6563582638875)
ndvi_raster_merc  = projectRaster(from = ndvi_raster_t, crs = merc_crs, res = res(ndvi_raster_t))
ndvi_62           = projectRaster(from = ndvi_raster_t, crs = merc_crs, res = res(ndvi_raster_t)/4, method = 'ngb')

# lc_raster_merc_62   = projectRaster(from = lc_raster_, crs = merc_crs, method='ngb', res = res(ndvi_raster_t)/4)
# lc_raster_merc_125  = projectRaster(from = lc_raster_, crs = merc_crs, method='ngb', res = res(ndvi_raster_t)/2)
lc_raster_merc_250  = projectRaster(from = lc_raster_, crs = merc_crs, method='ngb', res = res(ndvi_raster_t))
# lc_raster_merc_500  = projectRaster(from = lc_raster_, crs = merc_crs, method='ngb', res = res(ndvi_raster_t)*2)

# # Display Re-projected mercator ndvi and landcover 
# leaflet() %>% addTiles() %>% addRasterImage(lc_raster_merc_250, opacity = 1, colors = colors_) %>% addRasterImage(ndvi_raster_merc, opacity = .2)

# Crop the Re-projected mercator ndvi and landcover to 20000 m from center
r_250_m_cropped_merc_20 = crop_raster(lat_merc, lng_merc, ndvi_raster_merc, height = 20000, width = 20000, crs_str = merc_crs)
r_500_m_cropped_merc_20 = crop_raster(lat_merc, lng_merc, lc_raster_merc_250, height = 20000, width = 20000, crs_str = merc_crs)

# # Display Cropped, Re-projected mercator ndvi and landcover
# leaflet() %>% addTiles() %>% addRasterImage(r_500_m_cropped_merc_20, opacity = 1, colors = colors_) %>% addRasterImage(r_250_m_cropped_merc_20, opacity = .2)

# Create grid for the ndvi layer (same as app)
grid_250 = build_raster_grid(r_250_m_cropped_merc_20, crs='merc')
grid_500 = build_raster_grid(r_500_m_cropped_merc_20, crs='merc')

# leaflet() %>% addTiles() %>% addRasterImage(ndvi_62, opacity = 1, colors = colors_) %>%
#   addPolygons(data = grid_250, weight = .8, color = 'orange') %>% setView(lng = lng_wgs, lat = lat_wgs,zoom = 12)


# leaflet() %>% addTiles() %>% addRasterImage(lc_raster_merc_62, opacity = 1, colors = colors_) %>%
#   addPolygons(data = grid_250, weight = .8, color = 'orange') %>% setView(lng = lng_wgs, lat = lat_wgs,zoom = 12)
# 
# leaflet() %>% addTiles() %>% addRasterImage(lc_raster_merc_125, opacity = 1, colors = colors_) %>% 
#   addPolygons(data = grid_250, weight = .8, color = 'orange') %>% setView(lng = lng_wgs, lat = lat_wgs,zoom = 12)
# 
# leaflet() %>% addTiles() %>% addRasterImage(lc_raster_merc_250, opacity = 1, colors = colors_) %>%
#   addPolygons(data = grid_250, weight = .8, color = 'orange') %>% setView(lng = lng_wgs, lat = lat_wgs,zoom = 12)
# 
# leaflet() %>% addTiles() %>% addRasterImage(lc_raster_merc_500, opacity = 1, colors = colors_) %>%
#   addPolygons(data = grid_250, weight = .8, color = 'orange') %>% setView(lng = lng_wgs, lat = lat_wgs,zoom = 12)
```




Extract all the pixel center points and create a dataframe with id/lat/lng 
```{r}
source('../functions/geospatial.R')
# Values needed to calculate center pixels to use on analysis of netcdf data

r_         = crop_raster(lat_merc, lng_merc, ndvi_raster_merc, height = 2500, width = 2500, crs_str = merc_crs)
ndvi_grid  = build_raster_grid(r_, crs='merc')
xmin       = xmin(extent(r_))
xmax       = xmax(extent(r_))
ymin       = ymin(extent(r_))
ymax       = ymax(extent(r_))
nrows      = nrow(r_)
ncols      = ncol(r_)
resolution = res(r_)[1]

lats_merc = c()
lngs_merc = c()
ids = c()
lng_start = xmin + .5*(resolution)
lat_start = ymax + .5*(resolution)
for (row in c(1:nrows)){
  for (col in c(1:ncols)){
    lng = lng_start + (resolution)*(col-1)
    lat = lat_start - (resolution)*(row)
    id = paste0(row, '_',col)
    lngs_merc = c(lngs_merc,lng)
    lats_merc = c(lats_merc,lat)
    ids = c(ids, id)
  }
}

coords_wgs = from_crs1_to_crs2_lon_lat(lngs_merc, lats_merc, from_crs = merc_crs, to_crs = wgs_crs)
lngs_wgs = coordinates(coords_wgs)[,1]
lats_wgs = coordinates(coords_wgs)[,2]

coords_sin = from_crs1_to_crs2_lon_lat(lngs_merc, lats_merc, from_crs = merc_crs, to_crs = sinu_crs)
lngs_sin = coordinates(coords_sin)[,1]
lats_sin = coordinates(coords_sin)[,2]

pixel_ids = c(1:(ncols*nrows))
all_site_pixels_df = data.frame(pixel_id=pixel_ids, row_col = ids,
                                lat_merc_ = lats_merc, lng_merc_ = lngs_merc , 
                                lat_wgs_  = lats_wgs,  lng_wgs_  = lngs_wgs, 
                                lat_sin_  = lats_sin,  lng_sin_  = lngs_sin, 
                                site='acadia')
all_site_pixels_df

```

Check to make sure we are using the correct lats/lngs for the site
  - sanity check
```{r}
# leaflet() %>% addTiles() %>% addRasterImage(r_) %>%
#   addCircleMarkers(lat = all_site_pixels_df$lat_wgs_, lng = all_site_pixels_df$lng_wgs_, radius = 1, weight=3, opacity = 1, color='black') %>%
#   addPolylines(data = ndvi_grid, weight = 1.8, opacity = 1, group = '250m MODIS Grid', color = 'darkgrey') %>%
#   setView(lng = lng_wgs, lat = lat_wgs, zoom = 14)
```

build points to use for extracting aginst NDVI
```{r}
# use the all_site_pixels_df dataframe
coords_ = data.frame(x = all_site_pixels_df$lng_sin_, y = all_site_pixels_df$lat_sin_)
row.names(coords_) = all_site_pixels_df$row_col
center_points = SpatialPointsDataFrame(coords_, data=data.frame(ID=all_site_pixels_df$pixel_id, row_col = all_site_pixels_df$row_col ), proj4string=CRS(sinu_crs))
```


extract using a projected raster from sinusoidal into mercator 
- ngb method for qc (categorical)
- bilinear interpolation for ndvi (continous)
```{r}
# Read in ndvi (250m sinusoidal)
ndvi_name = subset(ndvi_files_t, file_type == 'nc')$file_name
ndvi_path_t   = paste0(test_download_dir, '/acadia_ndvi_t/', ndvi_name)
ndvi_brick_t  = raster::brick(ndvi_path_t, varname='_250m_16_days_NDVI', crs = sinu_crs)
ndvi_qc_brick_t  = raster::brick(ndvi_path_t, varname='_250m_16_days_VI_Quality', crs = sinu_crs)
# ndvi_brick_merc_t  = projectRaster(from = ndvi_brick_t, crs = merc_crs, res = res(ndvi_raster_t))
# ndvi_qc_brick_merc_t  = projectRaster(from = ndvi_qc_brick_t, crs = merc_crs, res = res(ndvi_raster_t))

ndvi_name = subset(ndvi_files_a, file_type == 'nc')$file_name
ndvi_path_a   = paste0(test_download_dir, '/acadia_ndvi_a/', ndvi_name)
ndvi_brick_a  = raster::brick(ndvi_path_t, varname='_250m_16_days_NDVI', crs = sinu_crs)
ndvi_qc_brick_a  = raster::brick(ndvi_path_t, varname='_250m_16_days_VI_Quality', crs = sinu_crs)
# ndvi_brick_merc_a  = projectRaster(from = ndvi_brick_a, crs = merc_crs, res = res(ndvi_raster_t))
# ndvi_qc_brick_merc_a  = projectRaster(from = ndvi_qc_brick_a, crs = merc_crs, res = res(ndvi_raster_t))

```

# Extract the values under the center points from the grid we are using
```{r}
ndvi_under_pixel_tera    = raster::extract(ndvi_brick_t, center_points)
qc_ndvi_under_pixel_tera = raster::extract(ndvi_qc_brick_t, center_points)

ndvi_under_pixel_aqua    = raster::extract(ndvi_brick_a, center_points)
qc_ndvi_under_pixel_aqua = raster::extract(ndvi_qc_brick_a, center_points)
```


# Build the dataframe with all the compiled information from the extracted values
```{r}
ndvi_filepaths_t
read.csv(ndvi_filepaths_t[3])
qc_df = read.csv(ndvi_filepaths_t[2])
unique(qc_df$VI.Usefulness)
qc_df
```


```{r}
subset(qc_df, qc_df$VI.Usefulness == 'Highest quality')
```
```{r}
subset(qc_df, qc_df$VI.Usefulness == 'Decreasing quality')
app_qc_values = c(68, 2112, 2116, 2181, 2372, 4160, 4164, 4229, 6208, 6212, 6277)

subset(qc_df, qc_df$Value %in% app_qc_values)

unique(qc_df$MODLAND)
```

NDVI qc filters with the qc lookup table
```{r}
tera_qc = read.csv('../www/site_data/acadia/data_layers/ndvi/tera/MOD13Q1-006-250m-16-days-VI-Quality-lookup.csv', stringsAsFactors = FALSE) 
aqua_qc = read.csv('../www/site_data/acadia/data_layers/ndvi/aqua/MYD13Q1-006-250m-16-days-VI-Quality-lookup.csv', stringsAsFactors = FALSE)

t_app_qc_values_df = subset(tera_qc, tera_qc$MODLAND == 'VI produced with good quality' & tera_qc$VI.Usefulness == 'Decreasing quality' | 
    tera_qc$VI.Usefulness == 'Highest quality' & tera_qc$MODLAND == 'VI produced with good quality')
t_qc_values = t_app_qc_values_df$Value
t_qc_values

a_app_qc_values_df = subset(aqua_qc, aqua_qc$MODLAND == 'VI produced with good quality' & aqua_qc$VI.Usefulness == 'Decreasing quality' | 
    aqua_qc$VI.Usefulness == 'Highest quality' & aqua_qc$MODLAND == 'VI produced with good quality')
a_qc_values = a_app_qc_values_df$Value
a_qc_values

```

NDVI qc filters with the qc lookup table
```{r}
tera_qc_evi = read.csv('../www/site_data/acadia/data_layers/evi/tera/MOD13Q1-006-250m-16-days-VI-Quality-lookup.csv', stringsAsFactors = FALSE) 
aqua_qc_evi = read.csv('../www/site_data/acadia/data_layers/evi/aqua/MYD13Q1-006-250m-16-days-VI-Quality-lookup.csv', stringsAsFactors = FALSE)

t_app_qc_values_df_evi = subset(tera_qc_evi, tera_qc_evi$MODLAND == 'VI produced with good quality' & tera_qc_evi$VI.Usefulness == 'Decreasing quality' | 
    tera_qc_evi$VI.Usefulness == 'Highest quality' & tera_qc_evi$MODLAND == 'VI produced with good quality')
t_qc_values_evi = t_app_qc_values_df_evi$Value
t_qc_values_evi

a_app_qc_values_df_evi = subset(aqua_qc_evi, aqua_qc_evi$MODLAND == 'VI produced with good quality' & aqua_qc_evi$VI.Usefulness == 'Decreasing quality' | 
    aqua_qc_evi$VI.Usefulness == 'Highest quality' & aqua_qc_evi$MODLAND == 'VI produced with good quality')
a_qc_values_evi = a_app_qc_values_df_evi$Value
a_qc_values_evi

```



```{r}
app_qc_values_df = subset(qc_df, qc_df$MODLAND == 'VI produced with good quality' & qc_df$VI.Usefulness == 'Decreasing quality' | 
    qc_df$VI.Usefulness == 'Highest quality' & qc_df$MODLAND == 'VI produced with good quality')
app_qc_values = app_qc_values_df$Value
app_qc_values_df
```


```{r}
for (num in c (1:length(center_points@data$ID))){
  pixel_id = center_points@data$ID[num]
  row_col  = center_points@data$row_col[num]
  
  ndvi_tera = ndvi_under_pixel_tera[num,]
  ndvi_qc_tera = qc_ndvi_under_pixel_tera[num,]
  
  ndvi_aqua = ndvi_under_pixel_aqua[num,]
  ndvi_qc_aqua = qc_ndvi_under_pixel_aqua[num,]
  
  dates_tera = as.Date(names(ndvi_tera),format='X%Y.%m.%d')
  min_date_t = min(dates_tera)
  max_date_t = max(dates_tera)
  
  dates_aqua = as.Date(names(ndvi_aqua),format='X%Y.%m.%d')
  min_date_a = min(dates_aqua)
  max_date_a = max(dates_aqua)
  
  
  tera_qc_counts = as.data.frame(table(as.vector(ndvi_qc_tera)))
  tera_qc_counts_merged = base::merge(tera_qc_counts, qc_df, by.x = 'Var1', by.y = 'Value')
  
  aqua_qc_counts = as.data.frame(table(as.vector(ndvi_qc_tera)))
  aqua_qc_counts_merged = base::merge(tera_qc_counts, qc_df, by.x = 'Var1', by.y = 'Value')

  ndvi_brick_df_tera = data.frame(date     = dates_tera, 
                                  pixel    = pixel_id, 
                                  row_col  = row_col,
                                  ndvi_raw = as.vector(ndvi_tera), 
                                  ndvi_qc  = as.vector(ndvi_qc_tera),
                                  type     = 'TERA')
  ndvi_brick_df_aqua = data.frame(date     = dates_aqua, 
                                  pixel    = pixel_id, 
                                  row_col  = row_col,
                                  ndvi_raw = as.vector(ndvi_aqua), 
                                  ndvi_qc  = as.vector(ndvi_qc_aqua),
                                  type     = 'AQUA')
  ndvi_brick_df = rbind(ndvi_brick_df_tera, ndvi_brick_df_aqua)
  
  
  
  # Add ndvi_brick_df data (one pixel worth) to a larger df with all pixels and ndvi
  if (num == 1){
    ndvi_pixel_data_df = ndvi_brick_df
  }else {
    ndvi_pixel_data_df = rbind(ndvi_pixel_data_df, ndvi_brick_df)
  }}
  
ndvi_pixel_data_df$ndvi_filtered = ifelse(ndvi_pixel_data_df$ndvi_qc == 2112 | ndvi_pixel_data_df$ndvi_qc == 2114, 
                                          ndvi_pixel_data_df$ndvi_raw, NA)

```

Lets run some basic analysis on this dataset for Acadia. 
```{r}



dim(ndvi_pixel_data_df)


# Grab
test_pixel = subset(ndvi_pixel_data_df, row_col == '5_5')

# Grab TERA only
tera_df = subset(test_pixel, type == 'TERA')

# Display dates
date_ = tera_df$date
min_date = min(date_)
max_date = max(date_)
print (min_date)
print (max_date)

```


















































