---
title: "landcover_v006_inspection.Rmd"
author: "K. Enns"
date: "6/12/2019"
output: html_document
---

## This notebook downloads and visualizes the landcover layer from MODIS across NA

Get token for AppEEARS
```{r}
####################################################################################
# GO RUN global.R for variables and libraries required in this RMD file
####################################################################################

# devtools::install_github("ennsk/AppEEARS4R")
library(jsonlite)
library(appeears)
library(httr)
# username = ''
# password = ''
# token_response = appeears::appeears_start_session(username,password)
# rm(password)
# token         = paste("Bearer", token_response$token)
# response      = GET("https://lpdaacsvc.cr.usgs.gov/appeears/api/task", add_headers(Authorization = token))
# task_response = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
# tasks = jsonlite::fromJSON(txt=task_response)
```


```{r}
# tasks[grep(c('landcover'), tasks$task_name),]
files = get_appeears_bundle_df('48d7ab5d-2b4c-46d0-925f-003a5a4479f4')
files

# response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", '48d7ab5d-2b4c-46d0-925f-003a5a4479f4', '/', '1b518b73-d2d6-4067-a3a6-6a24863a8e97', sep = ""), write_disk('/users/kenns/downloads/MCD12Q1.006_LC_Type1_doy2017001_aid0001.tif', overwrite = TRUE), progress())
```
bring in tif of 2017 v006 layer
```{r}
# acadia
# lat = 44.3769444444
# lng = -68.2608333333

# Konza 39.0824, -96.5603
lat = 39.0824
lng = -96.5603

lnd_cover = raster('/users/kenns/downloads/MCD12Q1.006_LC_Type1_doy2017001_aid0001.tif')
lnd_cover_original = raster('/users/kenns/projects/r/apis/phenosynth/www/global_landcover_2016.tif')
# overlap = lnd_cover - lnd_cover_original
lnd_cover
lnd_cover_2017_cropped = crop_raster(lat, lng, lnd_cover, height = .03, width=.05)
library(leaflet)
leaflet() %>% addTiles() %>% addRasterImage(lnd_cover_2017_cropped)
# leaflet() %>% addTiles() %>% addRasterImage(overlap)
```


Converting Landcover Landsat layer from albers to wgs84
```{r}
NLCD_lc = raster::raster('/Users/kenns/Downloads/NLCD_2016_Land_Cover_L48_20190424/NLCD_2016_Land_Cover_L48_20190424.img')
landsat_atts = NLCD_lc@data@attributes
get_x_y_albers_from_wgs84 = function(lon_,lat_){
  xy              = data.frame(matrix(c(lon_,lat_), ncol=2))
  colnames(xy)    = c('lon', 'lat')
  coordinates(xy) = ~ lon + lat
  proj4string(xy) = CRS("+proj=longlat +datum=WGS84")
  p               = spTransform(xy, CRS("+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
  return (p)
}
lat = 39.0824
lng = -96.5603
albs_point = get_x_y_albers_from_wgs84(lng,lat)
lng = albs_point@coords[[1]]
lat = albs_point@coords[[2]]

# Crop in Albers
width  = 12000
height = 12000
e      = as(extent(lng - width, lng + width, lat - height, lat + height), 'SpatialPolygons')
crs(e) <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
NLCD_lc_cropped        = raster::crop(NLCD_lc, e, snap='near')
NLCD_lc_cropped_wgs = projectRaster(NLCD_lc_cropped, crs="+proj=longlat +datum=WGS84", method='ngb')

# Crop again in WGS
width  = .05
height = .03
lat = 39.0824
lng = -96.5603
e2 =as(extent(lng - width, lng + width, lat - height, lat + height), 'SpatialPolygons')
crs(e2) <- "+proj=longlat +datum=WGS84"
NLCD_lc_final_wgs = raster::crop(NLCD_lc_cropped_wgs, e2, snap='near')

# Display using leaflet
leaflet() %>% addTiles() %>% addRasterImage(NLCD_lc_cropped_wgs)
leaflet() %>% addTiles() %>% addRasterImage(NLCD_lc_final_wgs)
            
# remove large raster layer out of memory so .rmd doesn't freeze
rm(NLCD_lc)
```



Converting Landcover Landsat layer from albers to web mercator 
```{r}
NLCD_lc = raster::raster('/Users/kenns/Downloads/NLCD_2016_Land_Cover_L48_20190424/NLCD_2016_Land_Cover_L48_20190424.img')
landsat_atts = NLCD_lc@data@attributes

get_x_y_albers_from_wgs84 = function(lon_,lat_){
  xy              = data.frame(matrix(c(lon_,lat_), ncol=2))
  colnames(xy)    = c('lon', 'lat')
  coordinates(xy) = ~ lon + lat
  proj4string(xy) = CRS("+proj=longlat +datum=WGS84")
  p               = spTransform(xy, CRS("+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"))
  return (p)
}

get_x_y_merc_from_wgs84 = function(lon_,lat_){
  xy              = data.frame(matrix(c(lon_,lat_), ncol=2))
  colnames(xy)    = c('lon', 'lat')
  coordinates(xy) = ~ lon + lat
  proj4string(xy) = CRS("+proj=longlat +datum=WGS84")
  p               = spTransform(xy, CRS('+init=EPSG:3857'))
  return (p)
}

# lat = 44.3769444444
# lng = -68.2608333333
lat = 39.0824
lng = -96.5603
albs_point = get_x_y_albers_from_wgs84(lng,lat)
merc_point = get_x_y_merc_from_wgs84(lng,lat)
lng = albs_point@coords[[1]]
lat = albs_point@coords[[2]]

# Crop in Albers
width  = 12000
height = 12000
e      = as(extent(lng - width, lng + width, lat - height, lat + height), 'SpatialPolygons')
crs(e) <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
NLCD_lc_cropped        = raster::crop(NLCD_lc, e, snap='near')
NLCD_lc_cropped_merc = projectRaster(NLCD_lc_cropped, crs=CRS('+init=EPSG:3857'), method='ngb')



# Crop in Mercator
merc_width  = 5000
merc_height = 5000
merc_lng = merc_point@coords[[1]]
merc_lat = merc_point@coords[[2]]

e      = as(extent(merc_lng - merc_width, merc_lng + merc_width, merc_lat - merc_height, merc_lat + merc_height), 'SpatialPolygons')
crs(e) <- CRS('+init=EPSG:3857')
NLCD_lc_final_merc  = raster::crop(NLCD_lc_cropped_merc, e, snap='near')

# Display using leaflet
leaflet() %>% addTiles() %>% addRasterImage(NLCD_lc_cropped_merc)
leaflet() %>% addTiles() %>% addRasterImage(NLCD_lc_final_merc)

# remove large raster layer out of memory so .rmd doesn't freeze
rm(NLCD_lc)
```

Pull one modis pixel, clip it to the landcover, and find % of landcover types
```{r}
modis_lc   = lnd_cover_2017_cropped 
landsat_lc = NLCD_lc_final_wgs

lat = 39.0824
lng = -96.5603

single_raster_pixel = crop_raster(lat, lng, modis_lc, height = .005, width=.005)
leaflet() %>% addTiles() %>% addRasterImage(single_raster_pixel)

new_landsat_lc = crop(landsat_lc, single_raster_pixel, snap='near')
leaflet() %>% addTiles() %>% addRasterImage(new_landsat_lc)

# Run this calculation to get % homogeneity of MODIS pixel
percent = is.element(landsat_lc@data@values,71)
sum(percent)/length(landsat_lc@data@values)*100

```





attributes for landsat landcover cropped raster
```{r}
key_df = subset(landsat_atts[[1]], landsat_atts[[1]]$COUNT != 0)
key_df
```

reclassify the layers into categories 1-17 like in pft from landcover
```{r}
# IDs
ids      = key_df$ID
lc_types = key_df$NLCD.Land.Cover.Class
```

create the new color palette for landsat
```{r}

build_landsat_lc_pallet = function(raster_, us_landsat_lc, landsat_key){
  print ('building landsat landcover palette')
  landsat_atts_ = us_landsat_lc@data@attributes
  key_df = subset(landsat_atts_[[1]], landsat_atts_[[1]]$COUNT != 0)
  print (key_df)
  colors = c()
  names  = c()
  color_list    = c('#1b8a28', '#36d03e', '#9ecb30', '#a0f79f', '#91bb88', '#b99091', '#f0dfb8', '#d6ed9a',
                    '#f1dc07', '#ecbb5b', '#4981b1', '#fcee72', '#fd0608', '#9b9353', '#bdbec0', '#bdbec0', '#89cae3')
  
  v = unique(values(raster_))
  remove = c(NA)
  v = v [! v %in% remove]
  v = sort(v, decreasing = FALSE)
  
  print (v)
  
  count = 0
  for (x in v){
    count = count + 1
      
    red = subset(landsat_key, landsat_key$ID == x)$Red/255
    green = subset(landsat_key, landsat_key$ID == x)$Green/255
    blue = subset(landsat_key, landsat_key$ID == x)$Blue/255
    color = rgb(red,green,blue)
    colors = c(colors, color)
    # colors = c(colors, color_list[count])
    name   = as.character(subset(landsat_key, landsat_key$ID == x)$NLCD.Land.Cover.Class)
    names  = c(names, name)
  }
  colors_ = list('colors' = colors, 'names' = names)
  return (colors_)
}

us_landsat_lc =  raster::raster('/Users/kenns/Downloads/NLCD_2016_Land_Cover_L48_20190424/NLCD_2016_Land_Cover_L48_20190424.img')
c = build_landsat_lc_pallet(NLCD_lc_final_wgs, us_landsat_lc, key_df)
rm(us_landsat_lc)

leaflet() %>% addTiles() %>% addRasterImage(NLCD_lc_final_wgs, colors = c$colors, opacity = .7) %>%
  addLegend(labels = c$names, colors = c$colors, position = "bottomleft", opacity = .95, title = 'MODIS Landcover')
# run to get nothing


```



# Give the MODIS Landcover layer feedback (homogeneity) using the landsat layer
```{r}
# Landsat (extent is .06 x .06)
lnd_cover_2017_cropped
# MODIS   (extent is .05 x .05)
NLCD_lc_final_wgs
```


# First test will be for WATER, see how homogeneous the water pixels in MODIS are based on landsat lc

Extract all the pixel center points/boundary box and create a dataframe with id/lat/lng 
```{r}
# Values needed to calculate center pixels to use on analysis of netcdf data
r_         = cropped_ndvi
xmin       = xmin(extent(r_))
xmax       = xmax(extent(r_))
ymin       = ymin(extent(r_))
ymax       = ymax(extent(r_))
nrows      = nrow(r_)
ncols      = ncol(r_)
resolution = res(r_)[1]

lngs = c()
lats = c()
lng_start = xmin + .5*(resolution)
lat_start = ymax + .5*(resolution)
for (row in c(1:nrows)){
  for (col in c(1:ncols)){
    lng = lng_start + (resolution)*(col-1)
    lat = lat_start - (resolution)*(row)
    lngs = c(lngs,lng)
    lats = c(lats,lat)
  }
}
pixel_ids = c(1:(ncols*nrows))
all_site_pixels_df = data.frame(pixel_id=pixel_ids, lat = lats, lng = lngs, site='acadia')
all_site_pixels_df
```


test
```{r}
library(raster)
r1 <- raster(matrix(1:4, nrow=4, ncol=4))
r2 <- raster(matrix(runif(16),nrow=4))
# x <- overlay(r1, r2, fun=function(x,y){ y[x==1] = .5; y[x==2] = .2; y})
x <- overlay(r1, r2, fun=function(x,y){ y[x==1] = .5; y[x==2] = .2; y})

plot(x)
```
```{r}
plot(r1)
```

```{r}
plot(r2)
```














# OLD LAYERS
```{r}
# Read in the nc file we downloaded above (landcover version 6)
lat = 40
lng = -105

lnd_cover = raster::brick('/Users/kenns/Downloads/MCD12Q1.006_500m_aid0001.nc', 'LC_Type1')
lnd_cover_2017 = subset(lnd_cover, 17)

lnd_cover_2017_cropped = crop_raster(lat, lng, lnd_cover_2017, height = 5, width=5)
library(leaflet)
leaflet() %>% addTiles() %>% addRasterImage(lnd_cover_2017_cropped, opacity = .5)
```
old layer
```{r}
old_lnd_cover = raster::raster('/users/kenns/projects/r/apis/phenosynth/www/global_landcover_2016.tif')
old_lnd_cover
```




































