---
title: "landsat_landcover.Rmd"
author: "K. Enns"
date: "12/05/2019"
output: html_document
---

### This notebook will be used to build out a structure for storing as well as storing cropped landcover landsat data to all phenocam sites


Converting Landcover Landsat layer from albers to wgs84
```{r}
# Download the NLCD 2016 CON"US landcover layers from online"
library(raster)
NLCD_lc = raster::raster('/Users/kenns/Downloads/NLCD_2016_Land_Cover_L48_20190424/NLCD_2016_Land_Cover_L48_20190424.img')
landsat_atts = NLCD_lc@data@attributes
```

CRS values
```{r}
merc_crs = "+proj=merc +a=6378137 +b=6378137 +lat_ts=0.0 +lon_0=0.0 +x_0=0.0 +y_0=0 +k=1.0 +units=m +nadgrids=@null +wktext  +no_defs"
wgs_crs  = "+proj=longlat +datum=WGS84"
alb_crs  = "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
```

Get site information for phenocam locations
```{r}
# Run the global file
setwd('/path/to/phenosynth') # set this to your project directory (setwd('/path/to/phenosynth'))
source('/path/to/phenosynth/global.R')
```

Get lat/lon for phenocam sites, reproject to merc, crop, and save out raster
```{r}
sites = cams_$site
output_dir = '../www/landsat_lc'

for (cam_site in sites[1]){
  print (cam_site)
  cam_site = 'NEON.D15.ONAQ.DP1.00033'
  site_row = subset(cams_, cams_$site == cam_site)
  site_lat_wgs = site_row$lat
  site_lon_wgs = site_row$lon

  site_albs_point = from_crs1_to_crs2_lon_lat(lon_ = site_lon_wgs, lat_ = site_lat_wgs, from_crs = wgs_crs, to_crs = alb_crs)
  site_lon_alb = site_albs_point@coords[[1]]
  site_lat_alb = site_albs_point@coords[[2]]
  
  site_sinu_point = from_crs1_to_crs2_lon_lat(lon_ = site_lon_wgs, lat_ = site_lat_wgs, from_crs = wgs_crs, to_crs = sinu_crs)
  site_lon_sinu = site_sinu_point@coords[[1]]
  site_lat_sinu = site_sinu_point@coords[[2]]

  if (is.na(extract(NLCD_lc, site_albs_point)[1])){
    print (paste0(cam_site, ' does not have NLCD data because it is outside of the NLCD extent'))
  } else{
    site_merc_point = from_crs1_to_crs2_lon_lat(lon_ = site_lon_wgs, lat_ = site_lat_wgs, from_crs = wgs_crs, to_crs = merc_crs)
    site_lon_merc = site_merc_point@coords[[1]]
    site_lat_merc = site_merc_point@coords[[2]]

    width  = 15000
    height = 15000

    e      = as(extent(site_lon_alb - width, site_lon_alb + width, site_lat_alb - height, site_lat_alb + height), 'SpatialPolygons')

    crs(e) = alb_crs

    site_NLCD_lc_cropped      = raster::crop(NLCD_lc, e, snap='near')
    site_NLCD_lc_cropped_merc = projectRaster(site_NLCD_lc_cropped, crs=merc_crs, method='ngb')

    # Crop again in Merc
    width  = 10000
    height = 10000

    e2 = as(extent(site_lon_merc - width, site_lon_merc + width, site_lat_merc - height, site_lat_merc + height), 'SpatialPolygons')
    crs(e2) = merc_crs
    site_NLCD_lc_final_merc = raster::crop(site_NLCD_lc_cropped_merc, e2, snap='near')

    dir.create(output_dir)
    file_name  = paste0(cam_site, '_landsat_lc')
    output_file = paste0(output_dir, '/',file_name,'.tif')
    raster::writeRaster(site_NLCD_lc_final_merc, output_file, format='GTiff', overwrite=TRUE)
  }
}
```

grab 1 raster from cached data
```{r}
# cam_site   = 'NEON.D15.ONAQ.DP1.00033'
output_dir = '../www/landsat_lc'
test_raster_file = paste0(output_dir, '/', cam_site, '_landsat_lc.tif')
test_raster = raster::raster(test_raster_file)
test_raster
```

Create the NLCD cross walk dataframe to MODIS classifications
```{r}
landsat_lc = read_csv("../www/Landsat.Landcover.csv")
# Read in csv for landsat landcover - modis landcover cross walk and remove NA values for Landsat
landsat_lc_lookup = read.csv('../www/landsat_lc/nlcd_key.csv') %>% 
  dplyr::select(ID,NLCD.Land.Cover.Class) %>% left_join(landsat_lc, by = c('ID' = 'Landsat.Class')) %>%
  mutate(MODIS.Class = replace(MODIS.Class, ID == 12, NA)) %>%
  left_join(pft_df, by = c('MODIS.Class' = 'pft_key')) %>% dplyr::select(-Desc.)
landsat_lc_lookup

landsat_lc_r = test_raster
unique_landsat_lc_values = unique(values(landsat_lc_r))
```


Reclassify the landsat landcover raster into MODIS values (0-17)
```{r}
# Build crosswalk matrix for reclassify function (rcl)
from_values    = landsat_lc_lookup$ID
becomes_values = landsat_lc_lookup$MODIS.Class

m = matrix(ncol = 2, nrow = length(from_values))
m[,1] = from_values
m[,2] = becomes_values

# Reclassify the Landsat landcover to match the crosswalk csv
landsat_reclass_lc_r = reclassify(landsat_lc_r, m)

# unique(read.csv('../www/landsat_lc/nlcd_key.csv')$ID)
# data.frame(landsat_id = unique(read.csv('../www/landsat_lc/nlcd_key.csv')$ID)) 

```

Use build_pft_palette on landsat reclassified to match modis classification system
```{r}
source('../functions/geospatial.R')
colors_landsat_reclass = build_pft_palette(landsat_reclass_lc_r)
colors_landsat_reclass

print ('building palet')
colors = c()
names  = c()

hash_colors    = c('#1b8a28', '#36d03e', '#9ecb30', '#a0f79f', '#91bb88', '#b99091', '#f0dfb8', '#d6ed9a',
                  '#f1dc07', '#ecbb5b', '#4981b1', '#fcee72', 'red', '#9b9353', '#bdbec0', '#bdbec0', '#89cae3')
id = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17)
common_name = c('dark green', 'green', 'swamp green', 'light green', 'grey green', 'purple brown',
                'beige', 'green beige', 'orange yellow', 'orange', 'dark blue', 'light yellow', 
                'red', 'brown', 'grey', 'grey', 'light blue')
all_names   = c(pft_df[2:17,]$pft_expanded, 'Water')
lc_colors_df  = data.frame(id = id, hash_colors = hash_colors, pft =  all_names,common_name = common_name, stringsAsFactors = FALSE)
lc_colors_df
leaflet() %>% addTiles() %>% addRasterImage(landsat_reclass_lc_r, colors = colors_$colors, opacity = 1) %>%
  addLegend(labels = all_names, colors = all_colors, position = "topright", opacity = .95, title = 'MODIS Landcover')



v = unique(values(landsat_reclass_lc_r))
remove = c(NA)
v = v [! v %in% remove]
v = sort(v, decreasing = FALSE)
v

for (x in v){
  if (x == 17 | x == 0){
    colors = c(colors,hash_colors[17])
    name   = as.character(subset(pft_df, pft_df$pft_key == 0)$pft_expanded)
    names  = c(names, name)
  }else{
    colors = c(colors, hash_colors[x])
    name   = as.character(subset(pft_df, pft_df$pft_key == x)$pft_expanded)
    names  = c(names, name)
  }
}
v
colors_ = list('colors' = colors, 'names' = names, 'pft_key' = v)
colors_

all_colors = hash_colors
  
leaflet() %>% addTiles() %>% addRasterImage(landsat_reclass_lc_r, colors = colors_$colors, opacity = 1) %>%
  addLegend(labels = colors_$names, colors = colors_$colors, position = "bottomleft", opacity = .95, title = 'MODIS Landcover')
  

# leaflet() %>% addTiles() %>% addRasterImage(landsat_reclass_lc_r, colors = colors_landsat_reclass$colors, opacity = .7) %>%
#   addLegend(labels = colors_landsat_reclass$names, colors = colors_landsat_reclass$colors, position = "bottomleft", opacity = .95, title = 'MODIS Landcover')
```
 
 
    
## How to build a heat map with MODIS 250m Pixels (see NDVI or EVI layers) and Landsat Landcover 

Coordinates for center of ACADIA phenocam site
```{r}
# coordinates for acadia center point phenocam
lat_merc = site_lat_merc
lng_merc = site_lon_merc
lat_sin = site_lat_sinu
lng_sin = site_lon_sinu
lat_wgs = site_lat_wgs
lng_wgs = site_lon_wgs

```

Extract values under a polygon or MODIS 250m pixel
```{r}
# Make sure you enter analyzer mode at site 'Acadia' in the application
ndvi_path   = paste0('../www/site_data/',cam_site,'/data_layers/ndvi/tera/MOD13Q1.006_250m_aid0001.nc')
ndvi_brick  = raster::brick(ndvi_path, varname='_250m_16_days_NDVI', crs = sinu_crs)
ndvi_raster = raster::subset(ndvi_brick, 1)
ndvi_raster_merc  = projectRaster(from = ndvi_raster, crs = merc_crs, res = res(ndvi_raster))

ndvi_raster_merc
```

Build a pixels df for all MODIS 250 pixels in raster
```{r}
source('../functions/geospatial.R')
# Values needed to calculate center pixels to use on analysis of netcdf data
r_         = crop_raster(lat_merc, lng_merc, ndvi_raster_merc, height = 10000, width = 10000, crs_str = merc_crs)
ndvi_grid  = build_raster_grid(r_, crs='merc')
xmin       = xmin(extent(r_))
xmax       = xmax(extent(r_))
ymin       = ymin(extent(r_))
ymax       = ymax(extent(r_))
nrows      = nrow(r_)
ncols      = ncol(r_)
resolution = res(r_)[1]

lats_merc = c()
lngs_merc = c()
ids = c()
modis_merc_polys = list()
lng_start = xmin + .5*(resolution)
lat_start = ymax + .5*(resolution)
for (row in c(1:nrows)){
  for (col in c(1:ncols)){
    # Get IDS
    id = paste0(row, '_',col)
    ids = c(ids, id)
    # Calculate Center Points
    lng = lng_start + (resolution)*(col-1)
    lat = lat_start - (resolution)*(row)
    lngs_merc = c(lngs_merc,lng)
    lats_merc = c(lats_merc,lat)
    # Calculate tl,tr,br,bl,tl coordinates (t = top, b = bottom, l = left, r = right)
    t_lat = lat + .5*(resolution)
    b_lat = lat - .5*(resolution)
    l_lng = lng - .5*(resolution)
    r_lng = lng + .5*(resolution)
    
    poly_lats = c(t_lat,t_lat,b_lat,b_lat,t_lat)
    poly_lngs = c(l_lng,r_lng,r_lng,l_lng,l_lng)
    
    modis_merc_polys[id] = list(list('lats' = poly_lats, 'lngs' = poly_lngs))
  }
}
```

Building out the Dataframe with center points and four corners for Building a polygon at each pixel
```{r}
coords_wgs = from_crs1_to_crs2_lon_lat(lngs_merc, lats_merc, from_crs = merc_crs, to_crs = wgs_crs)
lngs_wgs = coordinates(coords_wgs)[,1]
lats_wgs = coordinates(coords_wgs)[,2]

coords_sin = from_crs1_to_crs2_lon_lat(lngs_merc, lats_merc, from_crs = merc_crs, to_crs = sinu_crs)
lngs_sin = coordinates(coords_sin)[,1]
lats_sin = coordinates(coords_sin)[,2]

pixel_ids = c(1:(ncols*nrows))
all_site_pixels_df = data.frame(pixel_id=pixel_ids, row_col = ids,
                                lat_merc_ = lats_merc, lng_merc_ = lngs_merc , 
                                lat_wgs_  = lats_wgs,  lng_wgs_  = lngs_wgs, 
                                lat_sin_  = lats_sin,  lng_sin_  = lngs_sin, 
                                site='acadia')
all_site_pixels_df
```

loop through all_site_pixels_df and build a polygon of each pixel using the modis_merc_polys
```{r}
start_ = Sys.time()
# Grab all pixels from dataframe
pixels = all_site_pixels_df$row_col

# Set the pft MODIS variables for Evergreen Forest
selected_roi_pft = 1# works for acadia: 3
selected_roi_pft_name =  subset(pft_df, pft_df$pft_key == selected_roi_pft)$pft_expanded

pixel_percentages = c()
pixel_heterogens = c()
modis_wgs_polys = NULL
# Build the polygon
for (pixel in pixels){
  lats_merc = modis_merc_polys[pixel][[1]]$lats
  lngs_merc = modis_merc_polys[pixel][[1]]$lngs
  
  # in Merc for extraction across Landsat Landcover Layer
  p_merc = Polygon(matrix(ncol= 2, c(lngs_merc, lats_merc)))
  ps_merc = Polygons(list(p_merc), ID = pixel)
  sps_merc = SpatialPolygons(list(ps_merc))
  proj4string(sps_merc) = crs(landsat_reclass_lc_r)
  
  # Grab all pixels in modis 250 pixel 
  selected_pixel = raster::crop(landsat_reclass_lc_r, sps_merc, snap = 'out' )
  # reproject with higher resolution by setting the resolution equal to 1
  selected_pixel_high_res   = raster::projectRaster(from = selected_pixel, crs = merc_crs, method='ngb', res = res(selected_pixel)/40.2)
  # selected_pixel_high_res   = raster::projectRaster(from = selected_pixel, crs = merc_crs, method='ngb', res = res(selected_pixel)/5)
  selected_pixel_high_res_c = raster::crop(selected_pixel_high_res, sps_merc, snap = 'in' )
  
  # Build dataframe with frequency of landcover PFT values at this pixel
  data_df_at_pixel = as.data.frame(table(selected_pixel_high_res_c@data@values), stringsAsFactors=FALSE) %>% 
    mutate(Var1 = as.double(Var1)) %>%
    left_join(pft_df, by = c('Var1' = 'pft_key'))
  
  # Calculate percentage of selected values from total values
  total_pixels = sum(data_df_at_pixel$Freq)
  selected_values = subset(data_df_at_pixel, data_df_at_pixel$Var1 == selected_roi_pft)$Freq
  selected_percentage = selected_values/total_pixels 
  heterogeneity_at_pixel = length(data_df_at_pixel$Var1)
  
  if (length(selected_percentage) ==0){
    selected_percentage = 0
  }
  
    if (length(heterogeneity_at_pixel) ==0){
    heterogeneity_at_pixel = 0
  }
  # Print out a summary of the % found
  # print (paste0(selected_percentage * 100, ' % of this pixel is ', selected_roi_pft_name))
  
  pixel_heterogens  = c(pixel_heterogens, heterogeneity_at_pixel)
  pixel_percentages = c(pixel_percentages, selected_percentage)
  
  # in WGS for visualization in leaflet
  modis_wgs_pts = from_crs1_to_crs2_lon_lat(lon_ = lngs_merc, lat_ = lats_merc, from_crs = merc_crs, to_crs = wgs_crs)
  p_wgs = Polygon(matrix(ncol= 2,modis_wgs_pts@coords))
  ps_wgs = Polygons(list(p_wgs), ID = pixel)
  sps_wgs = SpatialPolygons(list(ps_wgs))
  proj4string(sps_wgs) = CRS(wgs_crs)
  # Bind the polygons together into a spatial polygon
  if (is.null(modis_wgs_polys)){
    modis_wgs_polys = sps_wgs
  } else{
    modis_wgs_polys = rbind(modis_wgs_polys, sps_wgs)
  }
}
end_   = Sys.time()

print (paste0('Total Time:  ', end_ - start_))
```


Use pixel percentages from above to build into a df that will be used to builda new Raster heatmap for PFT %s
```{r}
perc_data_df = data.frame(ID = pixels, pixel_percentages = pixel_percentages, pixel_heterogens = pixel_heterogens)
perc_data_df

leaflet() %>% addTiles() %>% addRasterImage(landsat_reclass_lc_r, colors = colors_$colors, opacity = 1) %>%
  addLegend(labels = colors_$names, colors = colors_$colors, position = "bottomleft", opacity = .95, title = 'MODIS Landcover') %>%
  setView(lat = site_lat_wgs,lng = site_lon_wgs,zoom = 12)

test_r = r_
values(test_r) = perc_data_df$pixel_percentages
pal = colorNumeric(c("#FFFFCC", "Red"), values(test_r),
  na.color = "transparent")
leaflet() %>% addTiles() %>% addRasterImage(test_r, colors = pal, opacity = 0.8) %>% setView(lat = site_lat_wgs,lng = site_lon_wgs,zoom = 12)

test_r_hetero = r_
values(test_r_hetero) = perc_data_df$pixel_heterogens
pal = colorNumeric(c("#FFFFCC", "Red"), values(test_r_hetero),
  na.color = "transparent")
leaflet() %>% addTiles() %>% addRasterImage(test_r_hetero, colors = pal, opacity = 0.8) %>% setView(lat = site_lat_wgs,lng = site_lon_wgs,zoom = 12)
```


extracting values under one polygon for landsat
```{r}
test_pixel = '2_2'
# Keep height and width 1000 2 cells above for this to work appropriately
lats_merc = modis_merc_polys[test_pixel][[1]]$lats
lngs_merc = modis_merc_polys[test_pixel][[1]]$lngs

# in Merc for extraction across Landsat Landcover Layer
p_merc = Polygon(matrix(ncol= 2, c(lngs_merc, lats_merc)))
ps_merc = Polygons(list(p_merc), ID = pixel)
sps_merc = SpatialPolygons(list(ps_merc))
proj4string(sps_merc) = crs(landsat_reclass_lc_r)

# Grab all pixels in modis 250 pixel 
selected_pixel = raster::crop(landsat_reclass_lc_r, sps_merc, snap = 'in' )
leaflet() %>% addTiles() %>% addPolygons(data = modis_wgs_polys) %>% addRasterImage(selected_pixel) %>%
  setView(lng = subset(all_site_pixels_df, row_col == test_pixel)$lng_wgs_, lat = subset(all_site_pixels_df, row_col == test_pixel)$lat_wgs_, zoom = 17)

# Grab all pixels in modis 250 pixel 
selected_pixel = raster::crop(landsat_reclass_lc_r, sps_merc, snap = 'out' )
leaflet() %>% addTiles() %>% addPolygons(data = modis_wgs_polys) %>% addRasterImage(selected_pixel) %>%
  setView(lng = subset(all_site_pixels_df, row_col == test_pixel)$lng_wgs_, lat = subset(all_site_pixels_df, row_col == test_pixel)$lat_wgs_, zoom = 17)

# reproject with higher resolution (Might be time consuming? but works)
selected_pixel_high_res   = projectRaster(from = selected_pixel, crs = merc_crs, method='ngb', res = res(selected_pixel)/40.2)
selected_pixel_high_res_c = raster::crop(selected_pixel_high_res, sps_merc, snap = 'in' )
leaflet() %>% addTiles() %>% addPolygons(data = modis_wgs_polys) %>% addRasterImage(selected_pixel_high_res_c) %>% 
  setView(lng = subset(all_site_pixels_df, row_col == test_pixel)$lng_wgs_, lat = subset(all_site_pixels_df, row_col == test_pixel)$lat_wgs_, zoom = 17)

```

Get percentages under this 9_9 pixel from above
```{r}
# Set the pft MODIS variables for Evergreen Forest
selected_roi_pft = 1
selected_roi_pft_name =  subset(pft_df, pft_df$pft_key == selected_roi_pft)$pft_expanded

# Build dataframe with frequency of landcover PFT values at this pixel
data_df_at_pixel = as.data.frame(table(selected_pixel_high_res_c@data@values), stringsAsFactors=FALSE) %>% 
  mutate(Var1 = as.double(Var1)) %>%
  left_join(pft_df, by = c('Var1' = 'pft_key'))

# Calculate percentage of selected values from total values
total_pixels = sum(data_df_at_pixel$Freq)
selected_values = subset(data_df_at_pixel, data_df_at_pixel$Var1 == selected_roi_pft)$Freq
selected_percentage = selected_values/total_pixels * 100

# Print out a summary of the % found
print (paste0(selected_percentage, '% of this pixel is ', selected_roi_pft_name))
```






------------------------------------------------------
EXTRA STUFF
------------------------------------------------------

Visualization of points in center of pixels
```{r}
leaflet() %>% addTiles() %>% addRasterImage(r_) %>%
  addCircleMarkers(lat = all_site_pixels_df$lat_wgs_, lng = all_site_pixels_df$lng_wgs_, radius = 1, weight=3, opacity = 1, color='black') %>%
  addPolylines(data = ndvi_grid, weight = 1.8, opacity = 1, group = '250m MODIS Grid', color = 'darkgrey') %>%
  setView(lng = lng_wgs, lat = lat_wgs, zoom = 14)
```

```{r}
# source('../functions/geospatial.R')
# 
# albs_point = from_crs1_to_crs2_lon_lat(lon_ = site_lng_wgs, lat_ = site_lat_wgs, from_crs = wgs_crs, to_crs = alb_crs)
# lng_alb = albs_point@coords[[1]]
# lat_alb = albs_point@coords[[2]]
# 
# pt_merc = from_crs1_to_crs2_lon_lat(lon_ = site_lng_wgs, lat_ = site_lat_wgs, from_crs = wgs_crs, to_crs = merc_crs)
# lng_merc = pt_merc@coords[[1]]
# lat_merc = pt_merc@coords[[2]]

```

```{r}

# Crop in Albers
width  = 15000
height = 15000
e      = as(extent(site_lon_alb - width, site_lon_alb + width, site_lat_alb - height, site_lat_alb + height), 'SpatialPolygons')
crs(e) <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=23 +lon_0=-96 +x_0=0 +y_0=0 +ellps=WGS84 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs"
NLCD_lc_cropped      = raster::crop(NLCD_lc, e, snap='near')
NLCD_lc_cropped_wgs  = projectRaster(NLCD_lc_cropped, crs=wgs_crs, method='ngb')
NLCD_lc_cropped_merc = projectRaster(NLCD_lc_cropped, crs=merc_crs, method='ngb')
```

### Zoom into the next three leaflet maps to show differences between the wgs cropped layer and the other two.
 - Essentially when we crop the landcover into WGS, leaflet reprojects it into Mercator.  
 - NLCD_lc_cropped goes from albers equal -> Mercator (SAME)
 - NLCD_lc_cropped_wgs goes from albers equal -> WGS -> Mercator (DIFFERENT)
 - NLCD_lc_cropped_merc goes from albers equal -> Mercator (SAME)
```{r}
# leaflet() %>% addTiles() %>% addRasterImage(NLCD_lc_cropped)
```
```{r}
# leaflet() %>% addTiles() %>% addRasterImage(NLCD_lc_cropped_wgs)
```
```{r}
leaflet() %>% addTiles() %>% addRasterImage(NLCD_lc_cropped_merc)
```



```{r}
# Crop again in Merc
width  = 10000
height = 10000

e2 =as(extent(site_lon_merc - width, site_lon_merc + width, site_lat_merc - height, site_lat_merc + height), 'SpatialPolygons')
crs(e2) <- merc_crs
NLCD_lc_final_merc = raster::crop(NLCD_lc_cropped_merc, e2, snap='near')

# Display using leaflet
leaflet() %>% addTiles() %>% addRasterImage(NLCD_lc_cropped_merc)
leaflet() %>% addTiles() %>% addRasterImage(NLCD_lc_final_merc)
            
# remove large raster layer out of memory so .rmd doesn't freeze
```

Add regular colors for landsat nlcd layer
```{r}
build_landsat_lc_pallet = function(raster_, landsat_key){
  print ('building landsat landcover palette')
  colors = c()
  names  = c()
  color_list    = c('#1b8a28', '#36d03e', '#9ecb30', '#a0f79f', '#91bb88', '#b99091', '#f0dfb8', '#d6ed9a',
                    '#f1dc07', '#ecbb5b', '#4981b1', '#fcee72', '#fd0608', '#9b9353', '#bdbec0', '#bdbec0', '#89cae3')
  
  v = unique(values(raster_))
  remove = c(NA)
  v = v [! v %in% remove]
  v = sort(v, decreasing = FALSE)
  
  print (v)
  
  count = 0
  for (x in v){
    count = count + 1
      
    red = subset(landsat_key, landsat_key$ID == x)$Red/255
    green = subset(landsat_key, landsat_key$ID == x)$Green/255
    blue = subset(landsat_key, landsat_key$ID == x)$Blue/255
    color = rgb(red,green,blue)
    colors = c(colors, color)
    # colors = c(colors, color_list[count])
    name   = as.character(subset(landsat_key, landsat_key$ID == x)$NLCD.Land.Cover.Class)
    names  = c(names, name)
  }
  colors_ = list('colors' = colors, 'names' = names)
  return (colors_)
}

landsat_atts = NLCD_lc@data@attributes
key_df = subset(landsat_atts[[1]], landsat_atts[[1]]$COUNT != 0)
write.csv(key_df, '../www/landsat_lc/nlcd_key.csv')
c = build_landsat_lc_pallet(test_raster, key_df)

read.csv('../www/landsat_lc/nlcd_key.csv')

leaflet() %>% addTiles() %>% addRasterImage(test_raster, colors = c$colors, opacity = .7) %>%
  addLegend(labels = c$names, colors = c$colors, position = "bottomleft", opacity = .95, title = 'MODIS Landcover')
```



save out raster to .tiff files to check size
```{r}
output_dir = '../www/site_data/landsat_lc'
site       = 'acadia'
file_name  = paste0(site, '_landsat_lc')
dir.create(output_dir)
output_file = paste0(output_dir, '/',file_name,'.tif')
raster::writeRaster(NLCD_lc_final_merc, output_dir, format='GTiff', overwrite=TRUE)
```

Read raster back in
```{r}
test_raster_file = paste0(output_dir, '/', 'acadia', '_landsat_lc.tif')
test_raster = raster::raster(test_raster_file)
test_raster
leaflet() %>% addTiles() %>% addRasterImage(test_raster)

```










