---
title: "ornldaac_workflow"
author: "Kyle"
date: "8/21/2018"
output: html_document
---

Use this repos <https://github.com/ornldaac/webinar-modis-viirs-august2018/blob/master/NotebookR.ipynb>


## Importing Libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(httr)
library(jsonlite)

# Plots:
library(ggplot2)
library(scales)
library(viridis)
require(gridExtra)

# Rasters:
library(raster)
library(rasterVis)

options(warn=-1)
```

## Getting products

### 
```{r}
url <- "https://modis.ornl.gov/rst/api/v1/"

response <- GET("https://modis.ornl.gov/rst/api/v1/products")
http_status(response)$message
```

## Including Plots

You can also embed plots, for example:

```{r}
products <- content(response)$products
typeof(products)
products[1]
```

## Get dates

```{r}
# Set dates request parameters
prod <- 'VNP13A1'   # MODIS product
lat <- 35.71326     # Input latitude
lon <- -83.51047    # Input longitude

r <- GET(paste0("https://modis.ornl.gov/rst/api/v1/",prod,"/dates?latitude=",lat,"&longitude=",lon)) # Get dates response
dates <- content(r)$dates # Parse response object to list
modis_dates <- unlist(lapply(dates, function(dt) dt$modis_date)) # Split list of lists into list of modis date strings
calendar_dates <- as.Date(unlist(lapply(dates, function(dt) dt$calendar_date))) # and also into R date objects
doys <- substr(modis_dates,start=6,stop=8) # Also get a list of days of the year

# Print the first ten modis dates
paste(modis_dates[1:10])

```

## Get subset

```{r}
# Set the remaining subset request parameters
data_band <- '500_m_16_days_EVI2'        # Daytime LST band name
qc_band <- '500_m_16_days_VI_Quality'    # Daytime QC band name
above_below <- 2                         # km above/below
left_right <- 2                          # km left/right

requestURL <- function(latitude, longitude, product, band, start_date, end_date, kmAB, kmLR){
    return(
        paste0(
            url,product,"/subset?",
            "latitude=",latitude,
            "&longitude=",longitude,
            "&band=",band,
            "&startDate=",start_date,
            "&endDate=",end_date,
            "&kmAboveBelow=",kmAB,
            "&kmLeftRight=",kmLR
        )
    )
}

r <- GET(requestURL(lat, lon, prod, data_band, modis_dates[1], modis_dates[1], above_below, left_right))
subset <- fromJSON(toJSON(content(r)))
subset
```

## Get subset Metadata

```{r}
nrow <- as.integer(subset$nrow)             # number of rows
ncol <- as.integer(subset$ncol)             # number of columns
xllcorner <- as.double(subset$xllcorner)    # lower left hand corner x-coordinate
yllcorner <- as.double(subset$yllcorner)    # lower left hand corner y-coordinate
cellsize <- as.double(subset$cellsize)      # pixel size
scale <- as.double(subset$scale)            # scale factor

cat(
    "Row count: ",nrow,
    "\nCol count: ",ncol,
    "\nLower left X: ",xllcorner,
    "\nLower left Y: ",yllcorner,
    "\nPixel size: ",cellsize,
    "\nScale factor: ",scale
)
```

## Format the subset response to a familiar structure

```{r}
# Get subset$subset$data as a new data frame and transpose so that rows are timesteps and columns are pixels
format_subset <- t(as.data.frame(subset$subset$data, col.names=subset$subset$modis_date, check.names=FALSE))
format_subset <- format_subset*as.numeric(scale)
format_subset
```

## Plot the grid as a raster!  -- This is what We are doing using the Landcover we get from Appeears, lets see how this differs!

```{r}
# Make function to create raster objects
r_template <- function(vals, nrow,ncol,xllcorner,yllcorner,cellsize){
    return(
        raster(
            vals = vals,
            nrows = nrow,
            ncols = ncol,
            xmn = xllcorner,
            xmx = xllcorner + (ncol*cellsize),
            ymn = yllcorner,
            ymx = yllcorner + (nrow*cellsize),
            crs = '+proj=sinu +lon_0=0 +x_0=0 +y_0=0 +a=6371007.181 +b=6371007.181 +units=m +no_defs ',
            resolution = cellsize 
        )
    )
}

# Use subset metadata and the new function to make raster object
r_subset <- r_template(format_subset, nrow, ncol, xllcorner, yllcorner, cellsize)
# Warp to WGS84 as another raster object
r_subset_wgs84 <- projectRaster(r_subset, crs = '+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs ')

# Plot both with rasterVis::levelplot
r_ras1 <- levelplot(r_subset, main = paste0("EVI on ",subset$subset$calendar_date," (Sinu)"), margin = FALSE)
r_ras2 <- levelplot(r_subset_wgs84, main = paste0("EVI on ",subset$subset$calendar_date," (WGS84)"), margin = FALSE)

r_subset # Print raster (sinu) details
grid.arrange(r_ras1, r_ras2, ncol=2) # Display raster grids with gridExtra::grid.arrange

# Save raster objects as GeoTIFFs
#writeRaster(r_subset,'sinu_subset.tif',options=c('COMPRESS=LZW'))
#writeRaster(r_subset_wgs84,'wgs84_subset.tif',options=c('COMPRESS=LZW'))
```

## Make a time series from multiple subset requests

```{r}
start_time <- Sys.time()

# Initialize response data.frames to store the returned LST and QC data
proddata <- data.frame()
qcdata <- data.frame()

# Iterate through the list of dates and submit subset requests.
for (dt in modis_dates){

    # Submit request and append to LST time series
    r <- GET(requestURL(lat, lon, prod, data_band, dt, dt, above_below, left_right))
    subset <- fromJSON(toJSON(content(r)))
    proddata <- rbind(proddata, subset$subset)

    # Submit request and append to QC time series
    r <- GET(requestURL(lat, lon, prod, qc_band, dt, dt, above_below, left_right))
    qcsubset <- fromJSON(toJSON(content(r)))
    qcdata <- rbind(qcdata, qcsubset$subset)
    print (dt)
    
}

saveRDS(proddata,file = "data/proddata.rds") # Save the data
saveRDS(qcdata,file = "data/qcdata.rds")

end_time <- Sys.time()
end_time - start_time
```

## Load from a file if you have already downloaded, and don't run the previous code

```{r}
proddata <- readRDS(file = "data/proddata.rds")
qcdata <- readRDS(file = "data/qcdata.rds")
```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```