---
title: "phenocam_heterogeneity"
author: "K. Enns"
date: "1/23/2020"
output: html_document
---

# Phenocam Heterogeneity
### This notebook attemps to calculate % landcover and # landcover types across all of the phenocam sites

### 3 scales per site:
  1. The pixel that the phenocam resides in
  2. A 3 x 3 (9 pixels) with the phenocam in the center pixel
  3. A 5 x 5 (25 pixels) with the phenocam in the center pixel
  
### Note: This process will only work for locations inside of the NLCD layer (Currently just The Contiguous US)


Start with 1 phenocam site data
```{r}
#######################################################
# Be sure to run global.R before running this script
#######################################################

# Select site 
site_name   = 'NEON.D15.ONAQ.DP1.00033'
# site_name   = 'kelloggkorn'
# site_name   = 'acadia'

# Get site Data
site_row = subset(cams_, cams_$site == site_name)

# Extract lat and lon from site data
site_lat = site_row$lat
site_lon = site_row$lon

```

Import the Landcover layer for this site
```{r}
landcover_file = paste0('../www/landsat_lc/', site_name, '_landsat_lc.tif')


# If NLCD layer exists for site, add it to map
if (file.exists(landcover_file)){
  site_nlcd_raster = raster::raster(landcover_file) 
  key_df = read.csv('../www/landsat_lc/nlcd_key.csv')
  nlcd_c = build_landsat_lc_pallet(site_nlcd_raster, key_df)
} else{
  print ('Site is Either not in CONUS or has not been cached for PhenoSynth')
}
```

Reclassify the NLCD layer to match MODIS Landcover Layer
```{r}
# modis to landsat lookup - Removing Evergreen broadleaf forest and Deciduous needleaf forest and the 2nd Shrubland
Landsat_Landcover = read_csv("../www/Landsat.Landcover.csv")
landsat_lc = Landsat_Landcover %>% 
  mutate(Landsat.Class = replace(Landsat.Class, MODIS.Class == 3, NA)) %>%
  mutate(Landsat.Class = replace(Landsat.Class, MODIS.Class == 2, NA)) %>% 
  mutate(Landsat.Class = replace(Landsat.Class, MODIS.Class == 7, NA))

# create a landsat to modis lookup (so that no landsat values are left out)
landsat_lc_lookup = read.csv('../www/landsat_lc/nlcd_key.csv') %>% 
  dplyr::select(ID,NLCD.Land.Cover.Class) %>% left_join(landsat_lc, by = c('ID' = 'Landsat.Class')) %>%
  mutate(MODIS.Class = replace(MODIS.Class, ID == 12, NA)) %>%
  left_join(pft_df, by = c('MODIS.Class' = 'pft_key'))

# Build crosswalk matrix for reclassify function (rcl)
from_values = landsat_lc_lookup$ID
becomes_values   = landsat_lc_lookup$MODIS.Class

# Build matrix to use in reclassify function
m = matrix(ncol = 2, nrow = length(from_values))
m[,1] = from_values
m[,2] = becomes_values

# reclassified nlcd layer to match modis values
site_rc_nlcd = reclassify(site_nlcd_raster, m)
site_rc_nlcd_c = build_pft_palette(site_rc_nlcd)

```

Display reclassified NLCD layer on leaflet map
```{r}
# Build map
leaflet() %>% addTiles() %>% addRasterImage(site_rc_nlcd, colors = site_rc_nlcd_c$palette) %>%
  addLegend(labels = site_rc_nlcd_c$names, colors = site_rc_nlcd_c$colors, position = "bottomleft", opacity = .95, title = 'Landcover') %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 5, color = 'black', weight=2, opacity = 1, label = site_name)
```

### Now lets build out the pixel grids

Grab the modis pixel that the phenocam site lives
```{r}
###############################################################################################################################
# Note: Be sure to run app and go to this site and enter analyzer mode.  This will download the MODIS NDVI layer we can use to 
#    calculate the pixel boundaries for analysis
###############################################################################################################################

ndvi_dir   = paste0('../www/site_data/',site_name,'/data_layers/ndvi/tera/')
ndvi_files = list.files(ndvi_dir)
ndvi_tera_name   = ndvi_files[grepl('MOD13Q1.006_250m_aid0001.nc', ndvi_files)]
ndvi_tera_path   = paste0(ndvi_dir, ndvi_tera_name)
ndvi_tera_brick  = raster::brick(ndvi_tera_path, varname='_250m_16_days_NDVI', crs=sinu_crs)
ndvi_raster_t    = raster::subset(ndvi_tera_brick, 1)
ndvi_raster_merc = projectRaster(from = ndvi_raster_t, crs = merc_crs, res = res(ndvi_raster_t))

# Building Landcover layer and color pallette for specific pft composition in clipped raster
lat_wgs = site_lat
lng_wgs = site_lon
# from wgs to sinusoidal
pt_sinu = from_crs1_to_crs2_lon_lat(lon_ = lng_wgs, lat_ = lat_wgs, from_crs = wgs_crs, to_crs = sinu_crs)
lat_sin = pt_sinu@coords[2]
lng_sin = pt_sinu@coords[1]
# from wgs to web mercator
pt_merc = from_crs1_to_crs2_lon_lat(lon_ = lng_wgs, lat_ = lat_wgs, from_crs = wgs_crs, to_crs = merc_crs)
lat_merc = pt_merc@coords[2]
lng_merc = pt_merc@coords[1]

ndvi_r_m_c = crop_raster(lat_merc, lng_merc, ndvi_raster_merc, height = 10000, width = 10000, crs_str = merc_crs)
ndvi_r_m_c
```

Display NDVI raster and site
```{r}
# Set colors and legend values
colors = c('red','green')
at     = seq(0, maxValue(ndvi_r_m_c), length.out = 10)
cb     = colorBin(palette = colors, bins = at, domain = at)
# Build map
leaflet('map') %>% addTiles() %>% addRasterImage(ndvi_r_m_c, colors = cb) %>% addLegend(pal = cb, values = at) %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 5, color = 'black', weight=2, opacity = 1, label = site_name)
```

Build 3 different scales of NDVI grid to use for analysis
```{r}
source('../functions/geospatial.R')

# Set colors and legend values
colors = c('red','green')
at     = seq(0, maxValue(ndvi_raster_merc), length.out = 10)
cb     = colorBin(palette = colors, bins = at, domain = at)


resolution = res(ndvi_raster_merc)[1]

s_1      = .1
e_1      = as(extent(lng_merc -s_1, lng_merc +s_1, lat_merc -s_1, lat_merc +s_1), 'SpatialPolygons')
crs(e_1) =  merc_crs

s_3      = resolution
e_3      = as(extent(lng_merc -s_3, lng_merc +s_3, lat_merc -s_3, lat_merc +s_3), 'SpatialPolygons')
crs(e_3) =  merc_crs

s_5      = resolution *2
e_5      = as(extent(lng_merc -s_5, lng_merc +s_5, lat_merc -s_5, lat_merc +s_5), 'SpatialPolygons')
crs(e_5) =  merc_crs

r_1by      = raster::crop(ndvi_raster_merc, e_1, snap='out')
r_3by      = raster::crop(ndvi_raster_merc, e_3, snap='out')
r_5by      = raster::crop(ndvi_raster_merc, e_5, snap='out')


# Build Map (1x1)
g_1by = build_raster_grid(r_1by, crs='merc')
leaflet() %>% addTiles() %>% addRasterImage(r_1by, colors = cb) %>% addLegend(pal = cb, values = at) %>% addPolylines(data = g_1by) %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 5, color = 'black', weight=2, opacity = 1, label = site_name)
# Build Map (3x3)
g_3by = build_raster_grid(r_3by, crs='merc')
leaflet() %>% addTiles() %>% addRasterImage(r_3by, colors = cb) %>% addLegend(pal = cb, values = at) %>% addPolylines(data = g_3by) %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 5, color = 'black', weight=2, opacity = 1, label = site_name)
# Build Map (5x5)
g_5by = build_raster_grid(r_5by, crs='merc')
leaflet() %>% addTiles() %>% addRasterImage(r_5by, colors = cb) %>% addLegend(pal = cb, values = at) %>% addPolylines(data = g_5by) %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 5, color = 'black', weight=2, opacity = 1, label = site_name)
```

use the extents from above to create polygons
```{r}
p_1_merc = as(extent(r_1by), 'SpatialPolygons')
crs(p_1_merc) = merc_crs
p_3_merc = as(extent(r_3by), 'SpatialPolygons')
crs(p_3_merc) = merc_crs
p_5_merc = as(extent(r_5by), 'SpatialPolygons')
crs(p_5_merc) = merc_crs

# The WGS polygons.
e_1_wgs = spTransform(p_1_merc, wgs_crs)
e_3_wgs = spTransform(p_3_merc, wgs_crs)
e_5_wgs = spTransform(p_5_merc, wgs_crs)
# The Merc Polygons (will use to extract percent cover and heterogeneity)
p_1_merc
p_3_merc
p_5_merc

# 1x1 GRID display
leaflet() %>% addTiles() %>% addPolylines(data = g_1by) %>% addPolylines(data = e_1_wgs) %>% addRasterImage(site_rc_nlcd, colors = site_rc_nlcd_c$palette) %>%
  addLegend(labels = site_rc_nlcd_c$names, colors = site_rc_nlcd_c$colors, position = "bottomleft", opacity = .95, title = 'Landcover') %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 5, color = 'black', weight=2, opacity = 1, label = site_name) %>%
  setView(lat = site_lat, lng = site_lon, zoom = 17)
# 3x3 GRID display
leaflet() %>% addTiles() %>% addPolylines(data = g_3by) %>% addPolylines(data = e_3_wgs) %>% addRasterImage(site_rc_nlcd, colors = site_rc_nlcd_c$palette) %>%
  addLegend(labels = site_rc_nlcd_c$names, colors = site_rc_nlcd_c$colors, position = "bottomleft", opacity = .95, title = 'Landcover') %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 5, color = 'black', weight=2, opacity = 1, label = site_name) %>%
  setView(lat = site_lat, lng = site_lon, zoom = 16)
# 5x5 GRID display
leaflet() %>% addTiles() %>% addPolylines(data = g_5by) %>% addPolylines(data = e_5_wgs) %>% addRasterImage(site_rc_nlcd, colors = site_rc_nlcd_c$palette) %>%
  addLegend(labels = site_rc_nlcd_c$names, colors = site_rc_nlcd_c$colors, position = "bottomleft", opacity = .95, title = 'Landcover') %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 5, color = 'black', weight=2, opacity = 1, label = site_name) %>% 
  setView(lat = site_lat, lng = site_lon, zoom = 15)
```

Extract heterogeneity metrics under the shapefile (p_1_merc, p_3_merc, and p_5_merc)
```{r}
# Method to get 100% of the nlcd raster under the MODIS polygon 1x1
p_1by_merc_cropped = raster::crop(site_rc_nlcd, p_1_merc, snap = 'out' )
p_1by_merc_cropped_high_res   = raster::projectRaster(from = p_1by_merc_cropped, crs = merc_crs, method='ngb', res = res(p_1by_merc_cropped)/40.5)
p_1by_merc_cropped_high_res_cr = raster::crop(p_1by_merc_cropped_high_res, p_1_merc, snap = 'in' )
p_1by_merc_cropped_c = build_pft_palette(p_1by_merc_cropped_high_res_cr)
# Method to get 100% of the nlcd raster under the MODIS polygon 3x3
p_3by_merc_cropped = raster::crop(site_rc_nlcd, p_3_merc, snap = 'out' )
p_3by_merc_cropped_high_res   = raster::projectRaster(from = p_3by_merc_cropped, crs = merc_crs, method='ngb', res = res(p_3by_merc_cropped)/40.5)
p_3by_merc_cropped_high_res_cr = raster::crop(p_3by_merc_cropped_high_res, p_3_merc, snap = 'in' )
p_3by_merc_cropped_c = build_pft_palette(p_3by_merc_cropped_high_res_cr)
# Method to get 100% of the nlcd raster under the MODIS polygon 5x5
p_5by_merc_cropped = raster::crop(site_rc_nlcd, p_5_merc, snap = 'out' )
p_5by_merc_cropped_high_res   = raster::projectRaster(from = p_5by_merc_cropped, crs = merc_crs, method='ngb', res = res(p_5by_merc_cropped)/40.5)
p_5by_merc_cropped_high_res_cr = raster::crop(p_5by_merc_cropped_high_res, p_5_merc, snap = 'in' )
p_5by_merc_cropped_c = build_pft_palette(p_5by_merc_cropped_high_res_cr)

# Map display for 1x1
leaflet() %>% addTiles() %>% addPolylines(data = g_1by) %>% addPolylines(data = e_1_wgs) %>% 
  addRasterImage(p_1by_merc_cropped_high_res_cr, colors = p_1by_merc_cropped_c$palette) %>%
  addLegend(labels = p_1by_merc_cropped_c$names, colors = p_1by_merc_cropped_c$colors, position = "bottomleft", opacity = .95, title = 'Landcover') %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 5, color = 'black', weight=2, opacity = 1, label = site_name) %>% 
  setView(lat = site_lat, lng = site_lon, zoom = 15)
# Map display for 3x3
leaflet() %>% addTiles() %>% addPolylines(data = g_3by) %>% addPolylines(data = e_3_wgs) %>% 
  addRasterImage(p_3by_merc_cropped_high_res_cr, colors = p_3by_merc_cropped_c$palette) %>%
  addLegend(labels = p_3by_merc_cropped_c$names, colors = p_3by_merc_cropped_c$colors, position = "bottomleft", opacity = .95, title = 'Landcover') %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 5, color = 'black', weight=2, opacity = 1, label = site_name) %>% 
  setView(lat = site_lat, lng = site_lon, zoom = 15)
# Map display for 5x5 
leaflet() %>% addTiles() %>% addPolylines(data = g_5by) %>% addPolylines(data = e_5_wgs) %>% 
  addRasterImage(p_5by_merc_cropped_high_res_cr, colors = p_5by_merc_cropped_c$palette) %>%
  addLegend(labels = p_5by_merc_cropped_c$names, colors = p_5by_merc_cropped_c$colors, position = "bottomleft", opacity = .95, title = 'Landcover') %>%
  addCircleMarkers(lat = site_lat, lng = site_lon, radius = 5, color = 'black', weight=2, opacity = 1, label = site_name) %>% 
  setView(lat = site_lat, lng = site_lon, zoom = 15)


test = previewColors(colorFactor("RdYlBu", domain = NULL), factor(LETTERS[1:5], levels = LETTERS))

unique(values(p_3by_merc_cropped_high_res_cr))

p_3by_merc_cropped_c$colors

```



Calculate heterogeneity metrics for the 3 different sized extents (1x1, 3x3, 5x5)
```{r}
data_df_at_extent_1 = as.data.frame(table(p_1by_merc_cropped_high_res_cr@data@values), stringsAsFactors=FALSE) %>% 
  mutate(Var1 = as.double(Var1)) %>%
  left_join(pft_df, by = c('Var1' = 'pft_key')) %>% 
  mutate(id = '1by1') %>% mutate(total_pixels = sum(Freq)) %>%
  mutate(percent_cover = Freq/total_pixels) %>% 
  mutate(heterogeneity = length(Var1))
data_df_at_extent_3 = as.data.frame(table(p_3by_merc_cropped_high_res_cr@data@values), stringsAsFactors=FALSE) %>% 
  mutate(Var1 = as.double(Var1)) %>%
  left_join(pft_df, by = c('Var1' = 'pft_key')) %>% 
  mutate(id = '3by3') %>% mutate(total_pixels = sum(Freq)) %>%
  mutate(percent_cover = Freq/total_pixels) %>% 
  mutate(heterogeneity = length(Var1))
data_df_at_extent_5 = as.data.frame(table(p_5by_merc_cropped_high_res_cr@data@values), stringsAsFactors=FALSE) %>% 
  mutate(Var1 = as.double(Var1)) %>%
  left_join(pft_df, by = c('Var1' = 'pft_key')) %>% 
  mutate(id = '5by5') %>% mutate(total_pixels = sum(Freq)) %>%
  mutate(percent_cover = Freq/total_pixels) %>% 
  mutate(heterogeneity = length(Var1))

data_df_at_extent_all = rbind(data_df_at_extent_5,data_df_at_extent_3,data_df_at_extent_1)
```

Plot the heterogeneity metrics 
```{r}
all_pfts = unique(data_df_at_extent_all$pft_abbreviated)
plot_data_1 = data.frame(pft_abbreviated = all_pfts, stringsAsFactors = FALSE) %>% left_join(data_df_at_extent_1)
plot_data_3 = data.frame(pft_abbreviated = all_pfts, stringsAsFactors = FALSE) %>% left_join(data_df_at_extent_3)
plot_data_5 = data.frame(pft_abbreviated = all_pfts, stringsAsFactors = FALSE) %>% left_join(data_df_at_extent_5)

p = plot_ly(x = all_pfts, y = plot_data_1$percent_cover, type = 'bar', name = '1 x 1 Extent', 
  marker = list(color = 'rgb(49,130,189)')) %>%
  add_trace(y = plot_data_3$percent_cover, name = '3 x 3 Extent', marker = list(color = 'rgb(256,100,100)')) %>%
  add_trace(y = plot_data_5$percent_cover, name = '5 x 5 Extent', marker = list(color = 'rgb(123,204,12)')) %>%
  layout(xaxis = list(title = "Plant functional types", tickangle = -45),
         yaxis = list(title = "Percentages"),
         margin = list(b = 100),
         barmode = 'group')
p
```






















































