---
title: "Selected pixels"
author: "K. Duffy"
date: "9/17/2018"
output: html_document
---

### Downloading netcdf for NDVI from AppEEARS
```{r}
# Grab task for poudreriver ndvi netcdf
site_task_id = 'a11d9256-3efd-449c-85b0-e2af045bfa8a'
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", site_task_id, sep = ""))
bundle_response = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
document = jsonlite::fromJSON(txt=bundle_response)
files = document$files

# Grab netcdf file from AppEEARS
netcdf_id    = subset(files, file_type == 'nc')$file_id

get_download_folder = function(){
  if (Sys.info()['sysname'] == 'Darwin'){
    folder = paste('/Users/', Sys.getenv('LOGNAME'),'/Downloads/', sep = '')
  }else if (Sys.info()['sysname'] == 'Windows'){
    folder = paste('C:/Downloads/', sep = '')
  }else{
    folder = ''
  }
  return (folder)
  }
download_this_file = netcdf_id
# # retrieve the filename from the file_id
bundle = jsonlite::fromJSON(bundle_response)$files
filename = subset(bundle, bundle$file_id == download_this_file)$file_name
# create a destination directory to store the file in
dest_dir = get_download_folder()
filepath = paste(dest_dir, filename, sep = '')

# write the file to disk using the destination directory and file name 
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", site_task_id, '/', download_this_file, sep = ""),
                      write_disk(filepath, overwrite = TRUE), progress())

```


### Building 3 polygons for the poudreriver phenocam site (replicas of pixels from the app)
```{r}
# Format the data into a dataframe with column names long and lat
# df = data.frame(long = c(-105,-106,-106,-105,-105), lat = c(40,40,41,41,40))

library(sp)
matrix_to_polygon = function(matrix, id){
  p   = Polygon(matrix)
  ps  = Polygons(list(p), id)
  sps = SpatialPolygons(list(ps))
  sp::proj4string(sps) = CRS("+proj=longlat +datum=WGS84")
  return (sps)
}

pd_pixel1 = matrix_to_polygon(rbind(c(-104.8375, 40.45), c(-104.8333,40.45), c(-104.8333, 40.44583), c(-104.8375,40.44583), c(-104.8375,40.45)), 'pd_pixel1')
pd_pixel2 = matrix_to_polygon(rbind(c(-104.8333,40.45), c(-104.8292,40.45), c(-104.8292, 40.44583), c(-104.8333,40.44583), c(-104.8333,40.45)), 'pd_pixel2')
pd_pixel3 = matrix_to_polygon(rbind(c(-104.8292,40.45), c(-104.8250,40.45), c(-104.8250, 40.44583), c(-104.8292,40.44583), c(-104.8292,40.45)), 'pd_pixel3')

# Binding the three polygons together
pixel_sps = rbind(pd_pixel1, pd_pixel2)
pixel_sps = rbind(pixel_sps, pd_pixel3)
```


### Bringing in the netcdf ndvi file and displaying
###   the snapshot(in time) raster for the netcdf under the
###   (poudreriver) polygons.
```{r}
YlGn = brewer.pal(9, "YlGn")
pixel_sps
n_file      = filepath
netcdf_ndvi = raster(n_file)

dpts = ggplot2::fortify(pixel_sps)
lons = dpts$long
lats = dpts$lat

leaflet('map') %>%  addTiles() %>%
  addRasterImage(netcdf_ndvi, col = YlGn) %>%
  addPolygons(data=pixel_sps, weight=2) %>%
  setView(lng = -104.8312, lat = 40.44792, zoom = 14.5)
```

### Visualization of cropped raster.  Note we use extracted in the next cell to get the pixels under these 3 polygons
```{r}

cropped_ndvi = crop(netcdf_ndvi, pixel_sps, snap='out')

leaflet('map') %>%  addTiles() %>%
  addRasterImage(cropped_ndvi, col = YlGn) %>%
  addPolygons(data=pixel_sps, weight=2, color = 'red') %>%
  setView(lng = -104.8312, lat = 40.44792, zoom = 14.5)

```

### Extracted ndvi values under the polygons at this snapshot in time 
```{r}
extracted_ndvi = extract(netcdf_ndvi, pixel_sps, snap = 'in')
extracted_ndvi
```


### Add the ability to loop through this netcdf based on dates available to grab all of the ndvi values
###   for each pixel.
```{r}
library(ncdf4)
nc_data = nc_open(n_file)
ndvi = ncvar_get(nc_data, "_250m_16_days_NDVI")
qc   = ncvar_get(nc_data, "_250m_16_days_VI_Quality")
# Print a list of variables in file
print (attributes(nc_data$var)$names)
# Print a list of dimensions in file
print (attributes(nc_data$dim)$names)
# All info for the nc_data file
# print (nc_data)
```

### Using netcdf4 package to show the same workflow as above
```{r}
# Lat/Long values from the netcdf for pixels
lat = ncvar_get(nc_data, "lat")
lon = ncvar_get(nc_data, "lon")
# Dates are days since 2000-01-01 00:00:00 
dates = ncvar_get(nc_data, 'time')


# Setting fill values to NA
fillvalue = ncatt_get(nc_data, "_250m_16_days_NDVI", "_FillValue")
ndvi[ndvi == fillvalue$value] = NA

# Projection crs for raster
crs = CRS("+proj=longlat +datum=WGS84")

# Uncropped raster netcdf ndvi
r_ndvi = raster(t(ndvi[,,1]), xmn=min(lon), xmx=max(lon), ymn=min(lat), ymx=max(lat), crs=crs)
leaflet('map') %>%  addTiles() %>%
  addRasterImage(r_ndvi, col = YlGn) %>%
  addPolygons(data=pixel_sps, weight=2, color = 'red') %>%
  setView(lng = -104.8312, lat = 40.44792, zoom = 14.5)

# Cropped raster netcdf ndvi
cropped_ndvi_r = crop(r_ndvi, pixel_sps, snap='out')
leaflet('map') %>%  addTiles() %>%
  addRasterImage(cropped_ndvi_r, col = YlGn) %>%
  addPolygons(data=pixel_sps, weight=2, color = 'red') %>%
  setView(lng = -104.8312, lat = 40.44792, zoom = 14.5)
```


### Loop through netcdf date layers and extract the ndvi data
```{r}
data_plot  = c()
polys_len  = c()
pixel_len  = c()
int_pixels = list()
final_ndvi_list = c()
len = length(dates)

for (x in c(1:len)){
# for (x in c(1:2)){
  r_ndvi = raster(t(ndvi[,,x]), xmn=min(lon), xmx=max(lon), ymn=min(lat), ymx=max(lat), crs=crs)
  values_under_polygon = extract(r_ndvi, pixel_sps)
  
  # Setting length of polygons to select with 
  if (is.null(polys_len)){
    # Number of polygons (aka highlighted pixels) selected
    polys_len = length(values_under_polygon)
  }
  # Setting length of pixels in each polygon
  if (length(int_pixels) == 0){
    for (xx in c(1:polys_len)){
      # Number of pixels picked up by the highlighted pixel
      pixel_len  = length(values_under_polygon[[xx]])
      int_pixels[[xx]] = pixel_len
    }
  }
  
  ndvi_means = c()
  # Loop through the different polygons to extract ndvi values and save to dataframe
  for (i in c(1:polys_len)){
    ndvi_ = values_under_polygon[[i]]
    ndvi_means = c(ndvi_means, mean(ndvi_))
  }
  final_ndvi_list = c(final_ndvi_list, mean(ndvi_means))
}

print (final_ndvi_list)
print (length(final_ndvi_list))
```

### Plot averages of all netcdf pixels under the polygons and plotted by days after 2000-01-01 00:00:00
```{r}
data_df = data.frame(date = dates, ndvi = final_ndvi_list)
p = ggplot(data = data_df, aes(x= date, y= ndvi)) + 
  geom_line()
p
```



