---
title: "Sinu_to_Merc"
author: "Kyle"
date: "12/19/2018"
output: html_document
---


grab task_id from appeears
```{r}
library(httr)
task_id = "ba9d46ab-7648-4b7d-82db-670ac7a1d21b"
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", task_id, sep = ""))
bundle_response = prettify(jsonlite::toJSON(content(response), auto_unbox = TRUE))
```

grab file_id for the tiff we will use to transform and test with (in Sinusoidal)
```{r}
document = jsonlite::fromJSON(txt=bundle_response)
files = document$files
print ('file id for selected tif: ')
file_id = files[1,]$file_id  #1 is the position of the .tif file with pft
file_id
```

download file locally, then delete it (change the directory to wherever you want to temporarily download)
```{r}
dir = './www/'
filename = 'landcover_test_tiff.tif'
filepath = paste0(dir, filename)

print (paste0('downloading to: ', filepath))
response = GET(paste("https://lpdaacsvc.cr.usgs.gov/appeears/api/bundle/", task_id , '/', file_id, sep = ""), write_disk(filepath, overwrite = TRUE), progress())

```
read in the downloaded file and then delete it
```{r}
library(raster); library(leaflet)
sinu_lc = raster(filepath)
plot(sinu_lc)  # tif is too big to plot in leaflet, must crop first
```

functions used to switch between sinusoidal and mercator
```{r}
# Function to convert WGS lat/lon coordinates into Sinusoidal
  wgs_to_sinu = function(lon_,lat_){
    xy              = data.frame(matrix(c(lon_,lat_), ncol=2))
    colnames(xy)    = c('lon', 'lat')
    coordinates(xy) = ~ lon + lat
    proj4string(xy) = CRS("+proj=longlat +datum=WGS84")
    p               = spTransform(xy, CRS("+proj=sinu +lon_0=0 +x_0=0 +y_0=0 +a=6371007.181 +b=6371007.181 +units=m +no_defs"))
    return (p)
  }
# Function to conver Sinusoidal to WGS84
  merc_to_sinu = function(lon_,lat_){
    print ('Reprojecting coords to WGS84')
    xy              = data.frame(matrix(c(lon_,lat_), ncol=2))
    colnames(xy)    = c('lon', 'lat')
    coordinates(xy) = ~ lon + lat
    proj4string(xy) = CRS('+proj=merc +a=6378137 +b=6378137 +lat_ts=0.0 +lon_0=0.0 +x_0=0.0 +y_0=0 +k=1.0 +units=m+nadgrids=@null +wktext  +no_defs')
    p               = spTransform(xy, CRS("+proj=longlat +datum=WGS84"))
    return (p)
  }
  
```

crop the sinusoidal landcover raster so we can plot and view in an interactive leaflet map
```{r}
# raster we will manipulate: sinu_lc (stands for sinusoidal landcover layer)
data      = subset(cams_, Sitename == 'turkeypointenf74')

sinu_crs = CRS("+proj=sinu +lon_0=0 +x_0=0 +y_0=0 +a=6371007.181 +b=6371007.181 +units=m +no_defs")
wgs_crs  = CRS("+proj=longlat +datum=WGS84")

#Convert wgs lat/lon into sinusoidal
lon_wgs      = data$Lon
lat_wgs      = data$Lat

this = wgs_to_sinu(lon_wgs,lat_wgs)
coordinates(this)
lon_sinu = coordinates(this)[1]
lat_sinu = coordinates(this)[2]

height = 1000
width  = 1000
e      = as(extent(lon_sinu-width, lon_sinu + width, lat_sinu - height, lat_sinu + height), 'SpatialPolygons')
crs(e) <- "+proj=sinu +lon_0=0 +x_0=0 +y_0=0 +a=6371007.181 +b=6371007.181 +units=m +no_defs"

r       = raster::crop(sinu_lc, e, snap='out')
# r       = projectRaster(r, crs = newproj, res = 257.5014113)
# r       = projectRaster(r, crs = sinu_crs)
plot (r)
library(leaflet)
leaflet('testmap') %>% addTiles() %>% addRasterImage(r)
```

reproject the sinusoidal raster into mercator and add to a leaflet map (development)
```{r}
library(Proj4Leaflet)
merc_crs = CRS('+proj=merc +a=6378137 +b=6378137 +lat_ts=0.0 +lon_0=0.0 +x_0=0.0 +y_0=0 +k=1.0 +units=m+nadgrids=@null +wktext  +no_defs')
r

spTransform(r, CRSobj = )


```




