---
title: "transition dates plot aesthetics"
author: "K. Duffy"
date: "11/13/2018"
output: html_document
---


```{r}

gcc    = read.csv('/Users/kdw223/Google Drive/PhenoPostdoc/phenoRemote/www/site_data/acadia/data_layers/gcc_3_day.csv')
spring = read.csv('/Users/kdw223/Google Drive/PhenoPostdoc/phenoRemote/www/site_data/acadia/data_layers/gcc_3_day_spring_tds.csv')
fall   = read.csv('/Users/kdw223/Google Drive/PhenoPostdoc/phenoRemote/www/site_data/acadia/data_layers/gcc_3_day_fall_tds.csv')

gcc$date = as.Date(gcc$date)
# spring$date = as.Date(spring$date)
# fall$date = as.Date(fall$date)
# format dates correctly (unix time to date format)
unix = "1970-01-01"
spring[, 2:9] = apply(spring[, 2:9], 2, function(x)
  as.character(as.Date(x, origin = unix)))
fall[, 2:9] = apply(fall[, 2:9], 2, function(x)
  as.character(as.Date(x, origin = unix)))
```

manipulate data for the transition dates so that they match the smooth_gcc line (loess fit) at
that time instead of using the threshold from thetable ex(threshold_10)

```{r}
# df_test = subset(gcc, date >= '2007-01-01' & date <= '2012-01-01')
df_test = gcc
p = plot_ly(
            data = df_test,
            x = ~ date,
            y = ~ gcc_90,
            showlegend = FALSE,
            type = 'scatter',
            mode = 'markers'
          ) %>%
              add_trace(
              y = ~ smooth_gcc_90,
              mode = "lines",
              line = list(width = 2, color = "rgb(120,120,120)"),
              name = "Gcc loess fit",
              showlegend = TRUE
            ) %>%
  # SOS spring
            # 10%
            add_trace(
              data = spring,
              x = ~ as.Date(transition_10),
              y = ~ threshold_10,
              mode = "markers",
              type = "scatter",
              marker = list(color = "#7FFF00", symbol = "circle"),
              name = "SOS (10%)",
              showlegend = TRUE
            ) %>%
            add_segments(x = ~ as.Date(transition_10_lower_ci),
                         xend = ~ as.Date(transition_10_upper_ci),
                         y = ~ threshold_10,
                         yend = ~ threshold_10,
                         line = list(color = "#7FFF00"),
                         name = "SOS (10%) - CI"
            ) %>%
            # 25 %
            add_trace(
              x = ~ as.Date(transition_25),
              y = ~ threshold_25,
              mode = "markers",
              type = "scatter",
              marker = list(color = "#66CD00", symbol = "square"),
              showlegend = TRUE,
              name = "SOS (25%)"
            ) %>%
            add_segments(x = ~ as.Date(transition_25_lower_ci),
                         xend = ~ as.Date(transition_25_upper_ci),
                         y = ~ threshold_25,
                         yend = ~ threshold_25,
                         line = list(color = "#66CD00"),
                         name = "SOS (25%) - CI"
            ) %>%
            # 50 %
            add_trace(
              x = ~ as.Date(transition_50),
              y = ~ threshold_50,
              mode = "markers",
              type = "scatter",
              marker = list(color = "#458B00", symbol = "diamond"),
              showlegend = TRUE,
              name = "SOS (50%)"
            ) %>%
            add_segments(x = ~ as.Date(transition_50_lower_ci),
                         xend = ~ as.Date(transition_50_upper_ci),
                         y = ~ threshold_50,
                         yend = ~ threshold_50,
                         line = list(color = "#458B00"),
                         name = "SOS (50%) - CI"
            ) %>%
            
            # EOS fall
            # 50%
            add_trace(
              data = fall,
              x = ~ as.Date(transition_50),
              y = ~ threshold_50,
              mode = "markers",
              type = "scatter",
              marker = list(color = "#FFB90F", symbol = "diamond"),
              showlegend = TRUE,
              name = "EOS (50%)"
            ) %>%
            add_segments(x = ~ as.Date(transition_50_lower_ci),
                         xend = ~ as.Date(transition_50_upper_ci),
                         y = ~ threshold_50,
                         yend = ~ threshold_50,
                         line = list(color = "#FFB90F"),
                         name = "EOS (50%) - CI"
            ) %>%
            # 25 %
            add_trace(
              x = ~ as.Date(transition_25),
              y = ~ threshold_25,
              mode = "markers",
              type = "scatter",
              marker = list(color = "#CD950C", symbol = "square"),
              showlegend = TRUE,
              name = "EOS (25%)"
            ) %>%
            add_segments(x = ~ as.Date(transition_25_lower_ci),
                         xend = ~ as.Date(transition_25_upper_ci),
                         y = ~ threshold_25,
                         yend = ~ threshold_25,
                         line = list(color = "#CD950C"),
                         name = "EOS (25%) - CI"
            ) %>%
            # 10 %
            add_trace(
              x = ~ as.Date(transition_10),
              y = ~ threshold_10,
              mode = "markers",
              marker = list(color = "#8B6508", symbol = "circle"),
              showlegend = TRUE,
              name = "EOS (10%)"
            ) %>%
            add_segments(x = ~ as.Date(transition_10_lower_ci),
                         xend = ~ as.Date(transition_10_upper_ci),
                         y = ~ threshold_10,
                         yend = ~ threshold_10,
                         line = list(color = "#8B6508"),
                         name = "EOS (10%) - CI"
            ) %>%
            layout(xaxis = list(title = "Date"),
                   yaxis = list(title = "Gcc"))
p
```
```{r}
p_gg = ggplot(data = df_test, aes(x = date, y = gcc_90, color = "#458B00")) +
          geom_point(size = .5)
p_gg = p_gg + geom_line(data = df_test, aes(x = date, y = smooth_gcc_90, color = "#66CD00"),size = 1)
p_gg = ggplotly(p_gg)
p_gg


```
MODIS application of plotly:
**Kyle can you throw in some code in the server to download the NDVI data as a .csv or similar, then I will finish tackling this.  Right now the NDVI csv is the QAQC Stuff
```{r}
ndvi    = readRDS('/Users/kdw223/Google Drive/PhenoPostdoc/phenoRemote/all_data.Rmd') #temporary hack to work offline
```
```{r}
p2 = plot_ly(
            data = ndvi,
            x = ~ date,
            y = ~ ndvi$value,
            showlegend = FALSE,
            type = 'scatter',
            mode = 'markers'
          ) %>%
              add_trace(
              y = smooth(ndvi$value),
              mode = "lines",
              line = list(width = 2, color = "rgb(120,120,120)"),
              name = "MODIS loess fit",
              showlegend = TRUE
            )
p2
```

got it to work!  ignore my miultiplot function.  need to add legends etc though
```{r}
p3=subplot(p, p2, nrows=2)
p3

```
This is saved for when I get the transition dates in from MODIS

%>%
  # SOS spring
            # 10%
            add_trace(
              data = spring,
              x = ~ as.Date(transition_10),
              y = ~ threshold_10,
              mode = "markers",
              type = "scatter",
              marker = list(color = "#7FFF00", symbol = "circle"),
              name = "SOS (10%)",
              showlegend = TRUE
            ) %>%
            add_segments(x = ~ as.Date(transition_10_lower_ci),
                         xend = ~ as.Date(transition_10_upper_ci),
                         y = ~ threshold_10,
                         yend = ~ threshold_10,
                         line = list(color = "#7FFF00"),
                         name = "SOS (10%) - CI"
            ) %>%
            # 25 %
            add_trace(
              x = ~ as.Date(transition_25),
              y = ~ threshold_25,
              mode = "markers",
              type = "scatter",
              marker = list(color = "#66CD00", symbol = "square"),
              showlegend = TRUE,
              name = "SOS (25%)"
            ) %>%
            add_segments(x = ~ as.Date(transition_25_lower_ci),
                         xend = ~ as.Date(transition_25_upper_ci),
                         y = ~ threshold_25,
                         yend = ~ threshold_25,
                         line = list(color = "#66CD00"),
                         name = "SOS (25%) - CI"
            ) %>%
            # 50 %
            add_trace(
              x = ~ as.Date(transition_50),
              y = ~ threshold_50,
              mode = "markers",
              type = "scatter",
              marker = list(color = "#458B00", symbol = "diamond"),
              showlegend = TRUE,
              name = "SOS (50%)"
            ) %>%
            add_segments(x = ~ as.Date(transition_50_lower_ci),
                         xend = ~ as.Date(transition_50_upper_ci),
                         y = ~ threshold_50,
                         yend = ~ threshold_50,
                         line = list(color = "#458B00"),
                         name = "SOS (50%) - CI"
            ) %>%
            
            # EOS fall
            # 50%
            add_trace(
              data = fall,
              x = ~ as.Date(transition_50),
              y = ~ threshold_50,
              mode = "markers",
              type = "scatter",
              marker = list(color = "#FFB90F", symbol = "diamond"),
              showlegend = TRUE,
              name = "EOS (50%)"
            ) %>%
            add_segments(x = ~ as.Date(transition_50_lower_ci),
                         xend = ~ as.Date(transition_50_upper_ci),
                         y = ~ threshold_50,
                         yend = ~ threshold_50,
                         line = list(color = "#FFB90F"),
                         name = "EOS (50%) - CI"
            ) %>%
            # 25 %
            add_trace(
              x = ~ as.Date(transition_25),
              y = ~ threshold_25,
              mode = "markers",
              type = "scatter",
              marker = list(color = "#CD950C", symbol = "square"),
              showlegend = TRUE,
              name = "EOS (25%)"
            ) %>%
            add_segments(x = ~ as.Date(transition_25_lower_ci),
                         xend = ~ as.Date(transition_25_upper_ci),
                         y = ~ threshold_25,
                         yend = ~ threshold_25,
                         line = list(color = "#CD950C"),
                         name = "EOS (25%) - CI"
            ) %>%
            # 10 %
            add_trace(
              x = ~ as.Date(transition_10),
              y = ~ threshold_10,
              mode = "markers",
              marker = list(color = "#8B6508", symbol = "circle"),
              showlegend = TRUE,
              name = "EOS (10%)"
            ) %>%
            add_segments(x = ~ as.Date(transition_10_lower_ci),
                         xend = ~ as.Date(transition_10_upper_ci),
                         y = ~ threshold_10,
                         yend = ~ threshold_10,
                         line = list(color = "#8B6508"),
                         name = "EOS (10%) - CI"
            ) %>%
            layout(xaxis = list(title = "Date"),
                   yaxis = list(title = "Gcc"))
p
```

