---
title: "phenocam_analysis"
author: "K. Enns"
date: "1/29/2020"
output: html_document
---


### RUN Global.R



Find which sites to use based on local cache / NLCD availability
```{r}
source('../../functions/geospatial.R')
sites_with_nlcd    = c()
sites_without_nlcd = c()
for (this_site in cams_$site){
  this_nlcd_file = paste0('../../www/landsat_lc/', this_site, '_landsat_lc.tif')
    # If NLCD layer exists for site, add it to map
  if (file.exists(this_nlcd_file)){
    sites_with_nlcd = c(sites_with_nlcd, this_site)
  } else{
    sites_without_nlcd = c(sites_without_nlcd, this_site)
  }
}
sites_with_modis_lc    = c()
sites_without_modis_lc = c()
sites_with_ndvi        = c()
sites_without_ndvi     = c()
# Loop through the phenocam sites
for (this_site in sites_with_nlcd){
  # Get site Data
  # Extract nlcd file
  this_nlcd_file = paste0('../../www/landsat_lc/', this_site, '_landsat_lc.tif')
  # Extract modis NDVI file
  modis_ndvi_dir = paste0('../../www/site_data/', this_site, '/data_layers/ndvi/tera/')
  modis_ndvi_files = list.files(modis_ndvi_dir)
  this_modis_ndvi_file = paste0(modis_ndvi_dir, modis_ndvi_files[grep('MOD13Q1.006_250m_aid0001.nc', modis_ndvi_files)])
  # Extract modis LC file
  modis_lc_dir   = paste0('../../www/site_data/', this_site, '/data_layers/lc/')
  modis_lc_files = list.files(modis_lc_dir)
  this_modis_lc_file = paste0(modis_lc_dir, modis_lc_files[grep('MCD12Q1.006_500m_aid0001.nc', modis_lc_files)])
  
  
  # MODIS LC
  if (length(modis_lc_files) == 0){
    sites_without_modis_lc = c(sites_without_modis_lc, this_site)
  }else {
    if(file.exists(this_modis_lc_file)){
      if (length(this_modis_lc_file) > 1){
        print (paste0('This site has more than 1 file: ', this_modis_lc_file))
      }
      sites_with_modis_lc = c(sites_with_modis_lc, this_site)
    }else{
      sites_without_modis_lc = c(sites_without_modis_lc, this_site)
    }
  }
  
  # MODIS NDVI 
  if (length(modis_ndvi_files) == 0){
    sites_without_ndvi = c(sites_without_ndvi, this_site)
  }else{
    if(file.exists(this_modis_ndvi_file)){
      sites_with_ndvi = c(sites_with_ndvi, this_site)
    }else{
      sites_without_ndvi = c(sites_without_ndvi, this_site)
    }
  }
}
print ('------------------ NLCD ------------------')
print ('Sites That have no NLCD layer:')
length(sites_without_nlcd)
print ('Sites with NLCD layer:')
length(sites_with_nlcd)
print ('------------------ Sites with NLCD ------------------')
print ('------------------ MODIS LC ------------------')
print ('Sites That have no MODIS LC layer:')
length(sites_without_modis_lc)
print ('Sites with MODIS LC layer:')
length(sites_with_modis_lc)
print ('------------------ MODIS NDVI ------------------')
print ('Sites That have no MDOIS NDVI layer:')
length(sites_without_ndvi)
print ('Sites with MODIS NDVI layer:')
length(sites_with_ndvi)
```



### We now have all of the data.  
1. NLCD
2. MODIS LandCover
3. PhenocamROI data

-  Next step is to calculate phenocam level values across the 3 scales of 1x1, 3x3, 5x5 using
     the ndvi layer's raster grid (250m resolution in Sinusoidal then transformed to mercator)


MODIS LandCover data
```{r}
# Start with sites all phenocam sites that have nlcd, modis landcover and phenocam ROI data.
roi_pfts = c()
all_data_df = data.frame()
total_sites = length(sites_with_nlcd)
sites_with_nlcd_post_qc = sites_with_nlcd
# Loop through the phenocam sites
# grep('intervale', sites_with_nlcd_post_qc)
for (pc_site in sites_with_nlcd){
# for (pc_site in c('intervale')){
  print (pc_site)
  print (format(Sys.time(), '%Y_%m_%d_%H%M%S'))
  
  ######################################################## PHENOCAM data
  # Get phenocam data
  site_row = subset(cams_, cams_$site == pc_site)
  # Extract lat and lon from site data
  lat_wgs = site_row$lat
  lng_wgs = site_row$lon
  # from wgs to sinusoidal
  pt_sinu = from_crs1_to_crs2_lon_lat(lon_ = lng_wgs, lat_ = lat_wgs, from_crs = wgs_crs, to_crs = sinu_crs)
  lat_sin = pt_sinu@coords[2]
  lng_sin = pt_sinu@coords[1]
  # from wgs to web mercator
  pt_merc = from_crs1_to_crs2_lon_lat(lon_ = lng_wgs, lat_ = lat_wgs, from_crs = wgs_crs, to_crs = merc_crs)
  lat_merc = pt_merc@coords[2]
  lng_merc = pt_merc@coords[1]
  
  ######################################################## NLCD
  # Read in NLCD Landcover layer
  landcover_file = paste0('../../www/landsat_lc/', pc_site, '_landsat_lc.tif')
  site_nlcd_raster = raster::raster(landcover_file)
  if (unique(values(site_nlcd_raster)) == 0){
    print (paste0('This site: ',pc_site,' only has 0 values for the NLCD rater, Skip this and remove it from MODIS and ROI counts'))
    total_sites = total_sites - 1
    sites_with_nlcd_post_qc = sites_with_nlcd_post_qc[-grep(pc_site, sites_with_nlcd_post_qc)]
  }else {
      # modis to landsat lookup - Removing Evergreen broadleaf forest and Deciduous needleaf forest and the 2nd Shrubland
    Landsat_Landcover = read_csv("../../www/Landsat.Landcover.csv")
    landsat_lc = Landsat_Landcover %>% 
      mutate(Landsat.Class = replace(Landsat.Class, MODIS.Class == 3, NA)) %>%
      mutate(Landsat.Class = replace(Landsat.Class, MODIS.Class == 2, NA)) %>% 
      mutate(Landsat.Class = replace(Landsat.Class, MODIS.Class == 7, NA))
    # create a landsat to modis lookup (so that no landsat values are left out)
    landsat_lc_lookup = read.csv('../../www/landsat_lc/nlcd_key.csv') %>% 
      dplyr::select(ID,NLCD.Land.Cover.Class) %>% left_join(landsat_lc, by = c('ID' = 'Landsat.Class')) %>%
      mutate(MODIS.Class = replace(MODIS.Class, ID == 12, NA)) %>%
      left_join(pft_df, by = c('MODIS.Class' = 'pft_key'))
    # Build crosswalk matrix for reclassify function (rcl)
    from_values = landsat_lc_lookup$ID
    becomes_values   = landsat_lc_lookup$MODIS.Class
    # Build matrix to use in reclassify function
    m = matrix(ncol = 2, nrow = length(from_values))
    m[,1] = from_values
    m[,2] = becomes_values
    # reclassified nlcd layer to match modis values
    site_rc_nlcd = reclassify(site_nlcd_raster, m)
    
    ######################################################## MODIS NDVI and LANDCOVER
    # Read in MODIS landcover
    modis_lc_dir   = paste0('../../www/site_data/', pc_site, '/data_layers/lc/')
    modis_lc_files = list.files(modis_lc_dir)
    this_modis_lc_file = paste0(modis_lc_dir, modis_lc_files[grep('MCD12Q1.006_500m_aid0001.nc', modis_lc_files)])
    # Read in NDVI raster brick to resample the MODIS landcover
    modis_ndvi_dir = paste0('../../www/site_data/', pc_site, '/data_layers/ndvi/tera/')
    modis_ndvi_files = list.files(modis_ndvi_dir)
    this_modis_ndvi_file = paste0(modis_ndvi_dir, modis_ndvi_files[grep('MOD13Q1.006_250m_aid0001.nc', modis_ndvi_files)])
    ndvi_tera_brick  = raster::brick(this_modis_ndvi_file, varname='_250m_16_days_NDVI', crs=sinu_crs)
    ndvi_raster_t    = raster::subset(ndvi_tera_brick, 1)
    ndvi_raster_merc = projectRaster(from = ndvi_raster_t, crs = merc_crs, res = res(ndvi_raster_t))
    ndvi_r_m_c = crop_raster(lat_merc, lng_merc, ndvi_raster_merc, height = 10000, width = 10000, crs_str = merc_crs)
    
    # Read in MODIS landcover raster brick using ndvi to resample it
    lc_brick  = raster::brick(this_modis_lc_file, crs=sinu_crs) #ONAQ breaks here
    lc_raster = raster::subset(lc_brick, 1)
    lc_raster_ = raster::resample(x = lc_raster, y = ndvi_raster_t, crs = sinu_crs, method='ngb')
    lc_raster_merc = projectRaster(from = lc_raster_, crs = merc_crs, method='ngb', res = res(ndvi_raster_t))
    lc_raster_merc_cr = crop_raster(lat_merc, lng_merc, lc_raster_merc, height = 10000, width = 10000, crs_str = merc_crs)
    # lc_raster_merc_cr_c = build_pft_palette(lc_raster_merc)
  
    ######################################################## BUILD PIXEL BUFFERS
    #Build 3 different scales of NDVI grid to use for analysis
    resolution = res(ndvi_r_m_c)[1]
    # 1x1 extent
    s_1      = .1
    e_1      = as(extent(lng_merc -s_1, lng_merc +s_1, lat_merc -s_1, lat_merc +s_1), 'SpatialPolygons')
    crs(e_1) =  merc_crs
    # 3x3 extent
    s_3      = resolution
    e_3      = as(extent(lng_merc -s_3, lng_merc +s_3, lat_merc -s_3, lat_merc +s_3), 'SpatialPolygons')
    crs(e_3) =  merc_crs
    # 5x5 extent
    s_5      = resolution *2
    e_5      = as(extent(lng_merc -s_5, lng_merc +s_5, lat_merc -s_5, lat_merc +s_5), 'SpatialPolygons')
    crs(e_5) =  merc_crs
    # Raster
    r_1by      = raster::crop(ndvi_r_m_c, e_1, snap='out')
    r_3by      = raster::crop(ndvi_r_m_c, e_3, snap='out')
    r_5by      = raster::crop(ndvi_r_m_c, e_5, snap='out')
    # Build polygon with the extents to use for extracting data from landcover (nlcd and modis)
    p_1_merc = as(extent(r_1by), 'SpatialPolygons')
    crs(p_1_merc) = merc_crs
    p_3_merc = as(extent(r_3by), 'SpatialPolygons')
    crs(p_3_merc) = merc_crs
    p_5_merc = as(extent(r_5by), 'SpatialPolygons')
    crs(p_5_merc) = merc_crs
    
    # The WGS polygons.
    e_1_wgs = spTransform(p_1_merc, wgs_crs)
    e_3_wgs = spTransform(p_3_merc, wgs_crs)
    e_5_wgs = spTransform(p_5_merc, wgs_crs)
    
    ######################################################## NLCD
    #Extract heterogeneity metrics under the shapefile (p_1_merc, p_3_merc, and p_5_merc)
    # Method to get 100% of the nlcd raster under the MODIS polygon 1x1
    p_1by_merc_cropped = raster::crop(site_rc_nlcd, p_1_merc, snap = 'out' )
    p_1by_merc_cropped_high_res   = raster::projectRaster(from = p_1by_merc_cropped, crs = merc_crs, method='ngb', res = res(p_1by_merc_cropped)/40.5)
    p_1by_merc_cropped_high_res_cr = raster::crop(p_1by_merc_cropped_high_res, p_1_merc, snap = 'in' )
    # p_1by_merc_cropped_c = build_pft_palette(p_1by_merc_cropped_high_res_cr)
    # Method to get 100% of the nlcd raster under the MODIS polygon 3x3
    p_3by_merc_cropped = raster::crop(site_rc_nlcd, p_3_merc, snap = 'out' )
    p_3by_merc_cropped_high_res   = raster::projectRaster(from = p_3by_merc_cropped, crs = merc_crs, method='ngb', res = res(p_3by_merc_cropped)/40.5)
    p_3by_merc_cropped_high_res_cr = raster::crop(p_3by_merc_cropped_high_res, p_3_merc, snap = 'in' )
    # p_3by_merc_cropped_c = build_pft_palette(p_3by_merc_cropped_high_res_cr)
    # Method to get 100% of the nlcd raster under the MODIS polygon 5x5
    p_5by_merc_cropped = raster::crop(site_rc_nlcd, p_5_merc, snap = 'out' )
    p_5by_merc_cropped_high_res   = raster::projectRaster(from = p_5by_merc_cropped, crs = merc_crs, method='ngb', res = res(p_5by_merc_cropped)/40.5)
    p_5by_merc_cropped_high_res_cr = raster::crop(p_5by_merc_cropped_high_res, p_5_merc, snap = 'in' )
    # p_5by_merc_cropped_c = build_pft_palette(p_5by_merc_cropped_high_res_cr)
    
    
    # Build dataframes for each pixel for the amount of heterogeneity metrics
    nlcd_df_at_extent_1 = as.data.frame(table(values(p_1by_merc_cropped_high_res_cr)), stringsAsFactors=FALSE) %>% 
      mutate(Var1 = as.double(Var1)) %>%
      left_join(pft_df, by = c('Var1' = 'pft_key')) %>% 
      mutate(id = '1by1') %>% mutate(total_pixels = sum(Freq)) %>%
      mutate(percent_cover = Freq/total_pixels) %>% 
      mutate(heterogeneity = length(Var1) ) %>%
      mutate(type = 'NLCD') %>%
      mutate(site = pc_site)
    nlcd_df_at_extent_3 = as.data.frame(table(values(p_3by_merc_cropped_high_res_cr)), stringsAsFactors=FALSE) %>% 
      mutate(Var1 = as.double(Var1)) %>%
      left_join(pft_df, by = c('Var1' = 'pft_key')) %>% 
      mutate(id = '3by3') %>% mutate(total_pixels = sum(Freq)) %>%
      mutate(percent_cover = Freq/total_pixels) %>% 
      mutate(heterogeneity = length(Var1)) %>%
      mutate(type = 'NLCD') %>%
      mutate(site = pc_site)
    # Sometimes it will fail here.. Not sure why??
    nlcd_df_at_extent_5 = as.data.frame(table(values(p_5by_merc_cropped_high_res_cr)), stringsAsFactors=FALSE) %>% 
      mutate(Var1 = as.double(Var1)) %>%
      left_join(pft_df, by = c('Var1' = 'pft_key')) %>% 
      mutate(id = '5by5') %>% mutate(total_pixels = sum(Freq)) %>%
      mutate(percent_cover = Freq/total_pixels) %>% 
      mutate(heterogeneity = length(Var1)) %>%
      mutate(type = 'NLCD') %>%
      mutate(site = pc_site)
    
    nlcd_df_at_extent_all = rbind(nlcd_df_at_extent_5 ,nlcd_df_at_extent_3, nlcd_df_at_extent_1)
    
    ######################################################## MODIS landcover
      #Extract heterogeneity metrics under the shapefile (p_1_merc, p_3_merc, and p_5_merc)
    # Method to get 100% of the modis landcover raster under the MODIS polygon 1x1
    p_1by_merc_modis_cropped = raster::crop(lc_raster_merc_cr, p_1_merc, snap = 'out' )
    p_1by_merc_modis_cropped_high_res   = raster::projectRaster(from = p_1by_merc_modis_cropped, crs = merc_crs, method='ngb', res = res(p_1by_merc_modis_cropped)/40.5)
    p_1by_merc_modis_cropped_high_res_cr = raster::crop(p_1by_merc_modis_cropped_high_res, p_1_merc, snap = 'in' )
    # p_1by_merc_modis_cropped_c = build_pft_palette(p_1by_merc_modis_cropped_high_res_cr)
    # Method to get 100% of the nlcd raster under the MODIS polygon 3x3
    p_3by_merc_modis_cropped = raster::crop(lc_raster_merc_cr, p_3_merc, snap = 'out' )
    p_3by_merc_modis_cropped_high_res   = raster::projectRaster(from = p_3by_merc_modis_cropped, crs = merc_crs, method='ngb', res = res(p_3by_merc_modis_cropped)/40.5)
    p_3by_merc_modis_cropped_high_res_cr = raster::crop(p_3by_merc_modis_cropped_high_res, p_3_merc, snap = 'in' )
    # p_3by_merc_modis_cropped_c = build_pft_palette(p_3by_merc_modis_cropped_high_res_cr)
    # Method to get 100% of the nlcd raster under the MODIS polygon 5x5
    p_5by_merc_modis_cropped = raster::crop(lc_raster_merc_cr, p_5_merc, snap = 'out' )
    p_5by_merc_modis_cropped_high_res   = raster::projectRaster(from = p_5by_merc_modis_cropped, crs = merc_crs, method='ngb', res = res(p_5by_merc_modis_cropped)/40.5)
    p_5by_merc_modis_cropped_high_res_cr = raster::crop(p_5by_merc_modis_cropped_high_res, p_5_merc, snap = 'in' )
    # p_5by_merc_modis_cropped_c = build_pft_palette(p_5by_merc_modis_cropped_high_res_cr)
    
      # Build dataframes for each pixel for the amount of heterogeneity metrics
    modis_lc_df_at_extent_1 = as.data.frame(table(values(p_1by_merc_modis_cropped_high_res_cr)), stringsAsFactors=FALSE) %>% 
      mutate(Var1 = as.double(Var1)) %>%
      left_join(pft_df, by = c('Var1' = 'pft_key')) %>% 
      mutate(id = '1by1') %>% mutate(total_pixels = sum(Freq)) %>%
      mutate(percent_cover = Freq/total_pixels) %>% 
      mutate(heterogeneity = length(Var1)) %>%
      mutate(type = 'MODIS') %>%
      mutate(site = pc_site)
    modis_lc_df_at_extent_3 = as.data.frame(table(values(p_3by_merc_modis_cropped_high_res_cr)), stringsAsFactors=FALSE) %>% 
      mutate(Var1 = as.double(Var1)) %>%
      left_join(pft_df, by = c('Var1' = 'pft_key')) %>% 
      mutate(id = '3by3') %>% mutate(total_pixels = sum(Freq)) %>%
      mutate(percent_cover = Freq/total_pixels) %>% 
      mutate(heterogeneity = length(Var1)) %>%
      mutate(type = 'MODIS') %>%
      mutate(site = pc_site)
    # Sometimes it will fail here.. Not sure why??
    modis_lc_df_at_extent_5 = as.data.frame(table(values(p_5by_merc_modis_cropped_high_res_cr)), stringsAsFactors=FALSE) %>% 
      mutate(Var1 = as.double(Var1)) %>%
      left_join(pft_df, by = c('Var1' = 'pft_key')) %>% 
      mutate(id = '5by5') %>% mutate(total_pixels = sum(Freq)) %>%
      mutate(percent_cover = Freq/total_pixels) %>% 
      mutate(heterogeneity = length(Var1)) %>%
      mutate(type = 'MODIS')%>%
      mutate(site = pc_site)
    
    mods_lc_df_at_extent_all = rbind(modis_lc_df_at_extent_5, modis_lc_df_at_extent_3, modis_lc_df_at_extent_1)
    
    # # Build a leaflet sanity check for the analysis look (commment out if you are gonna loop through more than 10 sites)
    # print (leaflet() %>% addTiles() %>% addRasterImage(p_5by_merc_modis_cropped_high_res_cr, colors = p_5by_merc_modis_cropped_c$palette) %>%
    #   addRasterImage(p_5by_merc_cropped_high_res_cr, colors = p_5by_merc_cropped_c$palette, opacity = .4) %>%
    #   addPolygons(data = e_1_wgs) %>% 
    #   addPolygons(data = e_3_wgs) %>% 
    #   addPolygons(data = e_5_wgs) %>%
    #   addCircleMarkers(lat = lat_wgs, lng = lng_wgs, radius = 5, color = 'black', weight=2, opacity = 1, label = pc_site)) 
    
    all_data_df = rbind(all_data_df, mods_lc_df_at_extent_all, nlcd_df_at_extent_all)
  }
}
```

ROI data for Phenocams in Continental US
```{r}
# Start with sites all phenocam sites that have nlcd, modis landcover and phenocam ROI data.
roi_pfts = c()
# Loop through the phenocam sites
for (pc_site in sites_with_nlcd_post_qc){
  # Extract Phenocam ROI data (Plant functional data)
  pc_roi_rows = subset(roi_files, roi_files$site == pc_site)
  pc_roi_types = unique(pc_roi_rows$roitype)
  pc_roi_type_counts = length(pc_roi_types)
  # Add all of the pc_roi_types to a char vector
  roi_pfts = c(roi_pfts, pc_roi_types)
}
as.data.frame(table(roi_pfts), stringsAsFactors = FALSE)
```


```{r}
# Just so we don't overwrite the data if we already have it stored
everything_df = all_data_df
write.csv(everything_df, paste0('phenocam_analysis_',format(Sys.time(), '%Y_%m_%d_%H%M%S'),'.csv'))
unique(everything_df$site)
```


```{r}
subset(all_data_df, all_data_df$site == 'intervale')
unique(all_data_df$site)
```



```{r}
test = p_5by_merc_cropped_high_res_cr@data@values
class(test)

if (test == 0){
  print (0)
}

leaflet() %>% addTiles() %>% addRasterImage(p_5by_merc_cropped_high_res_cr)
values(p_5by_merc_cropped_high_res_cr)
```














